### 2017-07-16 draft.tex
Initial commit

\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref}
\usepackage{fullpage}

\sectionfont{\large}
\subsectionfont{\normalsize}

\input{commands}

\title{Naturalness and Long-lived Beyond the Standard Model Particles}
\author{Bryan Cardwell}

\begin{document}

\singlespacing

\maketitle

\begin{abstract}

I'll write an abstract here.

\end{abstract}

\doublespacing

\section{The Standard Model}

\section{Naturalness and the Higgs mass}
    The naturalness criterion takes several forms, some of which feel way more like bullshit than others. Here are the formulations I can think of off the top of my head: (1) all parameters in a model should be of order 1, (2) Loop-level contributions should not be larger than tree-level contributions, (3) any small parameter should be protected by a custodial symmetry, and (4) fine-tuning is bad. To my ear, (1) and (2) sound dumb and (3) and (4) might be compelling with the right context.

    Let's look at (3). In the SM, the parameter of interest is the Higgs mass, which unlike the fermions and gauge bosons, has no custodial symmetry to hold it down. The fermions masses are protected by a U(1)xU(1) chiral symmetry that would exist if the fermions were massless, and the vector bosons are protected by gauge symmetry (*how does this one work? Would gauge symmetry be enlarged if vector bosons were massless?). The Higgs, a fundamental scalar, has no such symmetry. Looking at the 1-loop corrections to the Higgs propagator, we see a quadratic dependence on the cutoff scale, which implies that a Higgs mass well below the energy scale of new physics is unnatural.

    Now look at (4), again in the context of the Higgs mass. If mH depends quadratically on the cutoff, we expect it's mass to be fucking huge, like comparable to the cutoff scale. We know experimentally that its mass is 125.1 GeV, so it's bare mass (*or is it a coupling constant of some kind? I need to be extremely clear on this) must exactly cancel the cutoff-dependent contribution. 'Whatever', you might say, 'things cancel each other out sometimes'. In this case, however, the values need to be tuned to the tune of 1 part in 10\^30 or some crazy shit like that. We have no good explanation for why these two numbers would match so perfectly, so it seems incredibly suspicious that it would just happen by chance.

    There are other unnatural quantities that people worry about (even though they're less important to my world). I know of two off the top of my head: (1) whatever the parameter of interest is in the strong CP problem and (2) the cosmological consant. The strong CP problem is something like "some parameter in QCD stuff implies maximal CP violation, but we don't see any CP violation in strong interactions. The cosmological constant is way the fuck too small compared to naive expectations. Maybe like 120 orders of magnitude too small? I don't know of any reasonable solutions to the cosmological constant problem, and it seems like such a giant crazy problem that people just kinda sweep it under the rug. I have now said roughly everything I know about naturalness problems outside the contet of the Higgs mass.

\section{Naturalness Beyond the Standard Model}
    There are a few proposed solutions to the SM naturalness problem. SUSY is the main one, and I'll spend the great majority of my time on it. Extra dimensions and composite Higgs models are the other two that pop up fairly often, but won't spend much time on them outside the next two sentences. Extra dimensions solves the hierarchy problem either by lowering the cutoff scale (as in large extra dimensions (ADD)) or introducing a warping factor that reduces the level of unnaturalness (warped extra dimensions (RS)). Composite Higgs models propose that the Higgs stops behaving as a fundamental scalar at some energy level, which removes the quadratic dependence.

    SUSY introduces a new symmetry in which every field can rotate freely between fermions and bosons. Thus, every correction to the Higgs mass from a fermion loop is exactly cancelled by the assoicated boson loop, and vice-versa. We know that SUSY can't be an exact symmetry because the superpartners would have already been observed with the same mass as their SM counterparts. Broken SUSY can still be natural, however, as long as it's approximately true. That is, as long as the superpartners show up at a mass scale not too far above the EW scale. Some sparticles are more important than others for correcting the higgs mass and therefore naturalness, so we can get away with some sparticles being more massive than others, which is getting more appealing as null LHC results keep rolling in. There are other tricky things you can do to work around all these null results; I'll need to learn more about them in the immediate future.

\section{Long-lived Particles}
\subsection{Standard Model}
\subsection{Beyond the Standard Model}

\section{The CMS Detector}
\subsection{Tracker}
        The inner tracking system can be dividing into three regions. At r < 20 cm, the high particle flux requires smaller pixels to keep occupancy near 0.1\%. Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.

        The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million 285 um thick silicon sensors, each of which covers an active area of 16.2 x 64.8 mm\^2 (*really? I feel like I've seen "1 m\^2 coverage" before. This is way more than that). The pixels are spread between four barrel layers (BPIX) and 3 endcap rings (FPIX). The innermost barrel layer is now at 2.9 cm, whereas the original BPIX had only 3 layers with the innermost at 4.4 cm. The increased number of channels (*I didn't mention that num of channels had changed been changed), combined with the extra barrel layer, and smaller first-laer radius allows for 4-hit tracking out to eta < 2.4 and improved b-tagging despite the increased pileup expected in 2017.

        The next two layers are collectively known as the silicon strip tracker (SST). The SST is itself seperated into four sections, the inner barrel (TIB), outer barrel (TOB), inner disks (TID), and endcap (TEC). Together, all four sections have (*weak word) 9.6 million silicon strips that vary from 23 um to 52 um (*does this include endcaps?) in single-point resolution depending on the particle flux in each region. At each triger, the strip output voltage is transferred via optical link (*right language?) to be read out by off-detector front-end electronics (*right language?).

\subsection{Electromagnetic Calorimeter}
        The electromagnetic calorimeter (ECAL) is composed of 61200 lead tunstate crystals in the barrel and 7324 in each endcap (*is 'each' right?). Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere length = 2.2 cm), and radiation hard (up to 10 Mrad) calorimeter. The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields (*say B-field part better).

        The barrel section (EB) extends from 129 to NUMBER (*look up) cm and covers a pseudorapidity range of 0 to 1.479. Each crystal covers about 1 (*square?) degree in theta-eta (*double check) and is tapered (*right word?) so that it's long edges define lines of constant phi. In the end, the crystals have a width of approximately one Moliere radius and a depth of 25.8 radiation lengths.

        The endcap section (EE) is 314 cm from the IP (*right word?) and covers a pseudorapidity range of 1.479 to 3.0. Additionally, a preshower detector (two planes of silicon strip detectors and a lead absorber) sits just inside the grid of lead tungstate crystals. (*Say what the preshower is for? Is it for pi0 rejection? If so, how and why?)

\subsection{Hadronic Calorimeter}
        The hadronic calorimeter (HCAL) is composed of plastic scintillator interspersed within brass absorber. The scintillation light is transferred to readout through wavelength shifting fibres (WLS) that are spliced onto clear fibers (*say what readout means. PMT?). The scintillator plates are 3.7 mm thick.
        The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers, each of which ha 15 brass plates and covers an area of 0.087 x 0.087 in eta-phi. In addition, a single layer of 10 mm thick scintillator tiles sits just outside the solenoid. This extra layer, known as hadron outer (HO), spans a pseudorapidty range of -1.26 to 1.26 and increaes the effective HCAL interaction length to greater than 10.
        Each endcap consists of 14 towers with five degree phi segmentation and spans a pseudorapidity range of 1.3 to 3.0. Also, a steel and quartz fiber forward calorimeter (HF) sits 11.2 m from the interaction pipe in a pseudorapidty range of 3.0 to 5.0. In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline. (*say why HF is necessary)

\subsection{Solenoid}
        CMS employs a 4T superconducting solenoid to aid in the measurement of charged particle momenta. The solenoid consists of 2168 turns of Nb-Ti superconducting cable and has an inner diameter of 5.9 m and a length of 12.9 m (*is 5.9 right? I see "cold bore = 6.3 m" in "At the CERN LHC"). The flux returns through an iron yoke that also houses the muon system. The significant (*quantify?) bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of 10\% for muons up to 1 TeV.

\subsection{Muon System}
        The muon system (MS), which is the outermost subdetector, detects muons with 3 varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps. The DTs and CSCs were chosen for the barrel and endcap, respectively, because the neutron-induced background, muon rates, and strength of the magnetic field are all higher in the encap. The RPCs are useful in both the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification. Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines (*quantify).

        In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at 4.0, 4.9, 5.9, and 7.9 m. SAY SOMETHING ABOUT HOW DTS ACTUALLY WORK. The maximum drift length is 2 cm and the single point resolution is 200 um. When reconstructing a vector describing the muon momentum, the phi precision is better than 100 um in position and 1 mrad in direction.

        Each muon endcap detector (ME) is composed of 234 CSCs and 4 RPC stations (*figure out exactly what RPC station means and say that instead). Each CSC has six gas gaps with radial cathode strips and nearly perpendicualr planes of anode wires. The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, but the slower (*quantify) cathode strip signal provides precise (*quantify) position measurements. In the end, the CSC spacial resolution is approximate 200 um and the angular resolution is approximately 10 mrad.

\subsection{Muon System}
        The trigger reduces the data writing rate from the 40 MHz collision rate to less than 1 kHz so that events can be written to tape. The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT). The HLT uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, ET, and mu) and uses custom electronics to reduce the rate to ~100 kHz in 3.8 us. The HLT then uses a dedicated processor farm to reduce the rate to the desired < 1 kHz.

\section{LHC Searches for Long-lived Particles}
\subsection{Overview}
\subsection{Displaced Vertices}
            LLPs with lifetimes on the order of ~1 nm (*check this) can decay inside the detector volume, but with a reconstructed vertex far from the nominal interaction point (*last 3 words true?). ATLAS performs one such search with large MET and at least one displaced vertex (DV) with large track multiplicity. The search is sensitive to long-lived gluinos with lifetimes in the 10 ps to 10 ns range.

            LLPs appear in BSM theories such as Hidden Valley models, where the LLP decay is suppressed by a large barrier potential, SUSY models with small R-parity violating couplings, and Split SUSY, where the LLP decay is suppressed by the high virtuality of an intermediate state. This search uses a simplified model in the Split SUSY paradigm as a benchmark. In the simplified model, gluinos are kinematically accessible while squarks are not. The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino. Because the squark mass is so high, the gluino lives long enough to form an R-hadron with SM quarks and propogate some measureable distance away from the IP.

            Jets and MET are reconstructed as normal in this analysis, but special care must be taken when looking for displaced tracks. The standard ATLAS tracking algorithm constrains the transverse and longitudinal impact parameters of potential tracks, so the authors employed an additional algorithm, referred to as large-radius tracking (LRT). LRT is run after the standard tracking algorithm and only uses hits that were not used in standard track reconstruction. By relaxing d0, z0, and number of hits requirements, LRT is able to reconstruct tracks that point back to DVs.

            Because no SM process will produce events that meet the mass and track multiplicity requirements on the DV, only instrumental backgrounds are considered. Specifically, hadronic interactions in detector material, incorrectly combining vertices from short-lived SM particles, and incorrectly adding hits from unrelated tracks to low-mass vertices (*make sure I understand this last one) can all lead to events that mimic the desired signal.

            The authors minimize the effect of hadronic interactions by vetoing the material-dense regions of the detector and estimate the residual background by extrapolating from the low-mass region, which is dominated by hadronic interactions. After a dedicated study, the background from merged vertices was found to be negligable. Finally, the background from crossing tracks is treated as an uncertainty in the background estimate that is determined with a model that adds pseudo-tracks to data vertices.

            After estimating 0.02 +- 0.02 background events, exactly 0 are observed. The result is then interpreted as upper limits on the gluino mass and pair-production cross section as a function of gluino lifetime. (*Include plots and/or report numbers)

\subsection{Disappearing Tracks}
            Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker. Specifically, models with winos as the lightest gauginos, such as many AMSB models, will have a chargino NLSP with an observable lifetime (0.2 ns is a typical estimate) that eventaully decays to the neutralino LSP and, commonly, a pion. The nearly-degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products. The low-momentum pion is then unlikely to be constructed, which results in a disappearing track (*explicitly mention assumed non-interaction of LSP?).

            Both ATLAS and CMS looked for disappearing tracks during Run I, but the new trackers installed in ATLAS during LS1 and CMS during the EYETS (*define acronyms) should increase sensitivity to decays at shorter radii (*I haven't mentioned previous iterations when talking about other analyses). The ALTAS search presented here is sensitie to LLP lifetimes of approximated 10 ps to 10 ns.

            The authors consider two signal processes: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET. Process (1) could be the only gaugino production mode at the LHC if the gluino mass to kinematically unaccessable (*check for plagarism and accuracy), but process (2), which leads chargino production in cascade decays,  will be dominant if the gluino mass is within reach. The ISR jet in process (1) is not physically required; it simply provides something for the gluinos to recoil off of so the MET signal isn't lost (*My interpretation. Run it by Andrew, Jamie, or Brian).

            Disappearing tracks canditates, called pixel tracklets, are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard track reconstruction algorithm. The pixel tracklets are required to pass several isolation, pT, and quality requirements such as number of pixel layer hits. Finally, the disappearing criteria is enforced by requiring exactly zero assiated hits in the SCT (*SCT = semiconductor tracker = tracking layer after pixel in ATLAS). (*Do I need to say anything about signal efficiency?) Event selection requires one pixel tracklet, no electron or muon candidates (to suppress ttbar W/Z+j processes), and the MET and jet requirements associated with either of the two production modes described above.

            Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by pixel hits that don't have the proper SCT hits associated to them, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon. These backgrounds come primarily from ttbar and W+j, and estimates for each type of background are obtained from data. After constructing control regions for the lepton- and hadron-related backgrounds, the authors extract transfer factors... (*I don't understand this. Need to work through it). The authors estimate the remaining background by defining a control region with large d0 uncertainty that is dominated by pixel tracklets reconstructed from random, unrelated hits. After verifying that the pT spectrum of fake pixel tracklets is independent of MET (which defines the signal and control regions), the authors estimate the contribution of this background in the signal region by multiplying the number of signal-region tracklets by the ratio of control-region fake tracklets to total control-region tracklets.

            No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass gluon mass plane for the QCD production process (*will be way clearer after texing in sparticle symbols). (*Include either plots or \#s)

\subsection{Stopped Particles}
            With long enough lifetimes and sufficient mass, LLPs could actually come to rest in the detector before decaying. The eventual decay would then lead to energy deposits in the calorimeters or hits in the muon system that could be out of time with proton bunch crossings. A recent CMS analysis looked for such a signal in dimuon final states (*necessarily dimuon?) using the full 2015 and 2016 datasets.

            This analysis is interpreted in the context of two potential LLPs: gluinos and multiply charged massive particles (mchamps). Long-lived gluinos can appear in models such as Split SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light. After being pair produced, gluinos could form R-hadrons and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs. The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime. Mchamps will not be discussed further because their existence is not directly motivated by naturalness.

            This analysis uses the muon system to look for pairs of muons that arrive out of time with bunch crossings. The main backgrounds to such a signal are cosmics, beam halo, and muon system noise. Beam halo and muon system noise are easily removed by the selection criteria, but distinguishing signal from cosmics requires a more nuanced approach. After generating signal MC and modeling cosmics from data obtained in dedicated cosmic runs, the authors found that cosmics and signal could be differentiated using the time-of-flight information from the muon system RPCs and DTs. Essentially, the direction of muon momentum could be gleaned from the timing information, and the authors required outgoing muons in both the upper and lower hemispheres.

            In addition to the above criteria, the authors developed a new muon reconstruction algorithm, called displaced standalone (DSA), that uses only muon system hits and does not constrain the location of the primary vertex in any way. The full selection requires exactly one good DSA track in each hemisphere with pT greater than 50 GeV, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement, such as the minimum number of DT and RPC hits and maximum time measurement uncertainty. Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0), minimize background from beam halo and cosmics.

            After estimating the background by extrapolating data from the cosmic-enriched region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculated the expected background for LLP lifetimes ranging from 10\^-7 to 10\^6 s. In all cases, the expected background was less then one event. After unblinding, the observed number of events is exactly zero in every lifetime scenerio. These results are then interpreted as upper limits on the signal production cross section (*include limit plots or table), which are the first limits for stopped particles that decay to muons at the LHC.

\subsection{Heavy Stable Charged Particles}
            Particles that live for more than a couple ns (*Check this and be more exact) will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying. If such a particle is also sufficiently massive, it can be catigorized as a heavy stable charged particle (HSCP). HSCPs are characterterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material. Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss.

            HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and q=+-e (*dE/dx plot is nice around here). These criteria (tracker dE/dx and and MS TOF) provide two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS depending on the nature of R-hadron's interaction with nuclear matter, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with aritrary electric charge. The first two models bear more directly on naturalness and SUSY, so they will be the focus of this presentation.

            (*I should talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta~1. Zig-zag offset is used to estimate beta. Not sure where to fit it in.) (*Also need to talk about tracker-only vs tracker+TOF)

            The trigger requires all events to have either a high-pT muon or large MET. The high-pT muon trigger is more efficient for all benchmark models except the case where the R-hadron becomes neutral before reaching the MS. In the case where the R-hadron does not leave a track in the MS, the large MET trigger should recover some events.

            The authors estimate the signal-region background using and ABCD method in which events are binned in a 2D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region (*Do I need to explain this? If I do, I should be more clear). Systematic uncertainties are introduced in background estimation, signal acceptance, and integrated luminosity.

            No significant excess over predicted background is observed, so the results are interpreted as upper limits in the production cross section - mass plane for the considered models. By comparing the observed and theoretical limits, the authors also extract mass limits for the gluinos, stops, and staus in various models.

\section{Experimental Viability of Natural BSM}

\section{Conclusion}

\clearpage
\pagebreak
\singlespacing
\bibliography{candidacy}{}
\bibliographystyle{auto}

\end{document}

### 2017-07-18 tex/draft.tex
7/17 update

--- 2017-07-16 draft.tex
@@
 \section{The Standard Model}
+    The standard model of particle physics (SM) decribes all known particles and forces (except gravity) and is experimentally verified to astonishing (*weak word) accuracy.
+The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 5 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong fundamental forces, and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
+
+    The SM particles fit into multiplets of three symmetry groups, which makes the SM an SU(3)cxSU(2)LxSU(1)Y theory.
+These three symmetry groups correspond to color, the charge associated with the strong nuclear force; weak isopin, the charge associated with the left-handed chiral doublet something something; and weak hypercharge, the something something something, respectively.
+
+    The Higgs potential (*insert equation) has a nonzero vacuum expectation value (VEV), which spontaneously breaks the SU(2)LxU(1)Y symmetry to a U(1)EM symmetry.
+Breaking the continuous symmetries creates 4 Nambu-Goldstone bosons, 3 of which are 'eaten' by the W+, W-, and Z bosons, causing the gauge bosons to acquire mass (*say in terms of DOF instead?).
+After parameterizing the Higgs field in terms of its VEV and propagating something something, the SM Lagrangian now contains mass terms for the quarks and leptons (*this is the first time I'm saying those words)(*Include eqs probably).
+
+    Like all SM particles, the Higgs boson interacts with virtual particles in the vacuum through loop processes.
+The Higgs is unique, however, in that it is the only fundamental scalar in the theory.
+As a fundamental scalar, the Higgs sees corrections to its mass that depend quadratically on the energy scale at which the SM is replaced by a more complete theory (*eqs).
+The fermions and gauge bosons do not suffer this same fate because their masses are protected by the chiral and gauge symmetries, which are referred to as custodial symmetries in this context.
+The Higgs mass is found experimentally to be 125.1 GeV, even though it's sensitive to energy scales some 10\^16 times higher.
+This leads many (*weak) to describe the Higgs mass as 'unnatural', a concept that will be defined thoroughly below.
 

### 2017-07-20 tex/draft.tex
7/19 update

--- 2017-07-16 draft.tex
@@
 
+\newpage
+\tableofcontents
+\newpage
 \doublespacing
@@
 \section{The Standard Model}
+    The standard model of particle physics (SM) describes all known particles and forces (except gravity) and is experimentally verified to astonishing (*weak word) accuracy (*say 2nd clause better).
+The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 5 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces, and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
+
+    (*Rewrite this whole paragraph while looking at a book)
+    The SM particles fit into multiplets of three symmetry groups, which makes the SM an SU(3)cxSU(2)LxSU(1)Y theory (*awkward).
+These three symmetry groups correspond to color, the charge associated with the strong nuclear force; weak isospin, the charge associated with the left-handed chiral doublet something something; and weak hypercharge, the something something something, respectively.
+
+    The Higgs potential (*insert equation) has a nonzero vacuum expectation value (VEV), which spontaneously breaks the SU(2)LxU(1)Y symmetry to a U(1)EM symmetry.
+Breaking 3 of the 4 generators leaves 3 extra degrees of freedom, which ultimately become the masses of the W+, W-, and Z bosons, while the remaining degree of freedom is associated with electric charge and the massless photon.
+Expanding the Higgs field about its VEV and picking a gauge produces quark and charged lepton mass terms in the SM Lagrangian.
+In this way, spontaneous symmetry breaking of the Higgs field gives mass to all massive SM particles (*Give example mass term or work it out a little bit).
+
+    (*rewrite this paragraph while looking at a book)
+    Like the mass of all SM particles, the Higgs mass is affected by interactions with virtual particles through loop processes.
+As the only fundamental scalar in the theory, however, the Higgs sees corrections to its mass that depend quadratically on the cutoff scale of the SM.
+(*compare to dependence of fermions and gauge bosons, show a little math).
+To show this dependence on loop corrections, SM masses are often written as power series, where the first term is the bare (uncorrected) mass and the following terms are due to loop corrections (*how bout some eqs?).
+The next section will explore the concept of naturalness, a major motivating principle in beyond the SM (BSM) physics, that is directly tied to the relationship between a particle's bare mass and the terms that correct it.
 
 \section{Naturalness and the Higgs mass}
-    The naturalness criterion takes several forms, some of which feel way more like bullshit than others.
-Here are the formulations I can think of off the top of my head: (1) all parameters in a model should be of order 1, (2) Loop-level contributions should not be larger than tree-level contributions, (3) any small parameter should be protected by a custodial symmetry, and (4) fine-tuning is bad.
-To my ear, (1) and (2) sound dumb and (3) and (4) might be compelling with the right context.
+    The naturalness criterion takes several forms.
+Here are a few (*cite these): (1) all parameters in a model should be of order 1, (2) Loop-level contributions should not be larger than tree-level contributions, (3) any small parameter should be protected by a custodial symmetry, and (4) fine-tuning is bad (*probably a better way to say 4).
+Although these statements are all trying to get at the same fundamental notion, I find (3) and (4) to be most compelling.
 
+    (*cite guidice naturally and t'hooft naturalness)
     Let's look at (3).
-In the SM, the parameter of interest is the Higgs mass, which unlike the fermions and gauge bosons, has no custodial symmetry to hold it down.
-The fermions masses are protected by a U(1)xU(1) chiral symmetry that would exist if the fermions were massless, and the vector bosons are protected by gauge symmetry (*how does this one work?
-Would gauge symmetry be enlarged if vector bosons were massless?).
-The Higgs, a fundamental scalar, has no such symmetry.
-Looking at the 1-loop corrections to the Higgs propagator, we see a quadratic dependence on the cutoff scale, which implies that a Higgs mass well below the energy scale of new physics is unnatural.
+In the SM, the small parameter of interest is the Higgs mass, which has no custodial symmetry to hold it down.
+This situation contrasts that of the fermions and gauge bosons, whose masses are kept small by custodial symmetries.
+That is, the SM would be more symmetric (*weird wording?) if fermions and gauge bosons were massless.
+Specifically, massless fermions would have an extra U(1)xU(1) chiral symmetry, and massless vector bosons would have an extra gauge symmetry (*?!?!?!).
+The Higgs, a fundamental scalar, has no such symmetry (*repetative) so we deem its low mass to be unnatural.
+(*explain why fundamental scalars have no custodial symmetry?
+I certainly better learn why.)
 
     Now look at (4), again in the context of the Higgs mass.
-If mH depends quadratically on the cutoff, we expect it's mass to be fucking huge, like comparable to the cutoff scale.
-We know experimentally that its mass is 125.1 GeV, so it's bare mass (*or is it a coupling constant of some kind?
-I need to be extremely clear on this) must exactly cancel the cutoff-dependent contribution.
-'Whatever', you might say, 'things cancel each other out sometimes'.
-In this case, however, the values need to be tuned to the tune of 1 part in 10\^30 or some crazy shit like that.
-We have no good explanation for why these two numbers would match so perfectly, so it seems incredibly suspicious that it would just happen by chance.
+The terms correcting the Higgs mass depend quadratically on the cutoff energy scale, which must be at or below the scale where quantum gravity becomes important (MP = 1/rootG ~ 10\^18??).
+This creates a sticky situation.
+If the terms correcting the bare mass are order(10\^32)GeV and the observed Higgs mass is order(100)GeV, then the bare mass must exactly cancel the corrections to approximately 1 part in 10\^30.
+At present, no good evidence exists to explain why the bare mass and corrections would match so perfectly.
+The level of exact cancellation is known as 'fine tuning'.
 
-    There are other unnatural quantities that people worry about (even though they're less important to my world).
-I know of two off the top of my head: (1) whatever the parameter of interest is in the strong CP problem and (2) the cosmological consant.
-The strong CP problem is something like "some parameter in QCD stuff implies maximal CP violation, but we don't see any CP violation in strong interactions.
-The cosmological constant is way the fuck too small compared to naive expectations.
-Maybe like 120 orders of magnitude too small?
-I don't know of any reasonable solutions to the cosmological constant problem, and it seems like such a giant crazy problem that people just kinda sweep it under the rug.
-I have now said roughly everything I know about naturalness problems outside the contet of the Higgs mass.
+    (*probably doesn't need to be in final paper, but I'd like to check my basic understanding with Jamie, et al)
+    There are other unnatural quantities that people worry about in physics.
+I know of two off the top of my head: (1) thetaQCD in the strong CP problem (2) the cosmological consant.
+The strong CP problem comes from the fact that QCD technically allows CP violation even though such violation has never been observed.
+The degree of violation is parameterized as thetaQCD, which recasts the problem into the naturalness context of 'why is thetaQCD so small?'.
+The cosmological constant is experimentally ~60 to ~120 orders of magnitude smaller than the predicted value (*predicted how?).
+While these issues deserve serious attention, they will not be considered further here.
 
-\section{Naturalness Beyond the Standard Model}
+    (*talk about anthropic principle or other arguments against?)
+    (*I got tired of reading this section and haven't edited this paragraph at all yet)
     There are a few proposed solutions to the SM naturalness problem.
-SUSY is the main one, and I'll spend the great majority of my time on it.
+Supersymmetry (SUSY) is the main one, and I'll spend the great majority of my time on it.
 Extra dimensions and composite Higgs models are the other two that pop up fairly often, but won't spend much time on them outside the next two sentences.
@@
 Composite Higgs models propose that the Higgs stops behaving as a fundamental scalar at some energy level, which removes the quadratic dependence.
+(*Hidden valley, dark sector, little Higgs?)
 
-    SUSY introduces a new symmetry in which every field can rotate freely between fermions and bosons.
-Thus, every correction to the Higgs mass from a fermion loop is exactly cancelled by the assoicated boson loop, and vice-versa.
-We know that SUSY can't be an exact symmetry because the superpartners would have already been observed with the same mass as their SM counterparts.
-Broken SUSY can still be natural, however, as long as it's approximately true.
-That is, as long as the superpartners show up at a mass scale not too far above the EW scale.
-Some sparticles are more important than others for correcting the higgs mass and therefore naturalness, so we can get away with some sparticles being more massive than others, which is getting more appealing as null LHC results keep rolling in.
-There are other tricky things you can do to work around all these null results; I'll need to learn more about them in the immediate future.
+\section{SUSY and LLPs}
+    (*is there a way to move the naming stuff elsewhere or shorten it?)
+    SUSY introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between fermions and bosons.
+In it's simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson (*and an extra Higgs field - can I gloss over that?).
+The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
+stop or smuon), and the spin-1/2 superpartners to the SM bosons are given the name of their SM counterpart with "ino" tacked on to the end (e.g.
+Higgsino or wino).
+Together the superpartners to the SM particles are known as sparticles.
+Because fermion loops come with a relative minus sign (*there must be a better way to say that), every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
+If supersymmetry were exact, the bare Higgs mass would be uncorrected to all orders in perturbation theory.
 
-\section{Long-lived Particles}
-\subsection{Standard Model}
-\subsection{Beyond the Standard Model}
+    Experimental evidence shows that SUSY must be broken, however, because no superpartners have been found, and exact SUSY requires each superpartner to have the same mass as its standard model counterpart.
+The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenemena.
+A handful of models with particular approaches to SUSY breaking that are particularly prominant or particularly relevant to naturalness or long-lived particles (LLPs) are gauge-mediated susy breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), split SUSY, and R-parity violating SUSY (RPV).
+The details of these models will be explored as needed throughout this paper.
+
+    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and (*and/or?) would have reduced sensitivity to common SUSY search techniques (*does 'reduced sensitivity to techniques' make sense?).
+Specifically, we are interested in SUSY breaking models that predict LLPs.
+That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point, which includes everything from particles that decay at (*give ballparky number (~100um?)) to particles that propagate through the entire detector.
+
+    In both the SM and in BSM theories, LLPs result from one of the following: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
+In the SM, the electron and proton are the lightest particles carrying electric charge and baryon number, respectively, which leads to their absolute stability through charge and baryon number conservation.
+Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay (*also mention that they're both weak decays?).
+(*Mention neutrino, pion, kaon, whatever other bound state I might be forgetting?)
+
+    In SUSY models, LLPs arise for the same basic reasons, and many different SUSY models meet different LLP criteria in different ways.
+The most common (*based on my assumptions) SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from predicting proton decay.
+In models with R-parity, the SM particles have R-parity +1 (*double check this explanation) and their superpartners have R-parity -1.
+Conserving overall R-parity (*specifically the product; does overall mean that?) at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is an absolutely stable LLP.
+The second phenomenon is the main motivation behind using missing energy as the typical SUSY seach signature.
+
+    In models with R-parity violation (RPV), LLPs can be produced when the RPV terms have small coupling constants, which leads to long-lived, but not perfectly stable, LSPs (*any way non-LSPs could be long-lived for this reason too?).
+Luckily, RPV models can still avoid proton decay by only allowing terms that violate either baryon number or lepton number but not both.
+A similar situation arises in GMSB models where the gravitino is the LSP.
+The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs(*do I need to explain GMSB here?).
+(*cite dimopoulos low energy)
+
+    LLPs from highly-virtual intermediate particles can occur in models such as split (or mini-split) SUSY, where the scalar sparticles are significantly more massive than the gauginos.
+In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark.
+(*cite kilian) (*mention that split throws out naturalness motivation?)
+
+    SUSY models with degenerate sparticle spectra can have increased sparticle lifetimes from the reduced phase space for decays.
+In some AMSB models (*be more specific), for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
+The wino's lifetime, then, is increased by the lack of phase space in which to decay.
+(*cite R\&S out of this world)
+    (*merge last 2 paragraphs under 'mass spectra lead to LLP' concept?)
+    (*never said anything about hidden valley or dark sector stuff. Never said the word R-hadron. Never said stealth or displaced SUSY. Should I?)
 
@@
 \subsection{Overview}
+    LLPs leave distinct signatures that differentiate LLP signals from SM backgrounds but also add complexity to LLP analyses.
+CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to veer off the traditional analysis path in terms of object reconstruction (*really reconstruction?
+Maybe object definition?), background estimation, and which data tier to use (*can I say this more generally?).
+This paper will focus on four complementary LLP signatures: displaced vertices, disappearing tracks, stopped particles, and heavy stable charged particles (HSCPs)(*is HSCP a signature?
+say TOF / dE/dx instead?).
+
+    Displaced vertices and disappearing tracks both look for particles that are unstable on detector timescales (*quantify?).
+Displaced vertices searches are sensitive to LLPs that decay to visible (*detectable?
+some other word?) particles in the inner volume (*specify) of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point.
+Disappearing tracks searches are sensitive to LLPs that decay to invisible (*neutral?
+some other word?) particles along with particles that are too soft to be reconstructed.
+Together, these two types of analyses cover something something parameter space of LLPs that decay on detector timescales.
+
+    HSCP and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
+HSCP searches use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles, which normally (*quantify) have beta > 0.9.
+Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomena that could be possible with long-enough LLP lifetimes and small initial kinetic energy.
+These analyses look (*repetative) for calorimeter energy deposits or hits in the muon system (*too specific for LLP analyses intro?) that are out of time with proton bunch crossings that could be due to stopped particles decaying.
+
+    These four approaches cover a wide range of LLP lifetimes that would be missed in traditional searches.
+The next section will look  at a recent example of each analysis type from either ATLAS or CMS.
 \subsection{Displaced Vertices}

### 2017-07-21 tex/draft.tex
7/20 update

@@
 \section{The Standard Model}
-    The standard model of particle physics (SM) describes all known particles and forces (except gravity) and is experimentally verified to astonishing (*weak word) accuracy (*say 2nd clause better).
-The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 5 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces, and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
+    The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing (*weak word) accuracy (*say 2nd clause better).
+The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces (*maybe put in pre-EWSB terms instead?), and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
 
-    (*Rewrite this whole paragraph while looking at a book)
-    The SM particles fit into multiplets of three symmetry groups, which makes the SM an SU(3)cxSU(2)LxSU(1)Y theory (*awkward).
-These three symmetry groups correspond to color, the charge associated with the strong nuclear force; weak isospin, the charge associated with the left-handed chiral doublet something something; and weak hypercharge, the something something something, respectively.
+    All SM particles transform according to the gauged symmetry group SU(3)cxSU(2)LxU(1)Y, where SU(3)c is associated with color charge, SU(2)L is associated with weak isospin, and U(1)Y is associated with weak hypercharge.
+The gauge bosons are associated with the generators of these groups, thus there are 8 gluons associated with SU(3)c, 3 W bosons associated with SU(2)L, and 1 B boson associated with U(1)Y.
+The fermions are catagorized by which representation of each group they fit into.
+For example, SU(3)c distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and SU(2)L distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
+Finally, different values of weak hypercharge further distignuish SM particles according to a linear combination of their weak isospin and electric charge (*is there some more fundamental way to describe Y?).
 
-    The Higgs potential (*insert equation) has a nonzero vacuum expectation value (VEV), which spontaneously breaks the SU(2)LxU(1)Y symmetry to a U(1)EM symmetry.
-Breaking 3 of the 4 generators leaves 3 extra degrees of freedom, which ultimately become the masses of the W+, W-, and Z bosons, while the remaining degree of freedom is associated with electric charge and the massless photon.
-Expanding the Higgs field about its VEV and picking a gauge produces quark and charged lepton mass terms in the SM Lagrangian.
-In this way, spontaneous symmetry breaking of the Higgs field gives mass to all massive SM particles (*Give example mass term or work it out a little bit).
+    The Higgs potential has a nonzero vacuum expectation value (VEV), which spontaneously breaks SU(2)LxU(1)Y to U(1)EM while leaving SU(3)c unscathed.
+Once the dust settles, the B and 3 W bosons have been mixed to produce the W+, W-, Z bosons that mediate the weak force and the photon that mediates electromagnetism.
+3 of the 4 generators are broken in the process, leaving 3 extra degrees of freedom that ultimately become the masses of the W+, W-, and Z bosons while the remaining symmetry is associated with electric charge.
+Furthermore, expanding the Higgs field about its VEV produces mass terms for the quarks and charged leptons, thus giving mass to all massive SM particles.
+(*probably show a little math)
 
-    (*rewrite this paragraph while looking at a book)
-    Like the mass of all SM particles, the Higgs mass is affected by interactions with virtual particles through loop processes.
-As the only fundamental scalar in the theory, however, the Higgs sees corrections to its mass that depend quadratically on the cutoff scale of the SM.
-(*compare to dependence of fermions and gauge bosons, show a little math).
-To show this dependence on loop corrections, SM masses are often written as power series, where the first term is the bare (uncorrected) mass and the following terms are due to loop corrections (*how bout some eqs?).
-The next section will explore the concept of naturalness, a major motivating principle in beyond the SM (BSM) physics, that is directly tied to the relationship between a particle's bare mass and the terms that correct it.
+    (*kinda funny wording throughout. Maybe it would be better to trade some words for math?)
+    All SM particles interact with virtual particles through loop interactions.
+These interactions lead to corrections to SM parameters such as particle masses.
+It is common to write a given parameter as a linear combination of its 'bare' (uncorrected) value and its corrections.
+As the only fundamental scalar in SM, the Higgs is uniquely affected by these corrections.
+The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the Higgs bare mass and the terms that correct it.
 
@@
 
-    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and (*and/or?) would have reduced sensitivity to common SUSY search techniques (*does 'reduced sensitivity to techniques' make sense?).
-Specifically, we are interested in SUSY breaking models that predict LLPs.
+    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and (*and/or?) produce a signal that could be missed by common SUSY search techniques.
+Specifically, we are interested in SUSY models that predict LLPs.
 That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point, which includes everything from particles that decay at (*give ballparky number (~100um?)) to particles that propagate through the entire detector.
@@
 \section{The CMS Detector}
+\subsection{Overview}
+        (*cite cms experiment at the cern lhc)
+          The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from 14 TeV proton-proton collisions at the Large Hadron Collider (LHC).
+To meet this goal, CMS combines information from several subdetectors nested radially in and around a 4-T superconducting solenoid.
+All together, CMS is 21.6 m long, 14.6 m across, and weighs approximately 12500 tons.
+The subdetectors that make up CMS are described below.
+
 \subsection{Tracker}
-    The inner tracking system can be dividing into three regions.
-At r < 20 cm, the high particle flux requires smaller pixels to keep occupancy near 0.1\%.
+        (*cite CMS TDR, jinst 12 c02033)
+        (*maybe I should trade some number listing for talking about how silicon detectors work)
+        (*what about readout, cooling, etc?)
+        In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint (*too flowery?) primary and secondary vertices.
+The tracker is subdivided into two regions: at r < 20 cm, the high particle flux (*specify) requires smaller pixels to keep occupancy near 0.1\%.
 Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
 
-    The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million 285 um thick silicon sensors, each of which covers an active area of 16.2 x 64.8 mm\^2 (*really?
-I feel like I've seen "1 m\^2 coverage" before.
-This is way more than that).
-The pixels are spread between four barrel layers (BPIX) and 3 endcap rings (FPIX).
-The innermost barrel layer is now at 2.9 cm, whereas the original BPIX had only 3 layers with the innermost at 4.4 cm.
-The increased number of channels (*I didn't mention that num of channels had changed been changed), combined with the extra barrel layer, and smaller first-laer radius allows for 4-hit tracking out to eta < 2.4 and improved b-tagging despite the increased pileup expected in 2017.
+        The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million silicon pixels, each of which covers an active area of 100 by 150 um\^2.
+The pixels are spread between four barrel layers (BPIX) at 2.9 < r < 16 cm and 3 endcap rings (FPIX) at 29 < z < 52 cm.
+The upgraded pixel tracker should provide 4-hit tracking out to eta < 2.4 and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
 
-    The next two layers are collectively known as the silicon strip tracker (SST).
-The SST is itself seperated into four sections, the inner barrel (TIB), outer barrel (TOB), inner disks (TID), and endcap (TEC).
-Together, all four sections have (*weak word) 9.6 million silicon strips that vary from 23 um to 52 um (*does this include endcaps?) in single-point resolution depending on the particle flux in each region.
-At each triger, the strip output voltage is transferred via optical link (*right language?) to be read out by off-detector front-end electronics (*right language?).
+        Just outside the pixel tracker, the silicon strip tracker (SST) occupies the 20 < r < 116 cm and |z| < 282 cm region of CMS.
+Composed of 9.3 million silicon strips that vary from \_ to \_ in size (*look up) depending on particle flux, the SST covers an active area of roughly 196 m\^2.
+At each trigger, the strip output voltage is transferred via optical link to be read out by off-detector front-end electronics (*right language?).
 
 \subsection{Electromagnetic Calorimeter}
-    The electromagnetic calorimeter (ECAL) is composed of 61200 lead tunstate crystals in the barrel and 7324 in each endcap (*is 'each' right?).
-Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere length = 2.2 cm), and radiation hard (up to 10 Mrad) calorimeter.
+        (*cite CMS TDR)
+        (*talk about readout?)
+        (*More in the way of concept/how stuff works?)
+        Moving outward, the electromagnetic calorimeter (ECAL) follows the inner tracker.
+As a homogeneous scintillation calorimeter, ECAL uses 61200 lead tunstate crystals in the barrel and 7324 in each endcap to reconstruct the energy deposited during electromagnetic showers.
+Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere length = 2.2 cm), and radiation hard (up to 10 Mrad(*learn context for this number)) calorimeter.
 The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields (*say B-field part better).
 
-    The barrel section (EB) extends from 129 to NUMBER (*look up) cm and covers a pseudorapidity range of 0 to 1.479.
-Each crystal covers about 1 (*square?) degree in theta-eta (*double check) and is tapered (*right word?) so that it's long edges define lines of constant phi.
-In the end, the crystals have a width of approximately one Moliere radius and a depth of 25.8 radiation lengths.
+        The barrel section (EB) extends radially from 129 to 177 (*look up) cm and covers a pseudorapidity range of 0 to 1.479.
+The crystals are tapered to approximately project back to the IP but not so perfectly that particle trajectories would be likely to align with cracks.
+Each crystal is approximately one Moliere radius wide and 25.8 radiation lengths deep.
 
-    The endcap section (EE) is 314 cm from the IP (*right word?) and covers a pseudorapidity range of 1.479 to 3.0.
-Additionally, a preshower detector (two planes of silicon strip detectors and a lead absorber) sits just inside the grid of lead tungstate crystals.
+        The crystals in each endcap section (EE) are arranged in an x-y grid that starts at |z| = 315 cm and covers a pseudorapidity range of 1.479 to 3.0.
+Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals.
 (*Say what the preshower is for?
@@
 \subsection{Hadronic Calorimeter}
-    The hadronic calorimeter (HCAL) is composed of plastic scintillator interspersed within brass absorber.
-The scintillation light is transferred to readout through wavelength shifting fibres (WLS) that are spliced onto clear fibers (*say what readout means.
-PMT?).
-The scintillator plates are 3.7 mm thick.
-    The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers, each of which ha 15 brass plates and covers an area of 0.087 x 0.087 in eta-phi.
-In addition, a single layer of 10 mm thick scintillator tiles sits just outside the solenoid.
-This extra layer, known as hadron outer (HO), spans a pseudorapidty range of -1.26 to 1.26 and increaes the effective HCAL interaction length to greater than 10.
-    Each endcap consists of 14 towers with five degree phi segmentation and spans a pseudorapidity range of 1.3 to 3.0.
+        (*cite CMS TDR)
+        (*talk about readout?)
+        The hadronic calorimeter (HCAL) uses 3.7mm plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers.
+Embedded wavelength-shifting fibers capture the scintillation light and transfer it to clear fibers so it can eventually be read out by hybrid photodiodes.
+
+        The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers (*check), each of which contains 14 (*check) brass plates and covers an area of 0.087 x 0.087 in eta-phi (*get a feel for this area).
+In addition, an extra layer (or two at eta = 0) of scintillator tiles sits just outside the solenoid.
+This extra layer, known as hadron outer (HO), spans a pseudorapidty range of -1.26 to 1.26 and increases the minimum effective HCAL interaction length to greater than 11.8.
+
+        Each endcap consists spans a pseudorapidity range of 1.3 to 3.0 with 14 towers in eta and 5 to 10 degree phi segmentation.
 Also, a steel and quartz fiber forward calorimeter (HF) sits 11.2 m from the interaction pipe in a pseudorapidty range of 3.0 to 5.0.
 In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline.
-(*say why HF is necessary)
+(*say why HF is useful or mention crazy flux?)
 
 \subsection{Solenoid}
-    CMS employs a 4T superconducting solenoid to aid in the measurement of charged particle momenta.
-The solenoid consists of 2168 turns of Nb-Ti superconducting cable and has an inner diameter of 5.9 m and a length of 12.9 m (*is 5.9 right?
-I see "cold bore = 6.3 m" in "At the CERN LHC").
+        (*cite cms experiment at the cern lhc)
+        CMS employs a 4 T superconducting solenoid to aid in the measurement of charged particle momenta.
+The solenoid consists of 2168 turns of Nb-Ti superconducting cable and has an inner diameter of 6 m and a length of 12.5 m.
 The flux returns through an iron yoke that also houses the muon system.
@@
 \subsection{Muon System}
+        (*cite CMS TDR)
+        (*Specifically mention CMS design specs to meet physics goals?)
         The muon system (MS), which is the outermost subdetector, detects muons with 3 varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps.
-The DTs and CSCs were chosen for the barrel and endcap, respectively, because the neutron-induced background, muon rates, and strength of the magnetic field are all higher in the encap.
+The choice of detector varies between barrel and endcap due to the difference in neutron-induced background, muon rates, and magnetic field strength.
 The RPCs are useful in both the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
-Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines (*quantify).
+Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines (*quantify or show std plot?).
 
         In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at 4.0, 4.9, 5.9, and 7.9 m.
-SAY SOMETHING ABOUT HOW DTS ACTUALLY WORK.
-The maximum drift length is 2 cm and the single point resolution is 200 um.
+(*Say how DT works?) The maximum drift length is 2 cm and the single point resolution is 200 um.
 When reconstructing a vector describing the muon momentum, the phi precision is better than 100 um in position and 1 mrad in direction.
@@
         Each muon endcap detector (ME) is composed of 234 CSCs and 4 RPC stations (*figure out exactly what RPC station means and say that instead).
-Each CSC has six gas gaps with radial cathode strips and nearly perpendicualr planes of anode wires.
-The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, but the slower (*quantify) cathode strip signal provides precise (*quantify) position measurements.
-In the end, the CSC spacial resolution is approximate 200 um and the angular resolution is approximately 10 mrad.
+Each CSC has six gas gaps with radial cathode strips and nearly perpendicualar planes of anode wires.
+The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower (*quantify) cathode strip signal provides precise (*quantify) position measurements.
+All in all, the CSC spacial resolution is approximately 200 um and the angular resolution is approximately 10 mrad.
 
-\subsection{Muon System}
+\subsection{Trigger}
+        (*cite CMS TDR, jinst 12 c03021)
+        (*Is entire detector read out at L1?)
+        (*Mention fpgas in L1 or more details about HLT?)
+        (*Something about particle flow?)
+        (*Sloppy, but I'm getting tired)
         The trigger reduces the data writing rate from the 40 MHz collision rate to less than 1 kHz so that events can be written to tape.
@@
 Maybe object definition?), background estimation, and which data tier to use (*can I say this more generally?).
-This paper will focus on four complementary LLP signatures: displaced vertices, disappearing tracks, stopped particles, and heavy stable charged particles (HSCPs)(*is HSCP a signature?
-say TOF / dE/dx instead?).
+This paper will focus on four complementary LLP signatures: displaced vertices, disappearing tracks, slow-moving particles, and particles that stop completely before decaying.
 
@@
 Displaced vertices searches are sensitive to LLPs that decay to visible (*detectable?
-some other word?) particles in the inner volume (*specify) of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point.
+some other word?) particles in the inner volume (*specify) of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point (*wordy).
 Disappearing tracks searches are sensitive to LLPs that decay to invisible (*neutral?
@@
 
-    HSCP and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
-HSCP searches use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles, which normally (*quantify) have beta > 0.9.
-Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomena that could be possible with long-enough LLP lifetimes and small initial kinetic energy.
-These analyses look (*repetative) for calorimeter energy deposits or hits in the muon system (*too specific for LLP analyses intro?) that are out of time with proton bunch crossings that could be due to stopped particles decaying.
+        Slow and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
+Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles (*redundant), which normally (*quantify) have beta > 0.9.
+Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
+These analyses look for calorimeter energy deposits or hits in the muon system (*too specific for overview?) that are out of time with proton bunch crossings that could be due to the decay of stopped particles.
 
@@
 The next section will look  at a recent example of each analysis type from either ATLAS or CMS.
+
 \subsection{Displaced Vertices}
-    LLPs with lifetimes on the order of ~1 nm (*check this) can decay inside the detector volume, but with a reconstructed vertex far from the nominal interaction point (*last 3 words true?).
-ATLAS performs one such search with large MET and at least one displaced vertex (DV) with large track multiplicity.
-The search is sensitive to long-lived gluinos with lifetimes in the 10 ps to 10 ns range.
+            (*cite CONF-2017-026)
+            LLPs that decay before reaching the inner tracker but still live longer than the vast majority of SM particles can be identified by their displaced vertex (DV).
+That is, a reconstructed vertex far from the nominal interaction point.
+ATLAS performs a search for such particles by looking for at least one DV along with large MET (*has MET been defined yet?) and large track multiplicity.
+The search is sensitive to long-lived gluinos with lifetimes in the 20 ps to 10 ns range.
 
-    LLPs appear in BSM theories such as Hidden Valley models, where the LLP decay is suppressed by a large barrier potential, SUSY models with small R-parity violating couplings, and Split SUSY, where the LLP decay is suppressed by the high virtuality of an intermediate state.
-This search uses a simplified model in the Split SUSY paradigm as a benchmark.
+            This search uses a simplified model in the split SUSY paradigm as a benchmark.
 In the simplified model, gluinos are kinematically accessible while squarks are not.
-The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino.
-Because the squark mass is so high, the gluino lives long enough to form an R-hadron with SM quarks and propogate some measureable distance away from the IP.
+The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino (*diagram?).
+Because the squark mass is so high, the gluino lives long enough to form an R-hadron (*first use.
+Define here if not in LLP section) with SM quarks and propogate some measureable distance away from the IP before decaying.
 
-    Jets and MET are reconstructed as normal in this analysis, but special care must be taken when looking for displaced tracks.
-The standard ATLAS tracking algorithm constrains the transverse and longitudinal impact parameters of potential tracks, so the authors employed an additional algorithm, referred to as large-radius tracking (LRT).
-LRT is run after the standard tracking algorithm and only uses hits that were not used in standard track reconstruction.
+            Jets and MET are reconstructed as in standard analyses, but special care must be taken when looking for displaced tracks.
+The standard ATLAS tracking algorithm constrains the transverse and longitudinal impact parameters of potential tracks, so the authors employ an additional algorithm, referred to as large-radius tracking (LRT).
+LRT is run after the standard tracking algorithm and uses only hits that were not used in standard track reconstruction.
 By relaxing d0, z0, and number of hits requirements, LRT is able to reconstruct tracks that point back to DVs.
+(*should I talk about reconstruction efficiencies?)
 
             Because no SM process will produce events that meet the mass and track multiplicity requirements on the DV, only instrumental backgrounds are considered.
-Specifically, hadronic interactions in detector material, incorrectly combining vertices from short-lived SM particles, and incorrectly adding hits from unrelated tracks to low-mass vertices (*make sure I understand this last one) can all lead to events that mimic the desired signal.
+Specifically, the authors consider hadronic interactions in detector material, incorrectly combined vertices from short-lived SM particles, and incorrectly added hits from unrelated tracks to low-mass vertices.
 
@@
 After a dedicated study, the background from merged vertices was found to be negligable.
-Finally, the background from crossing tracks is treated as an uncertainty in the background estimate that is determined with a model that adds pseudo-tracks to data vertices.
+Finally, the background from crossing tracks is determined with a model that adds pseudo-tracks to data vertices and is normalized by comparing the sample of 3-track vertices in data to (2+1)-track vertices in the model.
 
             After estimating 0.02 +- 0.02 background events, exactly 0 are observed.
-The result is then interpreted as upper limits on the gluino mass and pair-production cross section as a function of gluino lifetime.
-(*Include plots and/or report numbers)
+The result is then interpreted as an upper limit on the gluino mass and pair-production cross section as a function of gluino lifetime.
+For an LSP neutralino mass of 100 GeV, the gluino mass limit is approximately 2000 GeV for lifetimes in the 20 ps to 10 ns range.
+(*Include plots)
 
 \subsection{Disappearing Tracks}
+            (*cite CONF-2017-017)
+            (*nice disappearing track cartoon)
+            (*nice cartoon feynman diagrams of signal processes)
             Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
@@
 The nearly-degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
-The low-momentum pion is then unlikely to be constructed, which results in a disappearing track (*explicitly mention assumed non-interaction of LSP?).
+The low-momentum pion is then unlikely to be constructed, which results in a disappearing track.
 
-    Both ATLAS and CMS looked for disappearing tracks during Run I, but the new trackers installed in ATLAS during LS1 and CMS during the EYETS (*define acronyms) should increase sensitivity to decays at shorter radii (*I haven't mentioned previous iterations when talking about other analyses).
+            Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 and CMS before 2017 should increase sensitivity to decays at shorter radii (*I haven't mentioned previous iterations when talking about other analyses).
 The ALTAS search presented here is sensitie to LLP lifetimes of approximated 10 ps to 10 ns.
@@
             The authors consider two signal processes: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET.
-Process (1) could be the only gaugino production mode at the LHC if the gluino mass to kinematically unaccessable (*check for plagarism and accuracy), but process (2), which leads chargino production in cascade decays,  will be dominant if the gluino mass is within reach.
+Process (1) could be the only gaugino production mode at the LHC if the gluino mass to kinematically unaccessable (*check for plagarism and accuracy), but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
 The ISR jet in process (1) is not physically required; it simply provides something for the gluinos to recoil off of so the MET signal isn't lost (*My interpretation.
-Run it by Andrew, Jamie, or Brian).
+Run it by someone who knows stuff).
 
-    Disappearing tracks canditates, called pixel tracklets, are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard track reconstruction algorithm.
+            Disappearing tracks canditates, called pixel tracklets, are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard reconstruction algorithm.
 The pixel tracklets are required to pass several isolation, pT, and quality requirements such as number of pixel layer hits.
-Finally, the disappearing criteria is enforced by requiring exactly zero assiated hits in the SCT (*SCT = semiconductor tracker = tracking layer after pixel in ATLAS).
-(*Do I need to say anything about signal efficiency?) Event selection requires one pixel tracklet, no electron or muon candidates (to suppress ttbar W/Z+j processes), and the MET and jet requirements associated with either of the two production modes described above.
+Finally, the disappearing criteria is enforced by requiring exactly zero associated hits in the subsequent tracking layer.
+Event selection requires one pixel tracklet, no electron or muon candidates (to suppress ttbar W/Z+j processes), and the MET and jet requirements associated with either of the two production modes described above.
 
-    Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by pixel hits that don't have the proper SCT hits associated to them, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
-These backgrounds come primarily from ttbar and W+j, and estimates for each type of background are obtained from data.
-After constructing control regions for the lepton- and hadron-related backgrounds, the authors extract transfer factors...
-(*I don't understand this.
-Need to work through it).
-The authors estimate the remaining background by defining a control region with large d0 uncertainty that is dominated by pixel tracklets reconstructed from random, unrelated hits.
-After verifying that the pT spectrum of fake pixel tracklets is independent of MET (which defines the signal and control regions), the authors estimate the contribution of this background in the signal region by multiplying the number of signal-region tracklets by the ratio of control-region fake tracklets to total control-region tracklets.
+            Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by pixel hits that don't have the proper hits from the next tracking layer associated to them, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon (*lots of words).
+These backgrounds come primarily from ttbar and W+jets processes, and estimates for each type of background are obtained from data.
+(*I initially wrote a whole big thing about how each bg was estimated, but I'm thinking it was overkill)
 
-    No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass gluon mass plane for the QCD production process (*will be way clearer after texing in sparticle symbols).
-(*Include either plots or \#s)
+            No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass gluon mass plane for the QCD production process (*hopefully will be way clearer after texing in sparticle symbols).
+(*Either include  plots or say numbers)
 
 \subsection{Stopped Particles}
+            (*cite CMS PAS EXO-17-004)
+            (*mention how stopped particles complement HSCP search?)
+            (*Allen talks about trigger efficiency stuff. Is that really important?)
             With long enough lifetimes and sufficient mass, LLPs could actually come to rest in the detector before decaying.
@@
 The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.
-Mchamps will not be discussed further because their existence is not directly motivated by naturalness.
+Mchamps will not be discussed further because their existence is not directly motivated by naturalness (*is this true?).
 
@@
 Beam halo and muon system noise are easily removed by the selection criteria, but distinguishing signal from cosmics requires a more nuanced approach.
-After generating signal MC and modeling cosmics from data obtained in dedicated cosmic runs, the authors found that cosmics and signal could be differentiated using the time-of-flight information from the muon system RPCs and DTs.
+After generating signal MC and modeling cosmics from data obtained in dedicated cosmic runs, the authors found that cosmics and signal could be differentiated using time-of-flight information from the muon system RPCs and DTs.
 Essentially, the direction of muon momentum could be gleaned from the timing information, and the authors required outgoing muons in both the upper and lower hemispheres.
@@
             In addition to the above criteria, the authors developed a new muon reconstruction algorithm, called displaced standalone (DSA), that uses only muon system hits and does not constrain the location of the primary vertex in any way.
-The full selection requires exactly one good DSA track in each hemisphere with pT greater than 50 GeV, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement, such as the minimum number of DT and RPC hits and maximum time measurement uncertainty.
-Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0), minimize background from beam halo and cosmics.
+The full selection requires exactly one good DSA track in each hemisphere with pT greater than 50 GeV, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement.
+Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0) minimize background from beam halo and cosmics.
 
-    After estimating the background by extrapolating data from the cosmic-enriched region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculated the expected background for LLP lifetimes ranging from 10\^-7 to 10\^6 s.
+            After estimating the background by extrapolating data from the cosmic-enriched region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculated the expected background for LLP lifetimes ranging from 100 ns to 1 us.
 In all cases, the expected background was less then one event.
@@
 \subsection{Heavy Stable Charged Particles}
+            (*cite CMS EXO7-010)
+            (*nice dE/dx plot (fig 1))
             Particles that live for more than a couple ns (*Check this and be more exact) will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
@@
 
-    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and q=+-e (*dE/dx plot is nice around here).
-These criteria (tracker dE/dx and and MS TOF) provide two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS depending on the nature of R-hadron's interaction with nuclear matter, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with aritrary electric charge.
-The first two models bear more directly on naturalness and SUSY, so they will be the focus of this presentation.
+            HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and |q|=+-e (*dE/dx plot is nice around here).
+Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with aritrary electric charge.
+This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY.
 
-    (*I should talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta~1.
+            (*I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta~1.
 Zig-zag offset is used to estimate beta.
-Not sure where to fit it in.) (*Also need to talk about tracker-only vs tracker+TOF)
+Not sure where to fit it in.) (*Worth mentioning tracker-only vs tracker+TOF)
 
@@
 By comparing the observed and theoretical limits, the authors also extract mass limits for the gluinos, stops, and staus in various models.
+(*Include plots - table is too big and too many numbers to list)
 
 \section{Experimental Viability of Natural BSM}
+\subsection{Limits Summary}
+\subsection{What makes a SUSY model natural?}
 
-\section{Conclusion}
+\section{Conclusion and Important Searches for 2017}
 

### 2017-07-21 tex/draft_noComments.tex
Initial commit

--- 2017-07-21 tex/draft.tex
@@
 \section{The Standard Model}
-    The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing (*weak word) accuracy (*say 2nd clause better).
-The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces (*maybe put in pre-EWSB terms instead?), and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
+    The standard model of particle physics (SM) describes all known particles and forces (except gravity) and is experimentally verified to astonishing accuracy.
+The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 5 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces, and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
 
-    All SM particles transform according to the gauged symmetry group SU(3)cxSU(2)LxU(1)Y, where SU(3)c is associated with color charge, SU(2)L is associated with weak isospin, and U(1)Y is associated with weak hypercharge.
-The gauge bosons are associated with the generators of these groups, thus there are 8 gluons associated with SU(3)c, 3 W bosons associated with SU(2)L, and 1 B boson associated with U(1)Y.
-The fermions are catagorized by which representation of each group they fit into.
-For example, SU(3)c distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and SU(2)L distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
-Finally, different values of weak hypercharge further distignuish SM particles according to a linear combination of their weak isospin and electric charge (*is there some more fundamental way to describe Y?).
+    The SM particles fit into multiplets of three symmetry groups, which makes the SM an SU(3)cxSU(2)LxSU(1)Y theory.
+These three symmetry groups correspond to color, the charge associated with the strong nuclear force; weak isospin, the charge associated with the left-handed chiral doublet something something; and weak hypercharge, the something something something, respectively.
 
-    The Higgs potential has a nonzero vacuum expectation value (VEV), which spontaneously breaks SU(2)LxU(1)Y to U(1)EM while leaving SU(3)c unscathed.
-Once the dust settles, the B and 3 W bosons have been mixed to produce the W+, W-, Z bosons that mediate the weak force and the photon that mediates electromagnetism.
-3 of the 4 generators are broken in the process, leaving 3 extra degrees of freedom that ultimately become the masses of the W+, W-, and Z bosons while the remaining symmetry is associated with electric charge.
-Furthermore, expanding the Higgs field about its VEV produces mass terms for the quarks and charged leptons, thus giving mass to all massive SM particles.
-(*probably show a little math)
+    The Higgs potential has a nonzero vacuum expectation value (VEV), which spontaneously breaks the SU(2)LxU(1)Y symmetry to a U(1)EM symmetry.
+Breaking 3 of the 4 generators leaves 3 extra degrees of freedom, which ultimately become the masses of the W+, W-, and Z bosons, while the remaining degree of freedom is associated with electric charge and the massless photon.
+Expanding the Higgs field about its VEV and picking a gauge produces quark and charged lepton mass terms in the SM Lagrangian.
+In this way, spontaneous symmetry breaking of the Higgs field gives mass to all massive SM particles.
 
-    (*kinda funny wording throughout. Maybe it would be better to trade some words for math?)
-    All SM particles interact with virtual particles through loop interactions.
-These interactions lead to corrections to SM parameters such as particle masses.
-It is common to write a given parameter as a linear combination of its 'bare' (uncorrected) value and its corrections.
-As the only fundamental scalar in SM, the Higgs is uniquely affected by these corrections.
-The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the Higgs bare mass and the terms that correct it.
+    Like the mass of all SM particles, the Higgs mass is affected by interactions with virtual particles through loop processes.
+As the only fundamental scalar in the theory, however, the Higgs sees corrections to its mass that depend quadratically on the cutoff scale of the SM.
+To show this dependence on loop corrections, SM masses are often written as power series, where the first term is the bare (uncorrected) mass and the following terms are due to loop corrections.
+The next section will explore the concept of naturalness, a major motivating principle in beyond the SM (BSM) physics, that is directly tied to the relationship between a particle's bare mass and the terms that correct it.
 
@@
     The naturalness criterion takes several forms.
-Here are a few (*cite these): (1) all parameters in a model should be of order 1, (2) Loop-level contributions should not be larger than tree-level contributions, (3) any small parameter should be protected by a custodial symmetry, and (4) fine-tuning is bad (*probably a better way to say 4).
+Here are a few: (1) all parameters in a model should be of order 1, (2) Loop-level contributions should not be larger than tree-level contributions, (3) any small parameter should be protected by a custodial symmetry, and (4) fine-tuning is bad.
 Although these statements are all trying to get at the same fundamental notion, I find (3) and (4) to be most compelling.
 
-    (*cite guidice naturally and t'hooft naturalness)
     Let's look at (3).
@@
 This situation contrasts that of the fermions and gauge bosons, whose masses are kept small by custodial symmetries.
-That is, the SM would be more symmetric (*weird wording?) if fermions and gauge bosons were massless.
-Specifically, massless fermions would have an extra U(1)xU(1) chiral symmetry, and massless vector bosons would have an extra gauge symmetry (*?!?!?!).
-The Higgs, a fundamental scalar, has no such symmetry (*repetative) so we deem its low mass to be unnatural.
-(*explain why fundamental scalars have no custodial symmetry?
-I certainly better learn why.)
+That is, the SM would be more symmetric if fermions and gauge bosons were massless.
+Specifically, massless fermions would have an extra U(1)xU(1) chiral symmetry, and massless vector bosons would have an extra gauge symmetry.
+The Higgs, a fundamental scalar, has no such symmetry so we deem its low mass to be unnatural.
 
@@
 
-    (*probably doesn't need to be in final paper, but I'd like to check my basic understanding with Jamie, et al)
     There are other unnatural quantities that people worry about in physics.
@@
 The degree of violation is parameterized as thetaQCD, which recasts the problem into the naturalness context of 'why is thetaQCD so small?'.
-The cosmological constant is experimentally ~60 to ~120 orders of magnitude smaller than the predicted value (*predicted how?).
+The cosmological constant is experimentally ~60 to ~120 orders of magnitude smaller than the predicted value.
 While these issues deserve serious attention, they will not be considered further here.
 
-    (*talk about anthropic principle or other arguments against?)
-    (*I got tired of reading this section and haven't edited this paragraph at all yet)
     There are a few proposed solutions to the SM naturalness problem.
@@
 Composite Higgs models propose that the Higgs stops behaving as a fundamental scalar at some energy level, which removes the quadratic dependence.
-(*Hidden valley, dark sector, little Higgs?)
 
 \section{SUSY and LLPs}
-    (*is there a way to move the naming stuff elsewhere or shorten it?)
     SUSY introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between fermions and bosons.
-In it's simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson (*and an extra Higgs field - can I gloss over that?).
+In it's simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson.
 The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
@@
 Together the superpartners to the SM particles are known as sparticles.
-Because fermion loops come with a relative minus sign (*there must be a better way to say that), every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
+Because fermion loops come with a relative minus sign, every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
 If supersymmetry were exact, the bare Higgs mass would be uncorrected to all orders in perturbation theory.
@@
 
-    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and (*and/or?) produce a signal that could be missed by common SUSY search techniques.
+    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and produce a signal that could be missed by common SUSY search techniques.
 Specifically, we are interested in SUSY models that predict LLPs.
-That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point, which includes everything from particles that decay at (*give ballparky number (~100um?)) to particles that propagate through the entire detector.
+That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point, which includes everything from particles that decay at to particles that propagate through the entire detector.
 
@@
 In the SM, the electron and proton are the lightest particles carrying electric charge and baryon number, respectively, which leads to their absolute stability through charge and baryon number conservation.
-Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay (*also mention that they're both weak decays?).
-(*Mention neutrino, pion, kaon, whatever other bound state I might be forgetting?)
+Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay.
 
     In SUSY models, LLPs arise for the same basic reasons, and many different SUSY models meet different LLP criteria in different ways.
-The most common (*based on my assumptions) SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from predicting proton decay.
-In models with R-parity, the SM particles have R-parity +1 (*double check this explanation) and their superpartners have R-parity -1.
-Conserving overall R-parity (*specifically the product; does overall mean that?) at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is an absolutely stable LLP.
+The most common SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from predicting proton decay.
+In models with R-parity, the SM particles have R-parity +1 and their superpartners have R-parity -1.
+Conserving overall R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is an absolutely stable LLP.
 The second phenomenon is the main motivation behind using missing energy as the typical SUSY seach signature.
 
-    In models with R-parity violation (RPV), LLPs can be produced when the RPV terms have small coupling constants, which leads to long-lived, but not perfectly stable, LSPs (*any way non-LSPs could be long-lived for this reason too?).
+    In models with R-parity violation (RPV), LLPs can be produced when the RPV terms have small coupling constants, which leads to long-lived, but not perfectly stable, LSPs.
 Luckily, RPV models can still avoid proton decay by only allowing terms that violate either baryon number or lepton number but not both.
 A similar situation arises in GMSB models where the gravitino is the LSP.
-The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs(*do I need to explain GMSB here?).
-(*cite dimopoulos low energy)
+The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs.
 
@@
 In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark.
-(*cite kilian) (*mention that split throws out naturalness motivation?)
 
     SUSY models with degenerate sparticle spectra can have increased sparticle lifetimes from the reduced phase space for decays.
-In some AMSB models (*be more specific), for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
+In some AMSB models, for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
 The wino's lifetime, then, is increased by the lack of phase space in which to decay.
-(*cite R\&S out of this world)
-    (*merge last 2 paragraphs under 'mass spectra lead to LLP' concept?)
-    (*never said anything about hidden valley or dark sector stuff. Never said the word R-hadron. Never said stealth or displaced SUSY. Should I?)
 
@@
 \subsection{Overview}
-        (*cite cms experiment at the cern lhc)
           The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from 14 TeV proton-proton collisions at the Large Hadron Collider (LHC).
@@
 \subsection{Tracker}
-        (*cite CMS TDR, jinst 12 c02033)
-        (*maybe I should trade some number listing for talking about how silicon detectors work)
-        (*what about readout, cooling, etc?)
-        In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint (*too flowery?) primary and secondary vertices.
-The tracker is subdivided into two regions: at r < 20 cm, the high particle flux (*specify) requires smaller pixels to keep occupancy near 0.1\%.
+        In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
+The tracker is subdivided into two regions: at r < 20 cm, the high particle flux requires smaller pixels to keep occupancy near 0.1\%.
 Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
@@
         Just outside the pixel tracker, the silicon strip tracker (SST) occupies the 20 < r < 116 cm and |z| < 282 cm region of CMS.
-Composed of 9.3 million silicon strips that vary from \_ to \_ in size (*look up) depending on particle flux, the SST covers an active area of roughly 196 m\^2.
-At each trigger, the strip output voltage is transferred via optical link to be read out by off-detector front-end electronics (*right language?).
+Composed of 9.3 million silicon strips that vary from \_ to \_ in size depending on particle flux, the SST covers an active area of roughly 196 m\^2.
+At each trigger, the strip output voltage is transferred via optical link to be read out by off-detector front-end electronics.
 
 \subsection{Electromagnetic Calorimeter}
-        (*cite CMS TDR)
-        (*talk about readout?)
-        (*More in the way of concept/how stuff works?)
         Moving outward, the electromagnetic calorimeter (ECAL) follows the inner tracker.
 As a homogeneous scintillation calorimeter, ECAL uses 61200 lead tunstate crystals in the barrel and 7324 in each endcap to reconstruct the energy deposited during electromagnetic showers.
-Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere length = 2.2 cm), and radiation hard (up to 10 Mrad(*learn context for this number)) calorimeter.
-The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields (*say B-field part better).
+Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere length = 2.2 cm), and radiation hard (up to 10 Mrad) calorimeter.
+The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields.
 
-        The barrel section (EB) extends radially from 129 to 177 (*look up) cm and covers a pseudorapidity range of 0 to 1.479.
+        The barrel section (EB) extends radially from 129 to 177 cm and covers a pseudorapidity range of 0 to 1.479.
 The crystals are tapered to approximately project back to the IP but not so perfectly that particle trajectories would be likely to align with cracks.
@@
 Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals.
-(*Say what the preshower is for?
-Is it for pi0 rejection?
-If so, how and why?)
 
 \subsection{Hadronic Calorimeter}
-        (*cite CMS TDR)
-        (*talk about readout?)
         The hadronic calorimeter (HCAL) uses 3.7mm plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers.
@@
 
-        The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers (*check), each of which contains 14 (*check) brass plates and covers an area of 0.087 x 0.087 in eta-phi (*get a feel for this area).
+        The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers, each of which contains 14 brass plates and covers an area of 0.087 x 0.087 in eta-phi.
 In addition, an extra layer (or two at eta = 0) of scintillator tiles sits just outside the solenoid.
@@
 In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline.
-(*say why HF is useful or mention crazy flux?)
 
 \subsection{Solenoid}
-        (*cite cms experiment at the cern lhc)
         CMS employs a 4 T superconducting solenoid to aid in the measurement of charged particle momenta.
@@
 The flux returns through an iron yoke that also houses the muon system.
-The significant (*quantify?) bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of 10\% for muons up to 1 TeV.
+The significant bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of 10\% for muons up to 1 TeV.
 
 \subsection{Muon System}
-        (*cite CMS TDR)
-        (*Specifically mention CMS design specs to meet physics goals?)
         The muon system (MS), which is the outermost subdetector, detects muons with 3 varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps.
@@
 The RPCs are useful in both the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
-Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines (*quantify or show std plot?).
+Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines.
 
         In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at 4.0, 4.9, 5.9, and 7.9 m.
-(*Say how DT works?) The maximum drift length is 2 cm and the single point resolution is 200 um.
+The maximum drift length is 2 cm and the single point resolution is 200 um.
 When reconstructing a vector describing the muon momentum, the phi precision is better than 100 um in position and 1 mrad in direction.
 
-        Each muon endcap detector (ME) is composed of 234 CSCs and 4 RPC stations (*figure out exactly what RPC station means and say that instead).
+        Each muon endcap detector (ME) is composed of 234 CSCs and 4 RPC stations.
 Each CSC has six gas gaps with radial cathode strips and nearly perpendicualar planes of anode wires.
-The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower (*quantify) cathode strip signal provides precise (*quantify) position measurements.
+The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower cathode strip signal provides precise position measurements.
 All in all, the CSC spacial resolution is approximately 200 um and the angular resolution is approximately 10 mrad.
@@
 \subsection{Trigger}
-        (*cite CMS TDR, jinst 12 c03021)
-        (*Is entire detector read out at L1?)
-        (*Mention fpgas in L1 or more details about HLT?)
-        (*Something about particle flow?)
-        (*Sloppy, but I'm getting tired)
         The trigger reduces the data writing rate from the 40 MHz collision rate to less than 1 kHz so that events can be written to tape.
@@
         LLPs leave distinct signatures that differentiate LLP signals from SM backgrounds but also add complexity to LLP analyses.
-CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to veer off the traditional analysis path in terms of object reconstruction (*really reconstruction?
-Maybe object definition?), background estimation, and which data tier to use (*can I say this more generally?).
+CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to veer off the traditional analysis path in terms of object reconstruction, background estimation, and which data tier to use.
 This paper will focus on four complementary LLP signatures: displaced vertices, disappearing tracks, slow-moving particles, and particles that stop completely before decaying.
 
-        Displaced vertices and disappearing tracks both look for particles that are unstable on detector timescales (*quantify?).
-Displaced vertices searches are sensitive to LLPs that decay to visible (*detectable?
-some other word?) particles in the inner volume (*specify) of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point (*wordy).
-Disappearing tracks searches are sensitive to LLPs that decay to invisible (*neutral?
-some other word?) particles along with particles that are too soft to be reconstructed.
+        Displaced vertices and disappearing tracks both look for particles that are unstable on detector timescales.
+Displaced vertices searches are sensitive to LLPs that decay to visible particles in the inner volume of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point.
+Disappearing tracks searches are sensitive to LLPs that decay to invisible particles along with particles that are too soft to be reconstructed.
 Together, these two types of analyses cover something something parameter space of LLPs that decay on detector timescales.
@@
         Slow and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
-Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles (*redundant), which normally (*quantify) have beta > 0.9.
+Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles, which normally have beta > 0.9.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
-These analyses look for calorimeter energy deposits or hits in the muon system (*too specific for overview?) that are out of time with proton bunch crossings that could be due to the decay of stopped particles.
+These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings that could be due to the decay of stopped particles.
 
@@
 \subsection{Displaced Vertices}
-            (*cite CONF-2017-026)
             LLPs that decay before reaching the inner tracker but still live longer than the vast majority of SM particles can be identified by their displaced vertex (DV).
 That is, a reconstructed vertex far from the nominal interaction point.
-ATLAS performs a search for such particles by looking for at least one DV along with large MET (*has MET been defined yet?) and large track multiplicity.
+ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity.
 The search is sensitive to long-lived gluinos with lifetimes in the 20 ps to 10 ns range.
@@
 In the simplified model, gluinos are kinematically accessible while squarks are not.
-The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino (*diagram?).
-Because the squark mass is so high, the gluino lives long enough to form an R-hadron (*first use.
-Define here if not in LLP section) with SM quarks and propogate some measureable distance away from the IP before decaying.
+The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino.
+Because the squark mass is so high, the gluino lives long enough to form an R-hadron with SM quarks and propogate some measureable distance away from the IP before decaying.
 
@@
 By relaxing d0, z0, and number of hits requirements, LRT is able to reconstruct tracks that point back to DVs.
-(*should I talk about reconstruction efficiencies?)
 
@@
 For an LSP neutralino mass of 100 GeV, the gluino mass limit is approximately 2000 GeV for lifetimes in the 20 ps to 10 ns range.
-(*Include plots)
 
 \subsection{Disappearing Tracks}
-            (*cite CONF-2017-017)
-            (*nice disappearing track cartoon)
-            (*nice cartoon feynman diagrams of signal processes)
             Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
@@
 
-            Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 and CMS before 2017 should increase sensitivity to decays at shorter radii (*I haven't mentioned previous iterations when talking about other analyses).
+            Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 and CMS before 2017 should increase sensitivity to decays at shorter radii.
 The ALTAS search presented here is sensitie to LLP lifetimes of approximated 10 ps to 10 ns.
@@
             The authors consider two signal processes: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET.
-Process (1) could be the only gaugino production mode at the LHC if the gluino mass to kinematically unaccessable (*check for plagarism and accuracy), but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
-The ISR jet in process (1) is not physically required; it simply provides something for the gluinos to recoil off of so the MET signal isn't lost (*My interpretation.
-Run it by someone who knows stuff).
+Process (1) could be the only gaugino production mode at the LHC if the gluino mass to kinematically unaccessable, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
+The ISR jet in process (1) is not physically required; it simply provides something for the gluinos to recoil off of so the MET signal isn't lost.
 
@@
 
-            Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by pixel hits that don't have the proper hits from the next tracking layer associated to them, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon (*lots of words).
+            Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by pixel hits that don't have the proper hits from the next tracking layer associated to them, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
 These backgrounds come primarily from ttbar and W+jets processes, and estimates for each type of background are obtained from data.
-(*I initially wrote a whole big thing about how each bg was estimated, but I'm thinking it was overkill)
 
-            No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass gluon mass plane for the QCD production process (*hopefully will be way clearer after texing in sparticle symbols).
-(*Either include  plots or say numbers)
+            No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass gluon mass plane for the QCD production process.
 
 \subsection{Stopped Particles}
-            (*cite CMS PAS EXO-17-004)
-            (*mention how stopped particles complement HSCP search?)
-            (*Allen talks about trigger efficiency stuff. Is that really important?)
             With long enough lifetimes and sufficient mass, LLPs could actually come to rest in the detector before decaying.
 The eventual decay would then lead to energy deposits in the calorimeters or hits in the muon system that could be out of time with proton bunch crossings.
-A recent CMS analysis looked for such a signal in dimuon final states (*necessarily dimuon?) using the full 2015 and 2016 datasets.
+A recent CMS analysis looked for such a signal in dimuon final states using the full 2015 and 2016 datasets.
 
@@
 The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.
-Mchamps will not be discussed further because their existence is not directly motivated by naturalness (*is this true?).
+Mchamps will not be discussed further because their existence is not directly motivated by naturalness.
 
@@
 After unblinding, the observed number of events is exactly zero in every lifetime scenerio.
-These results are then interpreted as upper limits on the signal production cross section (*include limit plots or table), which are the first limits for stopped particles that decay to muons at the LHC.
+These results are then interpreted as upper limits on the signal production cross section, which are the first limits for stopped particles that decay to muons at the LHC.
 
 \subsection{Heavy Stable Charged Particles}
-            (*cite CMS EXO7-010)
-            (*nice dE/dx plot (fig 1))
-            Particles that live for more than a couple ns (*Check this and be more exact) will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
+            Particles that live for more than a couple ns will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
 If such a particle is also sufficiently massive, it can be catigorized as a heavy stable charged particle (HSCP).
@@
 
-            HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and |q|=+-e (*dE/dx plot is nice around here).
+            HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and |q|=+-e.
 Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with aritrary electric charge.
 This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY.
-
-            (*I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta~1.
-Zig-zag offset is used to estimate beta.
-Not sure where to fit it in.) (*Worth mentioning tracker-only vs tracker+TOF)
 
@@
 
-            The authors estimate the signal-region background using and ABCD method in which events are binned in a 2D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region (*Do I need to explain this?
-If I do, I should be more clear).
+            The authors estimate the signal-region background using and ABCD method in which events are binned in a 2D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region.
 Systematic uncertainties are introduced in background estimation, signal acceptance, and integrated luminosity.
@@
 By comparing the observed and theoretical limits, the authors also extract mass limits for the gluinos, stops, and staus in various models.
-(*Include plots - table is too big and too many numbers to list)
 

### 2017-07-21 tex/draft.tex
Light edit of whole thing

@@
 It is common to write a given parameter as a linear combination of its 'bare' (uncorrected) value and its corrections.
-As the only fundamental scalar in SM, the Higgs is uniquely affected by these corrections.
+As the only fundamental scalar in the SM, the Higgs is uniquely affected by these corrections.
 The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the Higgs bare mass and the terms that correct it.
@@
 Here are a few (*cite these): (1) all parameters in a model should be of order 1, (2) Loop-level contributions should not be larger than tree-level contributions, (3) any small parameter should be protected by a custodial symmetry, and (4) fine-tuning is bad (*probably a better way to say 4).
-Although these statements are all trying to get at the same fundamental notion, I find (3) and (4) to be most compelling.
+Although these statements are all motivated by the samefundamental notion, I find (3) and (4) to be most compelling.
 
@@
     There are a few proposed solutions to the SM naturalness problem.
-Supersymmetry (SUSY) is the main one, and I'll spend the great majority of my time on it.
+Supersymmetry is the main one, and I'll spend the great majority of my time on it.
 Extra dimensions and composite Higgs models are the other two that pop up fairly often, but won't spend much time on them outside the next two sentences.
@@
 
-\section{SUSY and LLPs}
-    (*is there a way to move the naming stuff elsewhere or shorten it?)
-    SUSY introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between fermions and bosons.
+\section{Supersymmetry}
+    Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions.
 In it's simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson (*and an extra Higgs field - can I gloss over that?).
@@
 Together the superpartners to the SM particles are known as sparticles.
-Because fermion loops come with a relative minus sign (*there must be a better way to say that), every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
-If supersymmetry were exact, the bare Higgs mass would be uncorrected to all orders in perturbation theory.
 
-    Experimental evidence shows that SUSY must be broken, however, because no superpartners have been found, and exact SUSY requires each superpartner to have the same mass as its standard model counterpart.
+    When calculating contributions from loop diagrams, one finds that fermion loops differ in sign from boson loops, which means that in SUSY every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
+In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory.
+(*show example diagram with contribution?)
+
+    But the lack of sparticles in collider searches and everyday life tells us that SUSY must be broken.
+If SUSY were exact, every superpartner would have the exact same mass as its SM counterpart, which means all sparticles would have been found at the same energy scales as SM particles.
 The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenemena.
-A handful of models with particular approaches to SUSY breaking that are particularly prominant or particularly relevant to naturalness or long-lived particles (LLPs) are gauge-mediated susy breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), split SUSY, and R-parity violating SUSY (RPV).
+A handful of models with particular approaches to SUSY breaking that are particularly prominant or particularly relevant to naturalness or long-lived particles are gauge-mediated susy breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating SUSY (RPV).
 The details of these models will be explored as needed throughout this paper.
 
+\section{Long-lived Particles}
     The SUSY variants most relevant to this discussion are those that are motivated by naturalness and (*and/or?) produce a signal that could be missed by common SUSY search techniques.
-Specifically, we are interested in SUSY models that predict LLPs.
-That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point, which includes everything from particles that decay at (*give ballparky number (~100um?)) to particles that propagate through the entire detector.
+Specifically, we are interested in SUSY models that predict long-lived particles (LLPs).
+That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
+This category includes everything from particles that decay at (*give ballparky number (~100um?)) to particles that propagate through the entire detector.
 
-    In both the SM and in BSM theories, LLPs result from one of the following: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
-In the SM, the electron and proton are the lightest particles carrying electric charge and baryon number, respectively, which leads to their absolute stability through charge and baryon number conservation.
+    In the SM and in BSM theories, LLPs result from one of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
+In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the the lightest particles carrying their respective conserved quantities.
 Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay (*also mention that they're both weak decays?).
-(*Mention neutrino, pion, kaon, whatever other bound state I might be forgetting?)
+(*Mention neutrino, pion, kaon, some other bound state I might be forgetting?)
 
-    In SUSY models, LLPs arise for the same basic reasons, and many different SUSY models meet different LLP criteria in different ways.
-The most common (*based on my assumptions) SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from predicting proton decay.
-In models with R-parity, the SM particles have R-parity +1 (*double check this explanation) and their superpartners have R-parity -1.
-Conserving overall R-parity (*specifically the product; does overall mean that?) at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is an absolutely stable LLP.
-The second phenomenon is the main motivation behind using missing energy as the typical SUSY seach signature.
+    In SUSY models, LLPs arise for the same basic reasons, and different SUSY models meet different LLP criteria in different ways.
+The most common (*based on my assumptions) SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from proton decay.
+In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1.
+Conserving the product of R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
+A neutral LSP could show up in collider searches as significant missing energy, making MET the conventional SUSY signature in many searches.
 
-    In models with R-parity violation (RPV), LLPs can be produced when the RPV terms have small coupling constants, which leads to long-lived, but not perfectly stable, LSPs (*any way non-LSPs could be long-lived for this reason too?).
-Luckily, RPV models can still avoid proton decay by only allowing terms that violate either baryon number or lepton number but not both.
+    On the other hand, models with R-parity violation (RPV) produce long-lived, but not perfectly stable LSPs when RPV terms have small coupling constants.
+Luckily, RPV models can still avoid proton decay by allowing either terms that violate baryon number or terms that violate lepton number, but not both.
 A similar situation arises in GMSB models where the gravitino is the LSP.
-The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs(*do I need to explain GMSB here?).
-(*cite dimopoulos low energy)
+The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs.
+(*is now a good time to explain GMSB?)(*cite dimopoulos low energy)
 
-    LLPs from highly-virtual intermediate particles can occur in models such as split (or mini-split) SUSY, where the scalar sparticles are significantly more massive than the gauginos.
+    LLPs from highly-virtual intermediate particles can occur in models such as split SUSY, where the scalar sparticles are significantly more massive than the gauginos.
 In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark.
@@
 
-    SUSY models with degenerate sparticle spectra can have increased sparticle lifetimes from the reduced phase space for decays.
-In some AMSB models (*be more specific), for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
-The wino's lifetime, then, is increased by the lack of phase space in which to decay.
+    The degenerate mass spectra of other SUSY models can also give rise to LLPs.
+In some AMSB models (*explain AMSB?), for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
+The wino then becomes long-lived when its decay is suppressed by the lack of available phase space.
 (*cite R\&S out of this world)
@@
     (*what about readout, cooling, etc?)
-        In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint (*too flowery?) primary and secondary vertices.
-The tracker is subdivided into two regions: at r < 20 cm, the high particle flux (*specify) requires smaller pixels to keep occupancy near 0.1\%.
+    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
+The tracker is subdivided into two regions: at r < 20 cm, the high particle flux (*specify) requires small pixels to keep occupancy near 0.1\%.
 Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
@@
     Just outside the pixel tracker, the silicon strip tracker (SST) occupies the 20 < r < 116 cm and |z| < 282 cm region of CMS.
-Composed of 9.3 million silicon strips that vary from \_ to \_ in size (*look up) depending on particle flux, the SST covers an active area of roughly 196 m\^2.
-At each trigger, the strip output voltage is transferred via optical link to be read out by off-detector front-end electronics (*right language?).
+Composed of 9.3 million silicon strips that vary from \_ to \_ in size (*look up) depending on particle flux in the region, the SST covers an active area of roughly 196 m\^2.
+At each trigger, the strip output voltage is transferred via optical link to be read out by off-detector front-end electronics (*right jargon?).
 
@@
     (*More in the way of concept/how stuff works?)
-        Moving outward, the electromagnetic calorimeter (ECAL) follows the inner tracker.
+    After traversing the inner tracker, a particle would next encounter the electromagnetic calorimeter (ECAL).
 As a homogeneous scintillation calorimeter, ECAL uses 61200 lead tunstate crystals in the barrel and 7324 in each endcap to reconstruct the energy deposited during electromagnetic showers.
@@
     The barrel section (EB) extends radially from 129 to 177 (*look up) cm and covers a pseudorapidity range of 0 to 1.479.
-The crystals are tapered to approximately project back to the IP but not so perfectly that particle trajectories would be likely to align with cracks.
+The crystals are tapered to approximately project back to the IP but not so perfectly that likely particle trajectories align with cracks.
 Each crystal is approximately one Moliere radius wide and 25.8 radiation lengths deep.
@@
 
-        Each endcap consists spans a pseudorapidity range of 1.3 to 3.0 with 14 towers in eta and 5 to 10 degree phi segmentation.
+    Each endcap spans a pseudorapidity range of 1.3 to 3.0 with 14 towers in eta and 5 to 10 degree phi segmentation.
 Also, a steel and quartz fiber forward calorimeter (HF) sits 11.2 m from the interaction pipe in a pseudorapidty range of 3.0 to 5.0.
@@
 The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT).
-The HLT uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, ET, and mu) and uses custom electronics to reduce the rate to ~100 kHz in 3.8 us.
-The HLT then uses a dedicated processor farm to reduce the rate to the desired < 1 kHz.
+L1 uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, MET, and mu) and uses custom electronics to reduce the rate to ~100 kHz in 3.8 us.
+The HLT then uses a dedicated processor farm to further reduce the rate to the desired < 1 kHz.
 
@@
     LLPs leave distinct signatures that differentiate LLP signals from SM backgrounds but also add complexity to LLP analyses.
-CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to veer off the traditional analysis path in terms of object reconstruction (*really reconstruction?
+CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to stray from the traditional analysis path in terms of object reconstruction (*really reconstruction?
 Maybe object definition?), background estimation, and which data tier to use (*can I say this more generally?).
@@
     Displaced vertices and disappearing tracks both look for particles that are unstable on detector timescales (*quantify?).
-Displaced vertices searches are sensitive to LLPs that decay to visible (*detectable?
-some other word?) particles in the inner volume (*specify) of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point (*wordy).
-Disappearing tracks searches are sensitive to LLPs that decay to invisible (*neutral?
-some other word?) particles along with particles that are too soft to be reconstructed.
-Together, these two types of analyses cover something something parameter space of LLPs that decay on detector timescales.
+Displaced vertices searches are sensitive to LLPs that decay to visible particles in the inner volume (*specify) of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point (*wordy).
+Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed.
+Together, these two types of analyses cover (*something something) parameter space of LLPs that decay on detector timescales.
 
@@
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
-These analyses look for calorimeter energy deposits or hits in the muon system (*too specific for overview?) that are out of time with proton bunch crossings that could be due to the decay of stopped particles.
+These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings that could be due to the decay of stopped particles.
 
@@
     (*cite CONF-2017-026)
-            LLPs that decay before reaching the inner tracker but still live longer than the vast majority of SM particles can be identified by their displaced vertex (DV).
+    LLPs that decay before reaching the inner tracker but still live longer than the vast majority of SM particles can be identified with a displaced vertex (DV).
 That is, a reconstructed vertex far from the nominal interaction point.
-ATLAS performs a search for such particles by looking for at least one DV along with large MET (*has MET been defined yet?) and large track multiplicity.
-The search is sensitive to long-lived gluinos with lifetimes in the 20 ps to 10 ns range.
+ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity.
+The search is sensitive to LLPs with lifetimes in the 20 ps to 10 ns range.
 
@@
     Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 and CMS before 2017 should increase sensitivity to decays at shorter radii (*I haven't mentioned previous iterations when talking about other analyses).
-The ALTAS search presented here is sensitie to LLP lifetimes of approximated 10 ps to 10 ns.
+The ALTAS search presented here is sensitive to LLP lifetimes of approximated 10 ps to 10 ns (*make sure I'm talking about lifetime sensitivity in the same way across analyses).
 
     The authors consider two signal processes: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET.
-Process (1) could be the only gaugino production mode at the LHC if the gluino mass to kinematically unaccessable (*check for plagarism and accuracy), but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
+Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically unaccessable, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
 The ISR jet in process (1) is not physically required; it simply provides something for the gluinos to recoil off of so the MET signal isn't lost (*My interpretation.
@@
     (*mention how stopped particles complement HSCP search?)
-            (*Allen talks about trigger efficiency stuff. Is that really important?)
-            With long enough lifetimes and sufficient mass, LLPs could actually come to rest in the detector before decaying.
+    (*too redundant with overview?)
+    With long enough lifetimes and sufficient mass, LLPs could come to rest in the detector before decaying.
 The eventual decay would then lead to energy deposits in the calorimeters or hits in the muon system that could be out of time with proton bunch crossings.
@@
 The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.
-Mchamps will not be discussed further because their existence is not directly motivated by naturalness (*is this true?).
 
@@
 
-            HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and |q|=+-e (*dE/dx plot is nice around here).
+    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and \|q\|=+-e (*dE/dx plot is nice around here).
 Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with aritrary electric charge.
@@
 
-            The authors estimate the signal-region background using and ABCD method in which events are binned in a 2D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region (*Do I need to explain this?
+    The authors estimate the signal-region background using an ABCD method in which events are binned in a 2D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region (*Do I need to explain this?
 If I do, I should be more clear).

### 2017-07-21 tex/draft.tex
Rewrote naturalness, minor edits elsewhere

@@
 
+\usepackage[draft]{fixme}
+\fxsetup{layout=footnote, marginclue}
 \usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref}
@@
 \section{The Standard Model}
-    The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing (*weak word) accuracy (*say 2nd clause better).
-The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces (*maybe put in pre-EWSB terms instead?), and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
+    The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing \fxnote{weak word} accuracy.
+The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces, and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
 
@@
 For example, SU(3)c distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and SU(2)L distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
-Finally, different values of weak hypercharge further distignuish SM particles according to a linear combination of their weak isospin and electric charge (*is there some more fundamental way to describe Y?).
+Finally, different values of weak hypercharge further distignuish SM particles according to a linear combination of their weak isospin and electric charge \fxnote{is there some more fundamental way to describe Y?}.
 
@@
 Furthermore, expanding the Higgs field about its VEV produces mass terms for the quarks and charged leptons, thus giving mass to all massive SM particles.
-(*probably show a little math)
+\fxnote{probably show a little math}
 
-    (*kinda funny wording throughout. Maybe it would be better to trade some words for math?)
+    \fxnote{kinda funny wording throughout. Maybe it would be better to trade some words for math?}
     All SM particles interact with virtual particles through loop interactions.
@@
 \section{Naturalness and the Higgs mass}
-    The naturalness criterion takes several forms.
-Here are a few (*cite these): (1) all parameters in a model should be of order 1, (2) Loop-level contributions should not be larger than tree-level contributions, (3) any small parameter should be protected by a custodial symmetry, and (4) fine-tuning is bad (*probably a better way to say 4).
-Although these statements are all motivated by the samefundamental notion, I find (3) and (4) to be most compelling.
+    \fxnote{cite guidice naturally and t'hooft naturalness}
+    \fxnote{Haven't specifically said 'hierarchy problem. Is that bad?}
+    \fxnote{Never really talked about the effective theory concept or dimensional analysis}
+    The naturalness criterion can be stated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order 1, (2) An effective theory should not be sensitive to small variations in the parameters of higher-energy theory, and (3) any dimensionless parameter much smaller than 1 must be protected by a custodial symmetry.
+When applied to the Higgs mass, naturalness leads to what's known as the 'hierarchy problem' or unacceptable levels of 'fine tuning'.
+These issues are unpacked below.
 
-    (*cite guidice naturally and t'hooft naturalness)
-    Let's look at (3).
-In the SM, the small parameter of interest is the Higgs mass, which has no custodial symmetry to hold it down.
-This situation contrasts that of the fermions and gauge bosons, whose masses are kept small by custodial symmetries.
-That is, the SM would be more symmetric (*weird wording?) if fermions and gauge bosons were massless.
-Specifically, massless fermions would have an extra U(1)xU(1) chiral symmetry, and massless vector bosons would have an extra gauge symmetry (*?!?!?!).
-The Higgs, a fundamental scalar, has no such symmetry (*repetative) so we deem its low mass to be unnatural.
-(*explain why fundamental scalars have no custodial symmetry?
-I certainly better learn why.)
+    Experimentally, the mass of the Higgs boson is 125 GeV, a value that must be achieved by a linear combination of the bare mass and loop diagram corrections.
+The scale of the loop corrections is proportional to the square of the cutoff scale of the SM, which is the highest energy at which the SM is valid.
+If, hypothetically, the SM is valid all the way up to the Planck scale (where quantum gravity becomes important), then Higgs mass corrections would be order($MP^2$) ~ $10^{32}$ GeV.
 
-    Now look at (4), again in the context of the Higgs mass.
-The terms correcting the Higgs mass depend quadratically on the cutoff energy scale, which must be at or below the scale where quantum gravity becomes important (MP = 1/rootG ~ 10\^18??).
-This creates a sticky situation.
-If the terms correcting the bare mass are order(10\^32)GeV and the observed Higgs mass is order(100)GeV, then the bare mass must exactly cancel the corrections to approximately 1 part in 10\^30.
-At present, no good evidence exists to explain why the bare mass and corrections would match so perfectly.
-The level of exact cancellation is known as 'fine tuning'.
+    Order($10^{32}$) corrections imply that the bare Higgs mass must be negative and also order($10^{32}$) to reproduce the experimetnally known value.
+In fact, the bare mass and corrections must match to 1 part in ~$10^{30}$.
+While it's entirely possible that these two numbers just so happen to match so perfectly, but many \fxnote{weak} feel that such miraculous fine tuning must be a hint that some deeper physical mechanism is at work.
+That is, either some previously unknown symmetry is protecting the Higgs mass or the cutoff scale is order(TeV).
 
-    (*probably doesn't need to be in final paper, but I'd like to check my basic understanding with Jamie, et al)
-    There are other unnatural quantities that people worry about in physics.
+    Before digging into possible solutions to this problem, one other question must be addressed: why doesn't this same argument apply to all SM particles?
+The answer comes from naturalness statement (3) above.
+As a fundamental scalar, the Higgs boson lacks the chiral or gauge symmetries enjoyed by the fermions and vector bosons, respectively.
+These two symmetries cause the symmetry of the SM to be enhanced when the fermion and vector boson masses are set to 0.
+\fxnote{work out fermion case?} Setting the higgs mass to 0 in no way increases the symmetry of the theory, so we have no reason to expect it to be small.
+
+    There are three main approaches to resolving this problem: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
+Arguments against naturalness often involve the anthropic principle, which claims that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
+Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than 3 spatial dimensions, which lowers the Planck mass itself.
+Finally, the dominant BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below.
+\fxnote{didn't mention composite higgs}
+
+    \fxnote{Optional paragraph about non-Higgs unnaturalness:    There are other unnatural quantities that people worry about in physics.
 I know of two off the top of my head: (1) thetaQCD in the strong CP problem (2) the cosmological consant.
@@
 The degree of violation is parameterized as thetaQCD, which recasts the problem into the naturalness context of 'why is thetaQCD so small?'.
-The cosmological constant is experimentally ~60 to ~120 orders of magnitude smaller than the predicted value (*predicted how?).
-While these issues deserve serious attention, they will not be considered further here.
-
-    (*talk about anthropic principle or other arguments against?)
-    (*I got tired of reading this section and haven't edited this paragraph at all yet)
-    There are a few proposed solutions to the SM naturalness problem.
-Supersymmetry is the main one, and I'll spend the great majority of my time on it.
-Extra dimensions and composite Higgs models are the other two that pop up fairly often, but won't spend much time on them outside the next two sentences.
-Extra dimensions solves the hierarchy problem either by lowering the cutoff scale (as in large extra dimensions (ADD)) or introducing a warping factor that reduces the level of unnaturalness (warped extra dimensions (RS)).
-Composite Higgs models propose that the Higgs stops behaving as a fundamental scalar at some energy level, which removes the quadratic dependence.
-(*Hidden valley, dark sector, little Higgs?)
+The cosmological constant is experimentally ~60 to ~120 orders of magnitude smaller than the predicted value \fxnote{predicted how?}.
+While these issues deserve serious attention, they will not be considered further here}
 
@@
     Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions.
-In it's simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson (*and an extra Higgs field - can I gloss over that?).
+In it's simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson \fxnote{and an extra Higgs field - can I gloss over that?}.
 The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
@@
 In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory.
-(*show example diagram with contribution?)
+\fxnote{show example diagram with contribution?}
 
@@
 \section{Long-lived Particles}
-    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and (*and/or?) produce a signal that could be missed by common SUSY search techniques.
+    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and \fxnote{and/or?} produce a signal that could be missed by common SUSY search techniques.
 Specifically, we are interested in SUSY models that predict long-lived particles (LLPs).
 That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
-This category includes everything from particles that decay at (*give ballparky number (~100um?)) to particles that propagate through the entire detector.
+This category includes everything from particles that decay at \fxnote{give ballparky number (~100um?)} to particles that propagate through the entire detector.
 
@@
 In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the the lightest particles carrying their respective conserved quantities.
-Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay (*also mention that they're both weak decays?).
-(*Mention neutrino, pion, kaon, some other bound state I might be forgetting?)
+Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay \fxnote{also mention that they're both weak decays?}.
+\fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}
 
     In SUSY models, LLPs arise for the same basic reasons, and different SUSY models meet different LLP criteria in different ways.
-The most common (*based on my assumptions) SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from proton decay.
+The most common \fxnote{based on my assumptions} SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from proton decay.
 In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1.
@@
 The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs.
-(*is now a good time to explain GMSB?)(*cite dimopoulos low energy)
+\fxnote{is now a good time to explain GMSB?}\fxnote{cite dimopoulos low energy}
 
@@
 In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark.
-(*cite kilian) (*mention that split throws out naturalness motivation?)
+\fxnote{cite kilian} \fxnote{mention that split throws out naturalness motivation?}
 
     The degenerate mass spectra of other SUSY models can also give rise to LLPs.
-In some AMSB models (*explain AMSB?), for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
+In some AMSB models \fxnote{explain AMSB?}, for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
 The wino then becomes long-lived when its decay is suppressed by the lack of available phase space.
-(*cite R\&S out of this world)
-    (*merge last 2 paragraphs under 'mass spectra lead to LLP' concept?)
-    (*never said anything about hidden valley or dark sector stuff. Never said the word R-hadron. Never said stealth or displaced SUSY. Should I?)
+\fxnote{cite R\&S out of this world}
+    \fxnote{merge last 2 paragraphs under 'mass spectra lead to LLP' concept?}
+    \fxnote{never said anything about hidden valley or dark sector stuff. Never said the word R-hadron. Never said stealth or displaced SUSY. Should I?}
 
@@
 \subsection{Overview}
-    (*cite cms experiment at the cern lhc)
+    \fxnote{cite cms experiment at the cern lhc}
     The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from 14 TeV proton-proton collisions at the Large Hadron Collider (LHC).
@@
 \subsection{Tracker}
-    (*cite CMS TDR, jinst 12 c02033)
-    (*maybe I should trade some number listing for talking about how silicon detectors work)
-    (*what about readout, cooling, etc?)
+    \fxnote{cite CMS TDR, jinst 12 c02033}
+    \fxnote{maybe I should trade some number listing for talking about how silicon detectors work}
+    \fxnote{what about readout, cooling, etc?}
     In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
-The tracker is subdivided into two regions: at r < 20 cm, the high particle flux (*specify) requires small pixels to keep occupancy near 0.1\%.
+The tracker is subdivided into two regions: at r < 20 cm, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near 0.1\%.
 Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
 
-    The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million silicon pixels, each of which covers an active area of 100 by 150 um\^2.
+    The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million silicon pixels, each of which covers an active area of 100 by 150 $um^2$.
 The pixels are spread between four barrel layers (BPIX) at 2.9 < r < 16 cm and 3 endcap rings (FPIX) at 29 < z < 52 cm.
@@
     Just outside the pixel tracker, the silicon strip tracker (SST) occupies the 20 < r < 116 cm and |z| < 282 cm region of CMS.
-Composed of 9.3 million silicon strips that vary from \_ to \_ in size (*look up) depending on particle flux in the region, the SST covers an active area of roughly 196 m\^2.
-At each trigger, the strip output voltage is transferred via optical link to be read out by off-detector front-end electronics (*right jargon?).
+Composed of 9.3 million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly 196 $m^2$.
+At each trigger, the strip output voltage is transferred via optical link to be read out by off-detector front-end electronics \fxnote{right jargon?}.
 
 \subsection{Electromagnetic Calorimeter}
-    (*cite CMS TDR)
-    (*talk about readout?)
-    (*More in the way of concept/how stuff works?)
+    \fxnote{cite CMS TDR}
+    \fxnote{talk about readout?}
+    \fxnote{More in the way of concept/how stuff works?}
     After traversing the inner tracker, a particle would next encounter the electromagnetic calorimeter (ECAL).
 As a homogeneous scintillation calorimeter, ECAL uses 61200 lead tunstate crystals in the barrel and 7324 in each endcap to reconstruct the energy deposited during electromagnetic showers.
-Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere length = 2.2 cm), and radiation hard (up to 10 Mrad(*learn context for this number)) calorimeter.
-The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields (*say B-field part better).
+Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere length = 2.2 cm), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
+The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields \fxnote{say B-field part better}.
 
-    The barrel section (EB) extends radially from 129 to 177 (*look up) cm and covers a pseudorapidity range of 0 to 1.479.
+    The barrel section (EB) extends radially from 129 to 177 \fxnote{look up} cm and covers a pseudorapidity range of 0 to 1.479.
 The crystals are tapered to approximately project back to the IP but not so perfectly that likely particle trajectories align with cracks.
@@
 Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals.
-(*Say what the preshower is for?
+\fxnote{Say what the preshower is for?
 Is it for pi0 rejection?
-If so, how and why?)
+If so, how and why?}
 
 \subsection{Hadronic Calorimeter}
-    (*cite CMS TDR)
-    (*talk about readout?)
+    \fxnote{cite CMS TDR}
+    \fxnote{talk about readout?}
     The hadronic calorimeter (HCAL) uses 3.7mm plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers.
@@
 
-    The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers (*check), each of which contains 14 (*check) brass plates and covers an area of 0.087 x 0.087 in eta-phi (*get a feel for this area).
+    The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers \fxnote{check}, each of which contains 14 \fxnote{check} brass plates and covers an area of 0.087 x 0.087 in eta-phi \fxnote{get a feel for this area}.
 In addition, an extra layer (or two at eta = 0) of scintillator tiles sits just outside the solenoid.
@@
 In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline.
-(*say why HF is useful or mention crazy flux?)
+\fxnote{say why HF is useful or mention crazy flux?}
 
 \subsection{Solenoid}
-    (*cite cms experiment at the cern lhc)
+    \fxnote{cite cms experiment at the cern lhc}
     CMS employs a 4 T superconducting solenoid to aid in the measurement of charged particle momenta.
@@
 The flux returns through an iron yoke that also houses the muon system.
-The significant (*quantify?) bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of 10\% for muons up to 1 TeV.
+The significant \fxnote{quantify?} bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of 10\% for muons up to 1 TeV.
 
 \subsection{Muon System}
-    (*cite CMS TDR)
-    (*Specifically mention CMS design specs to meet physics goals?)
+    \fxnote{cite CMS TDR}
+    \fxnote{Specifically mention CMS design specs to meet physics goals?}
     The muon system (MS), which is the outermost subdetector, detects muons with 3 varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps.
@@
 The RPCs are useful in both the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
-Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines (*quantify or show std plot?).
+Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines \fxnote{quantify or show std plot?}.
 
     In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at 4.0, 4.9, 5.9, and 7.9 m.
-(*Say how DT works?) The maximum drift length is 2 cm and the single point resolution is 200 um.
+\fxnote{Say how DT works?} The maximum drift length is 2 cm and the single point resolution is 200 um.
 When reconstructing a vector describing the muon momentum, the phi precision is better than 100 um in position and 1 mrad in direction.
 
-    Each muon endcap detector (ME) is composed of 234 CSCs and 4 RPC stations (*figure out exactly what RPC station means and say that instead).
+    Each muon endcap detector (ME) is composed of 234 CSCs and 4 RPC stations \fxnote{figure out exactly what RPC station means and say that instead}.
 Each CSC has six gas gaps with radial cathode strips and nearly perpendicualar planes of anode wires.
-The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower (*quantify) cathode strip signal provides precise (*quantify) position measurements.
+The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements.
 All in all, the CSC spacial resolution is approximately 200 um and the angular resolution is approximately 10 mrad.
@@
 \subsection{Trigger}
-    (*cite CMS TDR, jinst 12 c03021)
-    (*Is entire detector read out at L1?)
-    (*Mention fpgas in L1 or more details about HLT?)
-    (*Something about particle flow?)
-    (*Sloppy, but I'm getting tired)
+    \fxnote{cite CMS TDR, jinst 12 c03021}
+    \fxnote{Is entire detector read out at L1?}
+    \fxnote{Mention fpgas in L1 or more details about HLT?}
+    \fxnote{Something about particle flow?}
+    \fxnote{Sloppy, but I'm getting tired}
     The trigger reduces the data writing rate from the 40 MHz collision rate to less than 1 kHz so that events can be written to tape.
@@
     LLPs leave distinct signatures that differentiate LLP signals from SM backgrounds but also add complexity to LLP analyses.
-CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to stray from the traditional analysis path in terms of object reconstruction (*really reconstruction?
-Maybe object definition?), background estimation, and which data tier to use (*can I say this more generally?).
+CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to stray from the traditional analysis path in terms of object reconstruction \fxnote{really reconstruction?
+Maybe object definition?}, background estimation, and which data tier to use \fxnote{can I say this more generally?}.
 This paper will focus on four complementary LLP signatures: displaced vertices, disappearing tracks, slow-moving particles, and particles that stop completely before decaying.
 
-    Displaced vertices and disappearing tracks both look for particles that are unstable on detector timescales (*quantify?).
-Displaced vertices searches are sensitive to LLPs that decay to visible particles in the inner volume (*specify) of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point (*wordy).
+    Displaced vertices and disappearing tracks both look for particles that are unstable on detector timescales \fxnote{quantify?}.
+Displaced vertices searches are sensitive to LLPs that decay to visible particles in the inner volume \fxnote{specify} of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point \fxnote{wordy}.
 Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed.
-Together, these two types of analyses cover (*something something) parameter space of LLPs that decay on detector timescales.
+Together, these two types of analyses cover \fxnote{something something} parameter space of LLPs that decay on detector timescales.
 
     Slow and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
-Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles (*redundant), which normally (*quantify) have beta > 0.9.
+Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles \fxnote{redundant}, which normally \fxnote{quantify} have beta > 0.9.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
@@
 \subsection{Displaced Vertices}
-    (*cite CONF-2017-026)
+    \fxnote{cite CONF-2017-026}
     LLPs that decay before reaching the inner tracker but still live longer than the vast majority of SM particles can be identified with a displaced vertex (DV).
@@
 In the simplified model, gluinos are kinematically accessible while squarks are not.
-The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino (*diagram?).
-Because the squark mass is so high, the gluino lives long enough to form an R-hadron (*first use.
-Define here if not in LLP section) with SM quarks and propogate some measureable distance away from the IP before decaying.
+The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino \fxnote{diagram?}.
+Because the squark mass is so high, the gluino lives long enough to form an R-hadron \fxnote{first use.
+Define here if not in LLP section} with SM quarks and propogate some measureable distance away from the IP before decaying.
 
@@
 For an LSP neutralino mass of 100 GeV, the gluino mass limit is approximately 2000 GeV for lifetimes in the 20 ps to 10 ns range.
-(*Include plots)
+\fxnote{Include plots}
 
 \subsection{Disappearing Tracks}
-    (*cite CONF-2017-017)
-    (*nice disappearing track cartoon)
-    (*nice cartoon feynman diagrams of signal processes)
+    \fxnote{cite CONF-2017-017}
+    \fxnote{nice disappearing track cartoon}
+    \fxnote{nice cartoon feynman diagrams of signal processes}
     Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
@@
 
-    Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 and CMS before 2017 should increase sensitivity to decays at shorter radii (*I haven't mentioned previous iterations when talking about other analyses).
-The ALTAS search presented here is sensitive to LLP lifetimes of approximated 10 ps to 10 ns (*make sure I'm talking about lifetime sensitivity in the same way across analyses).
+    Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 and CMS before 2017 should increase sensitivity to decays at shorter radii \fxnote{I haven't mentioned previous iterations when talking about other analyses}.
+The ALTAS search presented here is sensitive to LLP lifetimes of approximated 10 ps to 10 ns \fxnote{make sure I'm talking about lifetime sensitivity in the same way across analyses}.
 
@@
 Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically unaccessable, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
-The ISR jet in process (1) is not physically required; it simply provides something for the gluinos to recoil off of so the MET signal isn't lost (*My interpretation.
-Run it by someone who knows stuff).
+The ISR jet in process (1) is not physically required; it simply provides something for the gluinos to recoil off of so the MET signal isn't lost \fxnote{My interpretation.
+Run it by someone who knows stuff}.
 
@@
 
-    Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by pixel hits that don't have the proper hits from the next tracking layer associated to them, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon (*lots of words).
+    Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by pixel hits that don't have the proper hits from the next tracking layer associated to them, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon \fxnote{lots of words}.
 These backgrounds come primarily from ttbar and W+jets processes, and estimates for each type of background are obtained from data.
-(*I initially wrote a whole big thing about how each bg was estimated, but I'm thinking it was overkill)
+\fxnote{I initially wrote a whole big thing about how each bg was estimated, but I'm thinking it was overkill}
 
-    No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass gluon mass plane for the QCD production process (*hopefully will be way clearer after texing in sparticle symbols).
-(*Either include  plots or say numbers)
+    No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass gluon mass plane for the QCD production process \fxnote{hopefully will be way clearer after texing in sparticle symbols}.
+\fxnote{Either include plots or say numbers}
 
 \subsection{Stopped Particles}
-    (*cite CMS PAS EXO-17-004)
-    (*mention how stopped particles complement HSCP search?)
-    (*too redundant with overview?)
+    \fxnote{cite CMS PAS EXO-17-004}
+    \fxnote{mention how stopped particles complement HSCP search?}
+    \fxnote{too redundant with overview?}
     With long enough lifetimes and sufficient mass, LLPs could come to rest in the detector before decaying.
 The eventual decay would then lead to energy deposits in the calorimeters or hits in the muon system that could be out of time with proton bunch crossings.
-A recent CMS analysis looked for such a signal in dimuon final states (*necessarily dimuon?) using the full 2015 and 2016 datasets.
+A recent CMS analysis looked for such a signal in dimuon final states \fxnote{necessarily dimuon?} using the full 2015 and 2016 datasets.
 
@@
 After unblinding, the observed number of events is exactly zero in every lifetime scenerio.
-These results are then interpreted as upper limits on the signal production cross section (*include limit plots or table), which are the first limits for stopped particles that decay to muons at the LHC.
+These results are then interpreted as upper limits on the signal production cross section \fxnote{include limit plots or table}, which are the first limits for stopped particles that decay to muons at the LHC.
 
 \subsection{Heavy Stable Charged Particles}
-    (*cite CMS EXO7-010)
-    (*nice dE/dx plot (fig 1))
-    Particles that live for more than a couple ns (*Check this and be more exact) will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
+    \fxnote{cite CMS EXO7-010}
+    \fxnote{nice dE/dx plot (fig 1})
+    Particles that live for more than a couple ns \fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
 If such a particle is also sufficiently massive, it can be catigorized as a heavy stable charged particle (HSCP).
@@
 
-    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and \|q\|=+-e (*dE/dx plot is nice around here).
+    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and |q|=+-e \fxnote{dE/dx plot is nice around here}.
 Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with aritrary electric charge.
@@
 
-    (*I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta~1.
+    \fxnote{I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta~1.
 Zig-zag offset is used to estimate beta.
-Not sure where to fit it in.) (*Worth mentioning tracker-only vs tracker+TOF)
+Not sure where to fit it in.} \fxnote{Worth mentioning tracker-only vs tracker+TOF}
 
@@
 
-    The authors estimate the signal-region background using an ABCD method in which events are binned in a 2D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region (*Do I need to explain this?
-If I do, I should be more clear).
+    The authors estimate the signal-region background using an ABCD method in which events are binned in a 2D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region \fxnote{Do I need to explain this?
+If I do, I should be more clear}.
 Systematic uncertainties are introduced in background estimation, signal acceptance, and integrated luminosity.
@@
 By comparing the observed and theoretical limits, the authors also extract mass limits for the gluinos, stops, and staus in various models.
-(*Include plots - table is too big and too many numbers to list)
+\fxnote{Include plots - table is too big and too many numbers to list}
 

### 2017-07-21 tex/draft.tex
Little TeX fixes - version sent to everybody

@@
 \usepackage[draft]{fixme}
-\fxsetup{layout=footnote, marginclue}
+\fxsetup{layout=footnote}
+\usepackage[left]{lineno}
 \usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref}
@@
 \doublespacing
+\linenumbers
 
@@
 The scale of the loop corrections is proportional to the square of the cutoff scale of the SM, which is the highest energy at which the SM is valid.
-If, hypothetically, the SM is valid all the way up to the Planck scale (where quantum gravity becomes important), then Higgs mass corrections would be order($MP^2$) ~ $10^{32}$ GeV.
+If, hypothetically, the SM is valid all the way up to the Planck scale (where quantum gravity becomes important), then Higgs mass corrections would be order($MP^2$) $\approx 10^{32}$ GeV.
 
     Order($10^{32}$) corrections imply that the bare Higgs mass must be negative and also order($10^{32}$) to reproduce the experimetnally known value.
-In fact, the bare mass and corrections must match to 1 part in ~$10^{30}$.
-While it's entirely possible that these two numbers just so happen to match so perfectly, but many \fxnote{weak} feel that such miraculous fine tuning must be a hint that some deeper physical mechanism is at work.
+In fact, the bare mass and corrections must match to 1 part in $\approx 10^{30}$.
+While it's entirely possible that these two numbers just so happen to match so perfectly, many \fxnote{weak} feel that such miraculous fine tuning must be a hint that some deeper physical mechanism is at work.
 That is, either some previously unknown symmetry is protecting the Higgs mass or the cutoff scale is order(TeV).
@@
 The degree of violation is parameterized as thetaQCD, which recasts the problem into the naturalness context of 'why is thetaQCD so small?'.
-The cosmological constant is experimentally ~60 to ~120 orders of magnitude smaller than the predicted value \fxnote{predicted how?}.
+The cosmological constant is experimentally $\approx$60 to $\approx$120 orders of magnitude smaller than the predicted value \fxnote{predicted how?}.
 While these issues deserve serious attention, they will not be considered further here}
@@
 That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
-This category includes everything from particles that decay at \fxnote{give ballparky number (~100um?)} to particles that propagate through the entire detector.
+This category includes everything from particles that decay at \fxnote{give ballparky number ($\approx$100um?)} to particles that propagate through the entire detector.
 
@@
     In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
-The tracker is subdivided into two regions: at r < 20 cm, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near 0.1\%.
+The tracker is subdivided into two regions: at r $<$ 20 cm, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near 0.1\%.
 Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
@@
     The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million silicon pixels, each of which covers an active area of 100 by 150 $um^2$.
-The pixels are spread between four barrel layers (BPIX) at 2.9 < r < 16 cm and 3 endcap rings (FPIX) at 29 < z < 52 cm.
-The upgraded pixel tracker should provide 4-hit tracking out to eta < 2.4 and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
+The pixels are spread between four barrel layers (BPIX) at 2.9 $<$ r $<$ 16 cm and 3 endcap rings (FPIX) at 29 $<$ z $<$ 52 cm.
+The upgraded pixel tracker should provide 4-hit tracking out to eta $<$ 2.4 and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
 
-    Just outside the pixel tracker, the silicon strip tracker (SST) occupies the 20 < r < 116 cm and |z| < 282 cm region of CMS.
+    Just outside the pixel tracker, the silicon strip tracker (SST) occupies the 20 $<$ r $<$ 116 cm and $|z|$ $<$ 282 cm region of CMS.
 Composed of 9.3 million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly 196 $m^2$.
@@
 
-    The crystals in each endcap section (EE) are arranged in an x-y grid that starts at |z| = 315 cm and covers a pseudorapidity range of 1.479 to 3.0.
+    The crystals in each endcap section (EE) are arranged in an x-y grid that starts at $|z|$ = 315 cm and covers a pseudorapidity range of 1.479 to 3.0.
 Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals.
@@
 The choice of detector varies between barrel and endcap due to the difference in neutron-induced background, muon rates, and magnetic field strength.
-The RPCs are useful in both the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
+The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
 Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines \fxnote{quantify or show std plot?}.
@@
 The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT).
-L1 uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, MET, and mu) and uses custom electronics to reduce the rate to ~100 kHz in 3.8 us.
-The HLT then uses a dedicated processor farm to further reduce the rate to the desired < 1 kHz.
+L1 uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, MET, and mu) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
+The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz.
 
@@
     Slow and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
-Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles \fxnote{redundant}, which normally \fxnote{quantify} have beta > 0.9.
+Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles \fxnote{redundant}, which normally \fxnote{quantify} have beta $>$ 0.9.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
@@
 
-    Disappearing tracks canditates, called pixel tracklets, are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard reconstruction algorithm.
+    Disappearing track candidates, called pixel tracklets, are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard reconstruction algorithm.
 The pixel tracklets are required to pass several isolation, pT, and quality requirements such as number of pixel layer hits.
@@
 The eventual decay would then lead to energy deposits in the calorimeters or hits in the muon system that could be out of time with proton bunch crossings.
-A recent CMS analysis looked for such a signal in dimuon final states \fxnote{necessarily dimuon?} using the full 2015 and 2016 datasets.
+A recent CMS analysis looked for such a signal in dimuon final states using the full 2015 and 2016 datasets.
 
@@
     \fxnote{cite CMS EXO7-010}
-    \fxnote{nice dE/dx plot (fig 1})
+    \fxnote{nice dE/dx plot (fig 1)}
     Particles that live for more than a couple ns \fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
@@
 
-    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta~1 and |q|=+-e \fxnote{dE/dx plot is nice around here}.
-Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with aritrary electric charge.
+    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta$\approx$1 and $|q|$ = e.
+Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge.
 This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY.
 
-    \fxnote{I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta~1.
+    \fxnote{I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta$\approx$1.
 Zig-zag offset is used to estimate beta.

### 2017-07-24 tex/draft.tex
Minor edits from Juliette & Ethan

@@
     The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing \fxnote{weak word} accuracy.
-The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter, 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces, and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
+The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter; 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces; and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
 
     All SM particles transform according to the gauged symmetry group SU(3)cxSU(2)LxU(1)Y, where SU(3)c is associated with color charge, SU(2)L is associated with weak isospin, and U(1)Y is associated with weak hypercharge.
-The gauge bosons are associated with the generators of these groups, thus there are 8 gluons associated with SU(3)c, 3 W bosons associated with SU(2)L, and 1 B boson associated with U(1)Y.
+The gauge bosons are associated with the generators of these groups, thus there are 8 gluons associated with SU(3)c, three W bosons associated with SU(2)L, and 1 B boson associated with U(1)Y.
 The fermions are catagorized by which representation of each group they fit into.
@@
 
-    Before digging into possible solutions to this problem, one other question must be addressed: why doesn't this same argument apply to all SM particles?
+    Before digging into possible solutions to this problem\fxnote{specify}, one other question must be addressed: why doesn't this same argument apply to all SM particles?
 The answer comes from naturalness statement (3) above.
@@
 
-    There are three main approaches to resolving this problem: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
+    There are three main approaches to resolving this problem\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
 Arguments against naturalness often involve the anthropic principle, which claims that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
@@
     Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions.
-In it's simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson \fxnote{and an extra Higgs field - can I gloss over that?}.
+In its simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson \fxnote{and an extra Higgs field - can I gloss over that?}.
 The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
@@
     The SUSY variants most relevant to this discussion are those that are motivated by naturalness and \fxnote{and/or?} produce a signal that could be missed by common SUSY search techniques.
-Specifically, we are interested in SUSY models that predict long-lived particles (LLPs).
-That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
+Specifically, we are interested in SUSY models that predict new long-lived particles (LLPs).
+\fxnote{incomplete sentence} That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
 This category includes everything from particles that decay at \fxnote{give ballparky number ($\approx$100um?)} to particles that propagate through the entire detector.
@@
 \subsection{Overview}
+    \fxnote{Add LHC description}  
     \fxnote{cite cms experiment at the cern lhc}
@@
 \subsection{Stopped Particles}
+    \fxnote{Add calorimeter search?}  
     \fxnote{cite CMS PAS EXO-17-004}

### 2017-07-25 tex/draft.tex
Start What is Natural SUSY? draft

@@
 
+\pagenumbering{gobble}
 \singlespacing
-
 \maketitle
@@
 \linenumbers
+\pagenumbering{arabic}
 
@@
 
-\section{Experimental Viability of Natural BSM}
-\subsection{Limits Summary}
-\subsection{What makes a SUSY model natural?}
+\section{Experimental Viability of Natural SUSY}
+    \fxnote{Comparison of 'Cornering', 'Toward Full', and 'What is' should do the trick} 
+    \fxnote{Then add in current overall limits and reference specific LLP limits} 
+    Cornering perspective
+        When building a natural SUSY model, certain constraints are nearly unavoidable\fxnote{Dangerous.
+What if Linda knows how to avoid them?}.
+Specifically, the higgsino, which affects mH at tree level; the stop, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be heavy enough to pull mH up to 125 GeV\fxnote{Do I really understand this?} but light enough to avoid excessive fine tuning.
+Furthermore, the stop and gluino masses are correlated: a large mass difference between the two would constitute a new fine-tuning problem.
+
+        Natural SUSY scenarios, then, are most likely to be constrained by limits on stop and gluino masses due to the strong interaction of these two objects as opposed to the colorless Higgsino\fxnote{Dear lord, I don't understand why I can't figure out how to word this sentence}.
+Indeed, limits on mStop and mGluino wipe out much of the natural parameter space for many models with decoupled first and second geration fermions, baryonic RPV, or compressed spectra that minimize missing energy while the MSSM is completely excluded.\fxnote{Define naturalness quantitatively here?}  \fxnote{Good spot for sweet Cornering plots}
+
+        Demanding naturalness also constrains the messenger scale of SUSY breaking\fxnote{Make sure I understand this.
+Messenger scale == breaking scale?}.
+Corrections to the Higgs mass from stops and gluinos depend of the messenger scale\fxnote{reference eqs}, so natural SUSY generally prefers a lower scale.
+
+        Despite strong contraints, SUSY remains one of the least-tuned options for BSM naturalness\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.\fxnote{Good place for Feng "how much tuning is acceptable?
+discussion}
+
+    Toward Full perspective
+
+    What is perspective
 

### 2017-07-26 tex/draft.tex
Start to fix up Experimental Viability

@@
 \section{Experimental Viability of Natural SUSY}
-    \fxnote{Comparison of 'Cornering', 'Toward Full', and 'What is' should do the trick} 
-    \fxnote{Then add in current overall limits and reference specific LLP limits} 
-    Cornering perspective
     When building a natural SUSY model, certain constraints are nearly unavoidable\fxnote{Dangerous.
@@
 Specifically, the higgsino, which affects mH at tree level; the stop, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be heavy enough to pull mH up to 125 GeV\fxnote{Do I really understand this?} but light enough to avoid excessive fine tuning.
-Furthermore, the stop and gluino masses are correlated: a large mass difference between the two would constitute a new fine-tuning problem.
+Furthermore, the stop and gluino masses are correlated -\fxnote{m-dash?} a large difference between the two would be another source of fine tuning.
 
     Natural SUSY scenarios, then, are most likely to be constrained by limits on stop and gluino masses due to the strong interaction of these two objects as opposed to the colorless Higgsino\fxnote{Dear lord, I don't understand why I can't figure out how to word this sentence}.
-Indeed, limits on mStop and mGluino wipe out much of the natural parameter space for many models with decoupled first and second geration fermions, baryonic RPV, or compressed spectra that minimize missing energy while the MSSM is completely excluded.\fxnote{Define naturalness quantitatively here?}  \fxnote{Good spot for sweet Cornering plots}
+Demanding naturalness also constrains the messenger scale of SUSY breaking\fxnote{Make sure I understand this.
+Messenger scale != breaking scale?}.
+Corrections to the Higgs mass from stops and gluinos depend of the messenger scale\fxnote{reference eqs}, so natural SUSY generally prefers a lower scale.\fxnote{Either explain more thoroughly or drop completely.
+What are the consequences of a lower messenger scale?}
 
-        Demanding naturalness also constrains the messenger scale of SUSY breaking\fxnote{Make sure I understand this.
-Messenger scale == breaking scale?}.
-Corrections to the Higgs mass from stops and gluinos depend of the messenger scale\fxnote{reference eqs}, so natural SUSY generally prefers a lower scale.
+    Indeed, limits on mStop and mGluino from conventional SUSY searches wipe out much of the natural parameter space\fxnote{quantify?
+That would require getting into how one quantifies fine tuning} for many models with decoupled first and second geration fermions, baryonic RPV, or compressed spectra that minimize missing energy while the natural MSSM is completely excluded.\fxnote{Good spot for sweet Cornering plots}\fxnote{Use ATLAS SUSY summary plot too.
+CMS's isn't updated}
+
+\fxnote{How do LLPs open doors to naturalness and which of those doors have we already closed?}
 
@@
 discussion}
-
-    Toward Full perspective
-
-    What is perspective
 

### 2017-07-27 tex/draft.tex
add (or fix) Andrew's comments

@@
 For example, SU(3)c distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and SU(2)L distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
-Finally, different values of weak hypercharge further distignuish SM particles according to a linear combination of their weak isospin and electric charge \fxnote{is there some more fundamental way to describe Y?}.
+Finally, different values of weak hypercharge further distignuish SM particles according to the Gell-Mann\fxnote{em-dash}Nishijima formula, $iY=2(Q-I3$.
 
@@
 Once the dust settles, the B and 3 W bosons have been mixed to produce the W+, W-, Z bosons that mediate the weak force and the photon that mediates electromagnetism.
-3 of the 4 generators are broken in the process, leaving 3 extra degrees of freedom that ultimately become the masses of the W+, W-, and Z bosons while the remaining symmetry is associated with electric charge.
-Furthermore, expanding the Higgs field about its VEV produces mass terms for the quarks and charged leptons, thus giving mass to all massive SM particles.
-\fxnote{probably show a little math}
+\fxnote{Andrew says the next sentence isn't quite right.
+3 of 4 DOF from complex Higgs field are eaten by W+,W-,Z.
+Remaining DOF becomes physical Higgs boson.
+Masses don't come from broken generators.
+Read about it then fix} 3 of the 4 generators are broken in the process, leaving 3 extra degrees of freedom that ultimately become the masses of the W+, W-, and Z bosons while the remaining symmetry is associated with electric charge.
+Furthermore, expanding the Higgs field about its VEV produces mass terms for the quarks and charged leptons, thus giving mass to all massive SM particles.\fxnote{Fermion masses ad-hoc, not fundamental, says Andrew}  \fxnote{probably show a little math}\fxnote{Why can't we add explicit mass terms to SM lagrangian w/o Higgs?
+Summarize section 1 of Andrew's paper}
 
@@
 These interactions lead to corrections to SM parameters such as particle masses.
-It is common to write a given parameter as a linear combination of its 'bare' (uncorrected) value and its corrections.
-As the only fundamental scalar in the SM, the Higgs is uniquely affected by these corrections.
-The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the Higgs bare mass and the terms that correct it.
+It is common to write a given parameter as a linear combination of its 'bare' (uncorrected) value and its corrections.\fxnote{Not wrong, but sounds funny.
+Of course we write it that way when talking about a sum of diagrams} As the only fundamental scalar in the SM, the Higgs is uniquely affected by these corrections.\fxnote{Explain why scalars are more sensitive.
+Show math probably} The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the Higgs bare mass and the terms that correct it.
 
@@
 
-    Order($10^{32}$) corrections imply that the bare Higgs mass must be negative and also order($10^{32}$) to reproduce the experimetnally known value.
+    \fxnote{Point is that corrections come in with different signs and individual terms are huge.
+Really weird that they would cancel out so perfectly.
+Maybe add feynman diagrams to illustrate.
+Use Jaxodraw probably} Order($10^{32}$) corrections imply that the bare Higgs mass must be negative and also order($10^{32}$) to reproduce the experimetnally known value.
 In fact, the bare mass and corrections must match to 1 part in $\approx 10^{30}$.
@@
 
-    Before digging into possible solutions to this problem\fxnote{specify}, one other question must be addressed: why doesn't this same argument apply to all SM particles?
+   \fxnote{Confusing, says Andrew.
+Maybe add math}  Before digging into possible solutions to this problem\fxnote{specify}, one other question must be addressed: why doesn't this same argument apply to all SM particles?
 The answer comes from naturalness statement (3) above.
@@
 
-    There are three main approaches to resolving this problem\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
+    \fxnote{Clarify that not technically a problem.
+Nature might just be that way.
+Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to resolving this problem\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
 Arguments against naturalness often involve the anthropic principle, which claims that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
@@
     Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions.
-In its simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson \fxnote{and an extra Higgs field - can I gloss over that?}.
+In its simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson \fxnote{and an extra Higgs field - probably should mention it.
+Make sure I understand it either way}.
 The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
@@
 In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the the lightest particles carrying their respective conserved quantities.
-Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay \fxnote{also mention that they're both weak decays?}.
+Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay \fxnote{Mention that they have small couplings b/c weak force and high-mass intermediate particle is involved too}.
 \fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}
@@
     In SUSY models, LLPs arise for the same basic reasons, and different SUSY models meet different LLP criteria in different ways.
-The most common \fxnote{based on my assumptions} SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from proton decay.
+The most common\fxnote{bad langauge.
+Andrew suggests 'most straightforward' or 'most ad-hoc'} SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from proton decay\fxnote{Be prepared to show this.
+Maybe add some diagrams illustrating proton decay w/o R-parity}.
 In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1.
@@
 In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark.
-\fxnote{cite kilian} \fxnote{mention that split throws out naturalness motivation?}
+\fxnote{cite kilian} \fxnote{mention that split throws out naturalness motivation?}\fxnote{Add diagrams}
 
-    The degenerate mass spectra of other SUSY models can also give rise to LLPs.
+    \fxnote{There is no zino.
+Maybe I meant bino?
+Neutralinos and charginos are the physical states that are linear combos of winos, bino, higgsinos} The degenerate mass spectra of other SUSY models can also give rise to LLPs.
 In some AMSB models \fxnote{explain AMSB?}, for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
@@
     \fxnote{never said anything about hidden valley or dark sector stuff. Never said the word R-hadron. Never said stealth or displaced SUSY. Should I?} 
+    \fxnote{Andrew says don't worry about mentioning models that don't come up in the searches, but be prepared to explain the basic ideas behind HV, dark sector and how they result in LLP}
 
-\section{The CMS Detector}
+\section{The CMS Detector}\fxnote{Add pictures of everything}
 \subsection{Overview}
     \fxnote{Add LHC description}  
+    \fxnote{Mention that ATLAS is similar}  
+    \fxnote{Maybe mention PDFs. Definitely know about them}  
     \fxnote{cite cms experiment at the cern lhc}
-    The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from 14 TeV proton-proton collisions at the Large Hadron Collider (LHC).
+    The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from 14 TeV\fxnote{Mention lower-energy runs} proton-proton collisions at the Large Hadron Collider (LHC).
 To meet this goal, CMS combines information from several subdetectors nested radially in and around a 4-T superconducting solenoid.
@@
     \fxnote{cite CMS TDR, jinst 12 c02033}
-    \fxnote{maybe I should trade some number listing for talking about how silicon detectors work}
     \fxnote{what about readout, cooling, etc?}
-    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
-The tracker is subdivided into two regions: at r $<$ 20 cm, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near 0.1\%.
+    \fxnote{mention that analyses below used pre-upgrade tracker}
+    \fxnote{mention stereo modules and be able to explain stereo modules}
+    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.\fxnote{out-of-fielder may not know about 'track' or 'vertex'} The tracker is subdivided into two regions: at r $<$ 20 cm, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near 0.1\%.
 Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
@@
     The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million silicon pixels, each of which covers an active area of 100 by 150 $um^2$.
-The pixels are spread between four barrel layers (BPIX) at 2.9 $<$ r $<$ 16 cm and 3 endcap rings (FPIX) at 29 $<$ z $<$ 52 cm.
+The pixels are spread between four barrel layers (BPIX) at 2.9 $<$ r $<$ 16 cm and 3 endcap rings\fxnote{Andrew says it's 'disc', not 'ring'.
+Each disc is composed of two concentric rings of modules} (FPIX) at 29 $<$ z $<$ 52 cm.
 The upgraded pixel tracker should provide 4-hit tracking out to eta $<$ 2.4 and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
@@
 Composed of 9.3 million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly 196 $m^2$.
-At each trigger, the strip output voltage is transferred via optical link to be read out by off-detector front-end electronics \fxnote{right jargon?}.
+At each trigger, the strip output voltage is read out via optical link.
 
@@
 As a homogeneous scintillation calorimeter, ECAL uses 61200 lead tunstate crystals in the barrel and 7324 in each endcap to reconstruct the energy deposited during electromagnetic showers.
-Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere length = 2.2 cm), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
+Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere\fxnote{Andrew says 'radius', not 'length', and use accent!} length = 2.2 cm), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
 The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields \fxnote{say B-field part better}.
 
-    The barrel section (EB) extends radially from 129 to 177 \fxnote{look up} cm and covers a pseudorapidity range of 0 to 1.479.
+    The barrel section (EB) extends radially from 129 to 177 \fxnote{look up} cm and covers a pseudorapidity\fxnote{define} range of 0 to 1.479.
 The crystals are tapered to approximately project back to the IP but not so perfectly that likely particle trajectories align with cracks.
@@
 The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
-Combining MS and tracker measurements improves the muon pT resolution at high momenta where the tracker pT resolution declines \fxnote{quantify or show std plot?}.
+Combining MS and tracker measurements improves the muon pT\fxnote{define} resolution at high momenta where the tracker pT resolution declines \fxnote{quantify or show std plot?}.
 
@@
     \fxnote{Mention fpgas in L1 or more details about HLT?}
-    \fxnote{Something about particle flow?}
     \fxnote{Sloppy, but I'm getting tired}
@@
 The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT).
-L1 uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, MET, and mu) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
+L1 uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, MET\fxnote{define}, and mu) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
 The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz.
@@
 \section{LHC Searches for Long-lived Particles}
+\fxnote{Include diagrams for signal models} 
+\fxnote{mention which data was used for each search} 
+\fxnote{Steal limit plots and any cool figures from papers} 
 \subsection{Overview}
@@
 CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to stray from the traditional analysis path in terms of object reconstruction \fxnote{really reconstruction?
-Maybe object definition?}, background estimation, and which data tier to use \fxnote{can I say this more generally?}.
+Maybe object definition?}, background estimation, and which data tier to use \fxnote{data tier is too jargony}.
 This paper will focus on four complementary LLP signatures: displaced vertices, disappearing tracks, slow-moving particles, and particles that stop completely before decaying.
@@
     Slow and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
-Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles \fxnote{redundant}, which normally \fxnote{quantify} have beta $>$ 0.9.
+Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles \fxnote{redundant}, which normally \fxnote{quantify} have beta\fxnote{define} $>$ 0.9.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
@@
 In the simplified model, gluinos are kinematically accessible while squarks are not.
-The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino \fxnote{diagram?}.
+The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino \fxnote{steal diagram from andrew's preapproval.
+I can't access it - ask andrew}.
 Because the squark mass is so high, the gluino lives long enough to form an R-hadron \fxnote{first use.
-Define here if not in LLP section} with SM quarks and propogate some measureable distance away from the IP before decaying.
+Define here if not in LLP section} with SM partons and propogate some measureable distance away from the IP before decaying.
 
@@
 Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically unaccessable, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
-The ISR jet in process (1) is not physically required; it simply provides something for the gluinos to recoil off of so the MET signal isn't lost \fxnote{My interpretation.
-Run it by someone who knows stuff}.
+The ISR jet in process (1) gives the gauginos something to recoil off of so the MET signal isn't lost \fxnote{My interpretation.
+Run it by someone who knows stuff.
+Maybe just leave this out but be prepared to explain it?}.
 
@@
     This analysis uses the muon system to look for pairs of muons that arrive out of time with bunch crossings.
-The main backgrounds to such a signal are cosmics, beam halo, and muon system noise.
-Beam halo and muon system noise are easily removed by the selection criteria, but distinguishing signal from cosmics requires a more nuanced approach.
-After generating signal MC and modeling cosmics from data obtained in dedicated cosmic runs, the authors found that cosmics and signal could be differentiated using time-of-flight information from the muon system RPCs and DTs.
-Essentially, the direction of muon momentum could be gleaned from the timing information, and the authors required outgoing muons in both the upper and lower hemispheres.
+The main backgrounds to such a signal are cosmic muons, beam halo\fxnote{explain}, and muon system noise.
+Beam halo and muon system noise are easily removed by the selection criteria, but distinguishing signal from cosmic muons requires a more nuanced approach.
+After generating signal MC and modeling cosmic muons from data obtained in dedicated cosmic runs, the authors found that cosmic muons and signal could be differentiated using time-of-flight information from the muon system RPCs and DTs.
+Essentially, the direction of muon momentum could be gleaned from the timing information, and the authors required outgoing muons in both the upper and lower hemispheres.\fxnote{Get cartoon from Juliette}
 
@@
 In all cases, the expected background was less then one event.
-After unblinding, the observed number of events is exactly zero in every lifetime scenerio.
+Exactly zero events are observed in every lifetime scenario.
 These results are then interpreted as upper limits on the signal production cross section \fxnote{include limit plots or table}, which are the first limits for stopped particles that decay to muons at the LHC.
@@
     No significant excess over predicted background is observed, so the results are interpreted as upper limits in the production cross section - mass plane for the considered models.
-By comparing the observed and theoretical limits, the authors also extract mass limits for the gluinos, stops, and staus in various models.
+By comparing the observed limits and theoretical predictions, the authors also extract mass limits for the gluinos, stops, and staus in various models.
 \fxnote{Include plots - table is too big and too many numbers to list}
@@
 \section{Experimental Viability of Natural SUSY}
+    \fxnote{Andrew says: This should really be your most important section.
+You should try to bring together the results of the searches you talked about (and of other long-lived particle searches and even of more general SUSY searches) and explain what they mean for a possible natural explanation of EWSB.
+At what point can we claim that there is no natural solution, or at least that there is no natural solution in terms of SUSY?
+Essentially, nobody cares about what you talked about in Section 6; what's important is that you can give these results a meaningful context in the bigger picture of a natural explanation of EWSB.}
+
     When building a natural SUSY model, certain constraints are nearly unavoidable\fxnote{Dangerous.
@@
     \fxnote{How do LLPs open doors to naturalness and which of those doors have we already closed?} 
+    Opening to the possibility of long-lived sparticles increases the parameter space in which natural SUSY could be hiding. LLP analyses such as the ones described in \fxnote{Section whatever}
 

### 2017-07-27 tex/draft.tex
Update SM to reflect Andrew's comments

@@
     The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing \fxnote{weak word} accuracy.
-The SM consists of 12 spin-1/2 particles, the fermions, that make up all observed matter; 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces; and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
+The SM consists of 12 spin-$\frac{1}{2}$ particles, the fermions, that make up all observed matter; 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces; and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
 
-    All SM particles transform according to the gauged symmetry group SU(3)cxSU(2)LxU(1)Y, where SU(3)c is associated with color charge, SU(2)L is associated with weak isospin, and U(1)Y is associated with weak hypercharge.
-The gauge bosons are associated with the generators of these groups, thus there are 8 gluons associated with SU(3)c, three W bosons associated with SU(2)L, and 1 B boson associated with U(1)Y.
+    All SM particles transform according to the gauged symmetry group $\SUthreecSUtwoLUoneY$, where $\SUthreec$ is associated with color charge, $\SUtwoL$ is associated with weak isospin, and $\UoneY$ is associated with weak hypercharge.
+The gauge bosons are associated with the generators of these groups, thus there are 8 gluons associated with $\SUthreec$, three W bosons associated with $\SUtwoL$, and one B boson associated with $\UoneY$.
+The physical gauge bosons, which are linear combinations of the Ws and B, are the $\Wp$, $\Wm$, $\Z$, and photon ($\gamma$).
 The fermions are catagorized by which representation of each group they fit into.
-For example, SU(3)c distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and SU(2)L distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
-Finally, different values of weak hypercharge further distignuish SM particles according to the Gell-Mann\fxnote{em-dash}Nishijima formula, $iY=2(Q-I3$.
+For example, $\SUthreec$ distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and $\SUtwoL$ distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
+Finally, weak hypercharge further distignuishes SM particles according to the Gell-Mann--Nishijima formula, $Y=Q-I_3$, where Q is electric charge and $I_3$ is the third component of weak isospin.
 
-    The Higgs potential has a nonzero vacuum expectation value (VEV), which spontaneously breaks SU(2)LxU(1)Y to U(1)EM while leaving SU(3)c unscathed.
-Once the dust settles, the B and 3 W bosons have been mixed to produce the W+, W-, Z bosons that mediate the weak force and the photon that mediates electromagnetism.
-\fxnote{Andrew says the next sentence isn't quite right.
-3 of 4 DOF from complex Higgs field are eaten by W+,W-,Z.
-Remaining DOF becomes physical Higgs boson.
-Masses don't come from broken generators.
-Read about it then fix} 3 of the 4 generators are broken in the process, leaving 3 extra degrees of freedom that ultimately become the masses of the W+, W-, and Z bosons while the remaining symmetry is associated with electric charge.
-Furthermore, expanding the Higgs field about its VEV produces mass terms for the quarks and charged leptons, thus giving mass to all massive SM particles.\fxnote{Fermion masses ad-hoc, not fundamental, says Andrew}  \fxnote{probably show a little math}\fxnote{Why can't we add explicit mass terms to SM lagrangian w/o Higgs?
-Summarize section 1 of Andrew's paper}
+    Experimentally, the $\Wpm$, $\Z$, quarks, and charged leptons are massive\fxnote{Gloss over neutrino mass?}.
+Explicit mass terms for the fermions or gauge bosons would violate the chiral and gauge symmetries of the SM Lagrangian, however, so $\SUtwoLUoneY$ must be broken.
+Specifically, the nonzero vacuum expectation value (VEV) of the Higgs field spontaneously breaks $\SUtwoLUoneY$ to $\UoneQ$.
+In the process, three of the four degrees of freedom associated with the complex Higgs doublet become the longitudinal polarizations of $\Wpm$ and $\Z$, giving them mass.
+The remaining degree of freedom is the physical Higgs boson.
+Expanding the Higgs field about its VEV produces Yukawa interactions such as those shown below.
+These terms are interpreted as giving the quarks and charged leptons mass, where the mass of each particle is given by the product of the Higgs VEV and the coupling constant.
 
-    \fxnote{kinda funny wording throughout. Maybe it would be better to trade some words for math?}
-    All SM particles interact with virtual particles through loop interactions.
-These interactions lead to corrections to SM parameters such as particle masses.
-It is common to write a given parameter as a linear combination of its 'bare' (uncorrected) value and its corrections.\fxnote{Not wrong, but sounds funny.
-Of course we write it that way when talking about a sum of diagrams} As the only fundamental scalar in the SM, the Higgs is uniquely affected by these corrections.\fxnote{Explain why scalars are more sensitive.
-Show math probably} The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the Higgs bare mass and the terms that correct it.
+    \fxnote{Yukawa terms go here}
+
+    SM parameters, such as particle masses\fxnote{what else is corrected.
+How?}, are corrected by interactions with virtual particles through loop diagrams.
+Figure\fxnote{make and reference diagrams}, for example, shows the largest SM corrections to the Higgs and electron masses.
+Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale at which the SM is valid.
+The fermions and gauge bosons, on the other hand, only depend logarithmically\fxnote{check.
+be able to work out example} on $\Lambda$.
+The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the bare Higgs mass and the terms that correct it.
+
+    \fxnote{Feynman diagrams go here}
 
@@
     \fxnote{Never really talked about the effective theory concept or dimensional analysis}
-    The naturalness criterion can be stated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order 1, (2) An effective theory should not be sensitive to small variations in the parameters of higher-energy theory, and (3) any dimensionless parameter much smaller than 1 must be protected by a custodial symmetry.
-When applied to the Higgs mass, naturalness leads to what's known as the 'hierarchy problem' or unacceptable levels of 'fine tuning'.
+    The naturalness criterion can be stated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of higher-energy theory, and (3) any dimensionless parameter much smaller than one must be protected by a custodial symmetry.
+When applied to the Higgs mass, naturalness leads to what's known as the `hierarchy problem' or unacceptable levels of `fine tuning'.
 These issues are unpacked below.
@@
 Use Jaxodraw probably} Order($10^{32}$) corrections imply that the bare Higgs mass must be negative and also order($10^{32}$) to reproduce the experimetnally known value.
-In fact, the bare mass and corrections must match to 1 part in $\approx 10^{30}$.
+In fact, the bare mass and corrections must match to one part in $\approx 10^{30}$.
 While it's entirely possible that these two numbers just so happen to match so perfectly, many \fxnote{weak} feel that such miraculous fine tuning must be a hint that some deeper physical mechanism is at work.
@@
 The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
-stop or smuon), and the spin-1/2 superpartners to the SM bosons are given the name of their SM counterpart with "ino" tacked on to the end (e.g.
+stop or smuon), and the spin-$\frac{1}{2}$ superpartners to the SM bosons are given the name of their SM counterpart with "ino" tacked on to the end (e.g.
 Higgsino or wino).
@@
 Exactly zero events are observed in every lifetime scenario.
-These results are then interpreted as upper limits on the signal production cross section \fxnote{include limit plots or table}, which are the first limits for stopped particles that decay to muons at the LHC.
+These results are then interpreted as upper limits on the signal production cross section\fxnote{and mass limits}\fxnote{include limit plots or table}, which are the first limits for stopped particles that decay to muons at the LHC.
 

### 2017-07-27 tex/draft.tex
Thoroughly edit Naturalness section

@@
 
-\usepackage[draft]{fixme}
+\usepackage[final]{fixme}
 \fxsetup{layout=footnote}
 \usepackage[left]{lineno}
-\usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref}
+\usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx}
 \usepackage{fullpage}
@@
 \doublespacing
-\linenumbers
+%\linenumbers
 \pagenumbering{arabic}
@@
     The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing \fxnote{weak word} accuracy.
-The SM consists of 12 spin-$\frac{1}{2}$ particles, the fermions, that make up all observed matter; 12 spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces; and 1 fundamental scalar, the Higgs boson, which will be described in detail below.
+The SM consists of \num{12} spin-$\frac{1}{2}$ particles, the fermions, that make up all observed matter; \num{12} spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces; and one fundamental scalar, the Higgs boson, which will be described in detail below.
 
     All SM particles transform according to the gauged symmetry group $\SUthreecSUtwoLUoneY$, where $\SUthreec$ is associated with color charge, $\SUtwoL$ is associated with weak isospin, and $\UoneY$ is associated with weak hypercharge.
-The gauge bosons are associated with the generators of these groups, thus there are 8 gluons associated with $\SUthreec$, three W bosons associated with $\SUtwoL$, and one B boson associated with $\UoneY$.
+The gauge bosons are associated with the generators of these groups, thus there are \num{8} gluons associated with $\SUthreec$, three W bosons associated with $\SUtwoL$, and one B boson associated with $\UoneY$.
 The physical gauge bosons, which are linear combinations of the Ws and B, are the $\Wp$, $\Wm$, $\Z$, and photon ($\gamma$).
@@
 How?}, are corrected by interactions with virtual particles through loop diagrams.
-Figure\fxnote{make and reference diagrams}, for example, shows the largest SM corrections to the Higgs and electron masses.
-Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale at which the SM is valid.
+Figure\fxnote{make and reference diagrams}, for example, shows the potential corrections to the Higgs and electron masses.
+Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid.
 The fermions and gauge bosons, on the other hand, only depend logarithmically\fxnote{check.
@@
     \fxnote{cite guidice naturally and t'hooft naturalness}
-    \fxnote{Haven't specifically said 'hierarchy problem. Is that bad?}
-    \fxnote{Never really talked about the effective theory concept or dimensional analysis}
-    The naturalness criterion can be stated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of higher-energy theory, and (3) any dimensionless parameter much smaller than one must be protected by a custodial symmetry.
-When applied to the Higgs mass, naturalness leads to what's known as the `hierarchy problem' or unacceptable levels of `fine tuning'.
-These issues are unpacked below.
+    \fxnote{Never mentioned dimensional analysis}
 
-    Experimentally, the mass of the Higgs boson is 125 GeV, a value that must be achieved by a linear combination of the bare mass and loop diagram corrections.
-The scale of the loop corrections is proportional to the square of the cutoff scale of the SM, which is the highest energy at which the SM is valid.
-If, hypothetically, the SM is valid all the way up to the Planck scale (where quantum gravity becomes important), then Higgs mass corrections would be order($MP^2$) $\approx 10^{32}$ GeV.
+    The naturalness criterion can be formulated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of the higher-energy theory, and (3) any dimensionless parameter much smaller than unity must be protected by a custodial symmetry.
+Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory\fxnote{This is my weakest point because I don't understand it as well as I'd like to.
+It's also wordy and maybe repetative}.
+This discussion focuses on statement (3), which is in some ways a more nuanced version of (1) that explains cases where dimensional analysis fails.
 
-    \fxnote{Point is that corrections come in with different signs and individual terms are huge.
-Really weird that they would cancel out so perfectly.
-Maybe add feynman diagrams to illustrate.
-Use Jaxodraw probably} Order($10^{32}$) corrections imply that the bare Higgs mass must be negative and also order($10^{32}$) to reproduce the experimetnally known value.
-In fact, the bare mass and corrections must match to one part in $\approx 10^{30}$.
-While it's entirely possible that these two numbers just so happen to match so perfectly, many \fxnote{weak} feel that such miraculous fine tuning must be a hint that some deeper physical mechanism is at work.
+    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$.
+Experimentally, the Higgs mass is \SI{125}{GeV}\fxnote{cite CMS, ATLAS}, a value that must be achieved by the sum of the bare mass and all corrections.
+Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely.
+In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{GeV}), where quantum gravity becomes important.
+While it's possible that the bare mass and corrections just so happen to almost perfectly cancel, such miraculous fine tuning could also be a hint that some deeper physical mechanism is at work.
 That is, either some previously unknown symmetry is protecting the Higgs mass or the cutoff scale is order(TeV).
 
-    \fxnote{Confusing, says Andrew.
-Maybe add math}  Before digging into possible solutions to this problem\fxnote{specify}, one other question must be addressed: why doesn't this same argument apply to all SM particles?
-The answer comes from naturalness statement (3) above.
-As a fundamental scalar, the Higgs boson lacks the chiral or gauge symmetries enjoyed by the fermions and vector bosons, respectively.
-These two symmetries cause the symmetry of the SM to be enhanced when the fermion and vector boson masses are set to 0.
-\fxnote{work out fermion case?} Setting the higgs mass to 0 in no way increases the symmetry of the theory, so we have no reason to expect it to be small.
+    As a fundamental scalar, the Higgs is doubly cursed.
+As explained in \fxnote{reference SM section}, $\mHiggs$ is quadratically sensitive to $\Lambda$, but that's not all: the Higgs field also lacks the chiral and gauge symmetries enjoyed by the fermions and gauge bosons.
+These symmetries act as the custodial symmetries mentioned in naturalness statement (3) in that they protect the fermion and gauge boson masses from large corrections.
+Because the SM chiral and gauge symmetries only apply to the massless theory, the SM symmetry group would be enlarged if fermions and gauge bosons were massless.
+That is, if the fermions and gauge bosons were massless at tree level, the chiral and gauge symmetries would cause their masses to be uncorrected to all orders in perturbation theory.
+As massive particles, however, the chiral and gauge symmetries instead guarantee that any corrections to their tree-level masses are proportional to their tree-level masses, preventing any large fine tuning between correction terms.
 
@@
 Nature might just be that way.
-Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to resolving this problem\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
+Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to the apparently unnatural Higgs mass\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
 Arguments against naturalness often involve the anthropic principle, which claims that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
@@
 Finally, the dominant BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below.
-\fxnote{didn't mention composite higgs}
-
-    \fxnote{Optional paragraph about non-Higgs unnaturalness:    There are other unnatural quantities that people worry about in physics.
-I know of two off the top of my head: (1) thetaQCD in the strong CP problem (2) the cosmological consant.
-The strong CP problem comes from the fact that QCD technically allows CP violation even though such violation has never been observed.
-The degree of violation is parameterized as thetaQCD, which recasts the problem into the naturalness context of 'why is thetaQCD so small?'.
-The cosmological constant is experimentally $\approx$60 to $\approx$120 orders of magnitude smaller than the predicted value \fxnote{predicted how?}.
-While these issues deserve serious attention, they will not be considered further here}
 

### 2017-07-28 tex/draft.tex
Edit SUSY section

@@
 \section{Supersymmetry}
-    Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions.
-In its simplest form, SUSY results in one new boson for every SM fermion and one new fermion for every SM boson \fxnote{and an extra Higgs field - probably should mention it.
-Make sure I understand it either way}.
-The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
+    \fxnote{seems like I should mention that naturalness favors lighter sparticles}  
+    Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions\fxnote{I need to be better at explaining exactly what this means}.
+In its simplest form, SUSY results in one new boson for every SM fermion, one new fermion for every SM boson, and one new Higgs doublet.\fxnote{make sure I understand the new Higgs doublet} The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
 stop or smuon), and the spin-$\frac{1}{2}$ superpartners to the SM bosons are given the name of their SM counterpart with "ino" tacked on to the end (e.g.
 Higgsino or wino).
-Together the superpartners to the SM particles are known as sparticles.
+Collectively the superpartners to the SM particles are known as sparticles.\fxnote{cite martin}
 
     When calculating contributions from loop diagrams, one finds that fermion loops differ in sign from boson loops, which means that in SUSY every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
-In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory.
-\fxnote{show example diagram with contribution?}
+In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory, as shown below.
 
-    But the lack of sparticles in collider searches and everyday life tells us that SUSY must be broken.
-If SUSY were exact, every superpartner would have the exact same mass as its SM counterpart, which means all sparticles would have been found at the same energy scales as SM particles.
+    \fxnote{exact SUSY diagrams and correction term goes here}
+
+    Exact SUSY also requires that sparticles have the same mass as their SM counterparts, so the lack of sparticles in collider searches implies that SUSY must be broken.
+With broken susy, the same diagram as above produces a correction of the form
+
+    \fxnote{broken SUSY correction term goes here}
+
     The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenemena.

### 2017-07-28 tex/draft.tex
edit llp section

@@
     The SUSY variants most relevant to this discussion are those that are motivated by naturalness and \fxnote{and/or?} produce a signal that could be missed by common SUSY search techniques.
-Specifically, we are interested in SUSY models that predict new long-lived particles (LLPs).
-\fxnote{incomplete sentence} That is, particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
+Specifically, we are interested in SUSY models that predict new long-lived particles (LLPs), which are defined as particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
 This category includes everything from particles that decay at \fxnote{give ballparky number ($\approx$100um?)} to particles that propagate through the entire detector.
 
-    In the SM and in BSM theories, LLPs result from one of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
+    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
 In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the the lightest particles carrying their respective conserved quantities.
-Neutrons and muons, on the other hand, are long-lived beause the proton and electron masses leave them little phase space in which to decay \fxnote{Mention that they have small couplings b/c weak force and high-mass intermediate particle is involved too}.
-\fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}
+Neutrons and muons, on the other hand, are long-lived for reasons (2), (3), and (4).
+Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay.
+\fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}\fxnote{Add diagrams?}
 
-    In SUSY models, LLPs arise for the same basic reasons, and different SUSY models meet different LLP criteria in different ways.
-The most common\fxnote{bad langauge.
-Andrew suggests 'most straightforward' or 'most ad-hoc'} SUSY LLP occurs in models with conserved R-partity, which is a proposed symmetry that protects many models from proton decay\fxnote{Be prepared to show this.
+    In SUSY models, LLPs arise for the same basic reasons, and different SUSY models produce LLPs in different ways.
+The most straightforward SUSY LLP occurs in models with conserved R-partity, a proposed symmetry that prevents proton decay\fxnote{Be prepared to show this.
 Maybe add some diagrams illustrating proton decay w/o R-parity}.
@@
 Conserving the product of R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
-A neutral LSP could show up in collider searches as significant missing energy, making MET the conventional SUSY signature in many searches.
+A neutral LSP could show up in collider searches as missing energy (MET), making MET a key signature in many conventional searches.
 
-    On the other hand, models with R-parity violation (RPV) produce long-lived, but not perfectly stable LSPs when RPV terms have small coupling constants.
-Luckily, RPV models can still avoid proton decay by allowing either terms that violate baryon number or terms that violate lepton number, but not both.
+    \fxnote{Diagrams showing some combination of proton decay, stable LSP, and RPV LSP}
+
+    On the other hand, models with weakkly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs.
+Luckily, RPV models can still avoid proton decay by allowing either terms that violate baryon number or terms that violate lepton number, but not both\fxnote{cite something}.
 A similar situation arises in GMSB models where the gravitino is the LSP.
@@
 
-    LLPs from highly-virtual intermediate particles can occur in models such as split SUSY, where the scalar sparticles are significantly more massive than the gauginos.
+    LLPs can also arise from particular SUSY mass spectra.
+Models in the Split\fxnote{capitalize?}  SUSY paradigm, for example, propose that the scalar sparticles are significantly more massive than the gauginos.
 In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark.
-\fxnote{cite kilian} \fxnote{mention that split throws out naturalness motivation?}\fxnote{Add diagrams}
-
-    \fxnote{There is no zino.
-Maybe I meant bino?
-Neutralinos and charginos are the physical states that are linear combos of winos, bino, higgsinos} The degenerate mass spectra of other SUSY models can also give rise to LLPs.
-In some AMSB models \fxnote{explain AMSB?}, for example, the zino and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
+\fxnote{cite kilian} \fxnote{mention that split throws out naturalness motivation?}\fxnote{Add diagrams} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the zino\fxnote{no such thing.
+Maybe I meant bino or general neutralino?} and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
 The wino then becomes long-lived when its decay is suppressed by the lack of available phase space.
 \fxnote{cite R\&S out of this world}
-    \fxnote{merge last 2 paragraphs under 'mass spectra lead to LLP' concept?}
-    \fxnote{never said anything about hidden valley or dark sector stuff. Never said the word R-hadron. Never said stealth or displaced SUSY. Should I?} 
     \fxnote{Andrew says don't worry about mentioning models that don't come up in the searches, but be prepared to explain the basic ideas behind HV, dark sector and how they result in LLP}

### 2017-07-28 tex/draft.tex
Edit CMS detector

@@
 \usepackage[left]{lineno}
-\usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx}
+\usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx,cancel}
 \usepackage{fullpage}
@@
     All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$.
-Experimentally, the Higgs mass is \SI{125}{GeV}\fxnote{cite CMS, ATLAS}, a value that must be achieved by the sum of the bare mass and all corrections.
+Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}\fxnote{cite CMS, ATLAS}, a value that must be achieved by the sum of the bare mass and all corrections.
 Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely.
-In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{GeV}), where quantum gravity becomes important.
+In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important.
 While it's possible that the bare mass and corrections just so happen to almost perfectly cancel, such miraculous fine tuning could also be a hint that some deeper physical mechanism is at work.
@@
 Arguments against naturalness often involve the anthropic principle, which claims that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
-Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than 3 spatial dimensions, which lowers the Planck mass itself.
+Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck mass itself.
 Finally, the dominant BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below.
@@
 Conserving the product of R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
-A neutral LSP could show up in collider searches as missing energy (MET), making MET a key signature in many conventional searches.
+A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional searches.
 
@@
     \fxnote{Add LHC description}  
+    \fxnote{define eta, coordinate system in general}  
     \fxnote{Mention that ATLAS is similar}  
@@
     \fxnote{cite cms experiment at the cern lhc}
-    The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from 14 TeV\fxnote{Mention lower-energy runs} proton-proton collisions at the Large Hadron Collider (LHC).
-To meet this goal, CMS combines information from several subdetectors nested radially in and around a 4-T superconducting solenoid.
-All together, CMS is 21.6 m long, 14.6 m across, and weighs approximately 12500 tons.
+    The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC).
+To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{4}{\tesla} superconducting solenoid.
+All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}.
 The subdetectors that make up CMS are described below.
@@
     \fxnote{cite CMS TDR, jinst 12 c02033}
-    \fxnote{what about readout, cooling, etc?}
     \fxnote{mention that analyses below used pre-upgrade tracker}
     \fxnote{mention stereo modules and be able to explain stereo modules}
-    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.\fxnote{out-of-fielder may not know about 'track' or 'vertex'} The tracker is subdivided into two regions: at r $<$ 20 cm, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near 0.1\%.
+    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.\fxnote{out-of-fielder may not know about 'track' or 'vertex'} The tracker is subdivided into two regions: at $\mathrm{r}<\SI{20}{cm}$, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near \SI{0.1}{\percent}.
 Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
 
-    The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million silicon pixels, each of which covers an active area of 100 by 150 $um^2$.
-The pixels are spread between four barrel layers (BPIX) at 2.9 $<$ r $<$ 16 cm and 3 endcap rings\fxnote{Andrew says it's 'disc', not 'ring'.
-Each disc is composed of two concentric rings of modules} (FPIX) at 29 $<$ z $<$ 52 cm.
-The upgraded pixel tracker should provide 4-hit tracking out to eta $<$ 2.4 and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
+    The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately \num{124} million silicon pixels, each of which covers an active area of \num{100} by \SI{150}{\micro\meter^2}.
+The pixels are spread between four barrel layers (BPix) at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks (FPix) at $\num{29} < \mathrm{z} < \SI{52}{cm}$.
+The upgraded pixel tracker should provide 4-hit tracking out to $\eta < \num{2.4}$ and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
 
-    Just outside the pixel tracker, the silicon strip tracker (SST) occupies the 20 $<$ r $<$ 116 cm and $|z|$ $<$ 282 cm region of CMS.
-Composed of 9.3 million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly 196 $m^2$.
+    Just outside the pixel tracker, the silicon strip tracker (SST) occupies the $\num{20} < r < \SI{116}{cm}$ and $\lvert z \rvert < \SI{282}{cm}$ region of CMS.
+Composed of \num{9.3} million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly \SI{196}{m^2}.
 At each trigger, the strip output voltage is read out via optical link.
@@
     \fxnote{cite CMS TDR}
-    \fxnote{talk about readout?}
-    \fxnote{More in the way of concept/how stuff works?}
-    After traversing the inner tracker, a particle would next encounter the electromagnetic calorimeter (ECAL).
-As a homogeneous scintillation calorimeter, ECAL uses 61200 lead tunstate crystals in the barrel and 7324 in each endcap to reconstruct the energy deposited during electromagnetic showers.
-Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere\fxnote{Andrew says 'radius', not 'length', and use accent!} length = 2.2 cm), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
-The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields \fxnote{say B-field part better}.
+    \fxnote{I define EE & EB but never use those definitions}
+    After traversing the inner tracker, particles next encounter the electromagnetic calorimeter (ECAL).
+As a homogeneous scintillation calorimeter, ECAL uses \num{61200} lead tunstate crystals in the barrel and \num{7324} in each endcap to reconstruct the energy deposited during electromagnetic showers.
+Lead tungstate crystals allow for a fast (\SI{80}{\percent} of light within \SI{25}{ns}), compact (radiation length = \SI{0.89}{cm}), fine-grained (Moli\`ere radius = \SI{2.2}{cm}), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
+The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necesitates photodetectors with intrinsic gain that work in magnetic fields.
 
-    The barrel section (EB) extends radially from 129 to 177 \fxnote{look up} cm and covers a pseudorapidity\fxnote{define} range of 0 to 1.479.
-The crystals are tapered to approximately project back to the IP but not so perfectly that likely particle trajectories align with cracks.
-Each crystal is approximately one Moliere radius wide and 25.8 radiation lengths deep.
+    The barrel section (EB) extends radially from \num{129} to \SI{177}{cm} and covers a pseudorapidity range of \num{0} to \num{1.479}.
+The crystals are tapered to approximately project back to the IP\fxnote{define if not already} but not so perfectly that likely particle trajectories align with cracks.
+Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.
 
-    The crystals in each endcap section (EE) are arranged in an x-y grid that starts at $|z|$ = 315 cm and covers a pseudorapidity range of 1.479 to 3.0.
+    The crystals in each endcap section (EE) are arranged in an x-y grid that starts at $\lvert z \rvert = \SI{315}{cm}$ and covers a pseudorapidity range of \num{1.479} to \num{3.0}.
 Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals.
@@
     \fxnote{cite CMS TDR}
-    \fxnote{talk about readout?}
-    The hadronic calorimeter (HCAL) uses 3.7mm plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers.
-Embedded wavelength-shifting fibers capture the scintillation light and transfer it to clear fibers so it can eventually be read out by hybrid photodiodes.
+    \fxnote{define HB & HF never to be used}
+    The hadronic calorimeter (HCAL) uses \SI{3.7}{mm} plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers.
+Embedded wavelength-shifting fibers capture the scintillation light and transfer it to clear fibers to be read out by hybrid photodiodes.
 
-    The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers \fxnote{check}, each of which contains 14 \fxnote{check} brass plates and covers an area of 0.087 x 0.087 in eta-phi \fxnote{get a feel for this area}.
-In addition, an extra layer (or two at eta = 0) of scintillator tiles sits just outside the solenoid.
-This extra layer, known as hadron outer (HO), spans a pseudorapidty range of -1.26 to 1.26 and increases the minimum effective HCAL interaction length to greater than 11.8.
+    The barrel section (HB) spans a pseudorapidty range of \num{-1.4} to \num{1.4} and has \num{2304} towers \fxnote{check}, each of which contains \num{14} \fxnote{check} brass plates and covers an area of \num{0.087} x \SI{0.087}{in} $\eta-\phi$ \fxnote{get a feel for this area}.
+In addition, an extra layer (or two at $\eta = \num{0}$)of scintillator tiles sits just outside the solenoid.
+This extra layer, known as hadron outer (HO), spans a pseudorapidty range of \num{-1.26} to \num{1.26} and increases the minimum effective HCAL interaction length to greater than \num{11.8}.
 
-    Each endcap spans a pseudorapidity range of 1.3 to 3.0 with 14 towers in eta and 5 to 10 degree phi segmentation.
-Also, a steel and quartz fiber forward calorimeter (HF) sits 11.2 m from the interaction pipe in a pseudorapidty range of 3.0 to 5.0.
+    Each endcap spans a pseudorapidity range of \num{1.3} to \num{3.0} with \num{14} towers in eta and \num{5} to \SI{10}{\degree} $\phi$ segmentation.
+Also, a steel and quartz fiber forward calorimeter (HF) sits \SI{11.2}{m} from the interaction pipe in a pseudorapidty range of \num{3.0} to \num{5.0}.
 In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline.
@@
     \fxnote{cite cms experiment at the cern lhc}
-    CMS employs a 4 T superconducting solenoid to aid in the measurement of charged particle momenta.
-The solenoid consists of 2168 turns of Nb-Ti superconducting cable and has an inner diameter of 6 m and a length of 12.5 m.
+    CMS employs a \SI{4}{T} superconducting solenoid to aid in the measurement of charged particle momenta.
+The solenoid consists of \num{2168} turns of Nb-Ti superconducting cable and has an inner diameter of \SI{6}{m} and a length of \SI{12.5}{m}.
 The flux returns through an iron yoke that also houses the muon system.
-The significant \fxnote{quantify?} bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of 10\% for muons up to 1 TeV.
+The significant \fxnote{quantify?} bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of \SI{10}{\percent} for muons up to \SI{1}{\tera\electronvolt}.
 
@@
     \fxnote{Specifically mention CMS design specs to meet physics goals?}
-    The muon system (MS), which is the outermost subdetector, detects muons with 3 varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps.
-The choice of detector varies between barrel and endcap due to the difference in neutron-induced background, muon rates, and magnetic field strength.
+    The muon system (MS), which is the outermost subdetector, detects muons with \num{3} varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps.
+The choice of detector varies between barrel and endcap due to the difference in neutron-induced background\fxnote{what?} , muon rates, and magnetic field strength\fxnote{why does B matter?}.
 The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
@@
 
-    In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at 4.0, 4.9, 5.9, and 7.9 m.
-\fxnote{Say how DT works?} The maximum drift length is 2 cm and the single point resolution is 200 um.
-When reconstructing a vector describing the muon momentum, the phi precision is better than 100 um in position and 1 mrad in direction.
+    In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at \num{4.0}, \num{4.9}, \num{5.9}, and \SI{7.9}{m}.
+The maximum drift length is \SI{2}{\cm} and the single point resolution is \SI{200}{\cm}.
+When reconstructing a vector describing the muon momentum, the $\phi$ precision is better than \SI{100}{\micro\m} in position and \SI{1}{\milli\radian} in direction.
 
-    Each muon endcap detector (ME) is composed of 234 CSCs and 4 RPC stations \fxnote{figure out exactly what RPC station means and say that instead}.
+    Each muon endcap detector (ME) is composed of \num{234} CSCs and four RPC stations \fxnote{figure out exactly what RPC station means and say that instead}.
 Each CSC has six gas gaps with radial cathode strips and nearly perpendicualar planes of anode wires.
 The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements.
-All in all, the CSC spacial resolution is approximately 200 um and the angular resolution is approximately 10 mrad.
+All in all, the CSC spacial resolution is approximately \SI{200}{\micro\m} and the angular resolution is approximately \SI{10}{\milli\radian}.
 
@@
     \fxnote{Is entire detector read out at L1?}
-    \fxnote{Mention fpgas in L1 or more details about HLT?}
-    \fxnote{Sloppy, but I'm getting tired}
-    The trigger reduces the data writing rate from the 40 MHz collision rate to less than 1 kHz so that events can be written to tape.
+    The trigger reduces the data writing rate from the \SI{40}{\mega\hertz} collision rate to less than \SI{1}{\kilo\hertz} so that events can be written to tape.
 The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT).
-L1 uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, MET\fxnote{define}, and mu) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
+L1 uses input from ECAL, HCAL, and MS that represents physics objects ($\mathrm{e}$/$\gamma$, $\tau$, jets, $\mu$, and $\MET$) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
 The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz.
@@
 The result is then interpreted as an upper limit on the gluino mass and pair-production cross section as a function of gluino lifetime.
-For an LSP neutralino mass of 100 GeV, the gluino mass limit is approximately 2000 GeV for lifetimes in the 20 ps to 10 ns range.
+For an LSP neutralino mass of \SI{100}{\giga\electronvolt}, the gluino mass limit is approximately \SI{2000}{\giga\electronvolt} for lifetimes in the 20 ps to 10 ns range.
 \fxnote{Include plots}
@@
     In addition to the above criteria, the authors developed a new muon reconstruction algorithm, called displaced standalone (DSA), that uses only muon system hits and does not constrain the location of the primary vertex in any way.
-The full selection requires exactly one good DSA track in each hemisphere with pT greater than 50 GeV, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement.
+The full selection requires exactly one good DSA track in each hemisphere with pT greater than \SI{50}{\giga\electronvolt}, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement.
 Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0) minimize background from beam halo and cosmics.
@@
 What if Linda knows how to avoid them?}.
-Specifically, the higgsino, which affects mH at tree level; the stop, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be heavy enough to pull mH up to 125 GeV\fxnote{Do I really understand this?} but light enough to avoid excessive fine tuning.
+Specifically, the higgsino, which affects mH at tree level; the stop, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be heavy enough to pull mH up to \SI{125}{\giga\electronvolt}\fxnote{Do I really understand this?} but light enough to avoid excessive fine tuning.
 Furthermore, the stop and gluino masses are correlated -\fxnote{m-dash?} a large difference between the two would be another source of fine tuning.

### 2017-07-28 tex/draft.tex
Most of the typesetting

@@
 \subsection{Overview}
-    \fxnote{Add LHC description}  
     \fxnote{define eta, coordinate system in general}  
-    \fxnote{Mention that ATLAS is similar}  
-    \fxnote{Maybe mention PDFs. Definitely know about them}  
+    \fxnote{Mention that ATLAS is similar, says Andrew}  
+    \fxnote{Maybe mention PDFs. Definitely know about them, says Andrew}  
     \fxnote{cite cms experiment at the cern lhc}
-    The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC).
+    The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), which is a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 to the present.
 To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{4}{\tesla} superconducting solenoid.
@@
     \fxnote{mention that analyses below used pre-upgrade tracker}
-    \fxnote{mention stereo modules and be able to explain stereo modules}
-    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.\fxnote{out-of-fielder may not know about 'track' or 'vertex'} The tracker is subdivided into two regions: at $\mathrm{r}<\SI{20}{cm}$, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near \SI{0.1}{\percent}.
+    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
+The tracker is subdivided into two regions: at $\mathrm{r}<\SI{20}{cm}$, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near \SI{0.1}{\percent}.
 Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
@@
 \subsection{Overview}
-    LLPs leave distinct signatures that differentiate LLP signals from SM backgrounds but also add complexity to LLP analyses.
-CMS and ATLAS were generally designed to detect and reconstruct stable particles from prompt decays, so LLP analyses often need to stray from the traditional analysis path in terms of object reconstruction \fxnote{really reconstruction?
-Maybe object definition?}, background estimation, and which data tier to use \fxnote{data tier is too jargony}.
-This paper will focus on four complementary LLP signatures: displaced vertices, disappearing tracks, slow-moving particles, and particles that stop completely before decaying.
+    LLPs leave distinct signatures that differentiate signal from SM background but also add complexity to LLP analyses.
+CMS and ATLAS were designed to reconstruct stable particles from prompt decays, so LLP searches are often forced to stray from the traditional analysis path in terms of object reconstruction\fxnote{really reconstruction?
+Maybe object definition?} and background estimation.
+This report focuses on four complementary LLP signatures: displaced vertices, disappearing tracks, slow-moving particles, and particles that stop completely before decaying.
 
-    Displaced vertices and disappearing tracks both look for particles that are unstable on detector timescales \fxnote{quantify?}.
-Displaced vertices searches are sensitive to LLPs that decay to visible particles in the inner volume \fxnote{specify} of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point \fxnote{wordy}.
+    Displaced vertices and disappearing tracks both look for\fxnote{reword.
+the vertices and tracks don't look for anything} particles that are unstable on detector timescales.
+Displaced vertex searches are sensitive to LLPs that decay to visible particles in the inner volume \fxnote{specify} of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point \fxnote{wordy}.
 Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed.
@@
     Slow and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
-Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles \fxnote{redundant}, which normally \fxnote{quantify} have beta\fxnote{define} $>$ 0.9.
+Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles \fxnote{redundant}, which normally \fxnote{quantify} have $\beta=\frac{v}{c} > \num{0.9}$.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
@@
 ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity.
-The search is sensitive to LLPs with lifetimes in the 20 ps to 10 ns range.
+The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range.
 
@@
 LRT is run after the standard tracking algorithm and uses only hits that were not used in standard track reconstruction.
-By relaxing d0, z0, and number of hits requirements, LRT is able to reconstruct tracks that point back to DVs.
+By relaxing d0, z0,\fxnote{define} and number of hits requirements, LRT is able to reconstruct tracks that point back to DVs.
 
@@
 
-    After estimating 0.02 +- 0.02 background events, exactly 0 are observed.
+    After estimating $\num{0.02} \pm \num{0.02}$ background events, exactly zero are observed.
 The result is then interpreted as an upper limit on the gluino mass and pair-production cross section as a function of gluino lifetime.
-For an LSP neutralino mass of \SI{100}{\giga\electronvolt}, the gluino mass limit is approximately \SI{2000}{\giga\electronvolt} for lifetimes in the 20 ps to 10 ns range.
+For an LSP neutralino mass of \SI{100}{\giga\electronvolt}, the gluino mass limit is approximately \SI{2000}{\giga\electronvolt} for lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range.
 \fxnote{Include plots}
@@
     Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
-Specifically, models with winos as the lightest gauginos, such as many AMSB models, will have a chargino NLSP with an observable lifetime (0.2 ns is a typical estimate) that eventaully decays to the neutralino LSP and, commonly, a pion.
+Specifically, models with winos as the lightest gauginos, such as many AMSB models, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate) that eventaully decays to the neutralino LSP and, commonly, a pion.
 The nearly-degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
@@
 
-    Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 and CMS before 2017 should increase sensitivity to decays at shorter radii \fxnote{I haven't mentioned previous iterations when talking about other analyses}.
-The ALTAS search presented here is sensitive to LLP lifetimes of approximated 10 ps to 10 ns \fxnote{make sure I'm talking about lifetime sensitivity in the same way across analyses}.
+    Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 datataking and CMS before 2017 datataking should increase sensitivity to decays at shorter radii \fxnote{I haven't mentioned previous iterations when talking about other analyses}.
+The ALTAS search presented here is sensitive to LLP lifetimes of approximated \SI{10}{\pico\s} to \SI{10}{\nano\s} \fxnote{make sure I'm talking about lifetime sensitivity in the same way across analyses}.
 
@@
 
-    After estimating the background by extrapolating data from the cosmic-enriched region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculated the expected background for LLP lifetimes ranging from 100 ns to 1 us.
+    After estimating the background by extrapolating data from the cosmic-enriched region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculated the expected background for LLP lifetimes ranging from \SI{100}{\nano\s} to \SI{1}{\micro\s}.
 In all cases, the expected background was less then one event.
@@
 
-    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume beta$\approx$1 and $|q|$ = e.
+    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume $\beta \approx \num{1}$ and $\lvert q \rvert = e$.
 Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge.
@@
 
-    \fxnote{I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes beta$\approx$1.
+    \fxnote{I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes $\beta \approx \num{1}$.
 Zig-zag offset is used to estimate beta.
@@
 
-    The authors estimate the signal-region background using an ABCD method in which events are binned in a 2D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region \fxnote{Do I need to explain this?
+    The authors estimate the signal-region background using an ABCD method in which events are binned in a 2-D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region \fxnote{Do I need to explain this?
 If I do, I should be more clear}.
@@
 What if Linda knows how to avoid them?}.
-Specifically, the higgsino, which affects mH at tree level; the stop, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be heavy enough to pull mH up to \SI{125}{\giga\electronvolt}\fxnote{Do I really understand this?} but light enough to avoid excessive fine tuning.
-Furthermore, the stop and gluino masses are correlated -\fxnote{m-dash?} a large difference between the two would be another source of fine tuning.
+Specifically, the Higgsino\fxnote{careful, there could be multiple Higgsinos.
+Do I mean 'lightest Higgsino'?}, which affects mH at tree level; the stop\fxnote{mention that stop is more important than other sfermions b/c large yukawa coupling?
+I'll have to clarify that somewhere}, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be light enough to avoid excessive fine tuning.\fxnote{diagrams?} Furthermore, the stop and gluino masses are correlated --- a large difference between the two would itself be unnatural.
 
-    Natural SUSY scenarios, then, are most likely to be constrained by limits on stop and gluino masses due to the strong interaction of these two objects as opposed to the colorless Higgsino\fxnote{Dear lord, I don't understand why I can't figure out how to word this sentence}.
+    Natural SUSY scenarios, then, are most likely to be constrained by limits on the stop, gluino, and Higgsino masses.
+The Higgsino, however, does not carry color charge and is far less likely to be produced at the LHC,\fxnote{things get wordy and repetative after this} which means that stop and gluino limits will be the most important experimental constraints on natural SUSY.
 Demanding naturalness also constrains the messenger scale of SUSY breaking\fxnote{Make sure I understand this.
@@
 
-    Indeed, limits on mStop and mGluino from conventional SUSY searches wipe out much of the natural parameter space\fxnote{quantify?
+    Indeed, limits on mStop and mGluino from conventional SUSY searches wipe out much of the natural parameter space from prompt decays\fxnote{quantify?
 That would require getting into how one quantifies fine tuning} for many models with decoupled first and second geration fermions, baryonic RPV, or compressed spectra that minimize missing energy while the natural MSSM is completely excluded.\fxnote{Good spot for sweet Cornering plots}\fxnote{Use ATLAS SUSY summary plot too.

### 2017-07-29 tex/draft.tex
Edit through displaced vertices (inclusive)

@@
 \subsection{Overview}
-    LLPs leave distinct signatures that differentiate signal from SM background but also add complexity to LLP analyses.
-CMS and ATLAS were designed to reconstruct stable particles from prompt decays, so LLP searches are often forced to stray from the traditional analysis path in terms of object reconstruction\fxnote{really reconstruction?
+    LLPs leave distinct signatures that differentiate them from SM backgrounds but also add complexity to LLP analyses.
+CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays, so LLP searches are often forced to stray from the traditional analysis path in terms of object reconstruction\fxnote{really reconstruction?
 Maybe object definition?} and background estimation.
-This report focuses on four complementary LLP signatures: displaced vertices, disappearing tracks, slow-moving particles, and particles that stop completely before decaying.
+This report focuses on four complementary LLP signatures: displaced vertices, disappearing tracks, low-velocity particles, and particles that stop completely before decaying.
 
-    Displaced vertices and disappearing tracks both look for\fxnote{reword.
-the vertices and tracks don't look for anything} particles that are unstable on detector timescales.
-Displaced vertex searches are sensitive to LLPs that decay to visible particles in the inner volume \fxnote{specify} of the detector and leave tracks that can be traced back to a vertex that is sufficiently displaced from the nominal interaction point \fxnote{wordy}.
+    Displaced vertex and disappearing track analyses both look for particles that are unstable on detector timescales.
+Displaced vertex searches are sensitive to LLPs that decay to visible particles within the inner volume \fxnote{specify} of the detector, leaving tracks that point back to a vertex some measurable distance from the nominal interaction point (IP).
 Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed.
-Together, these two types of analyses cover \fxnote{something something} parameter space of LLPs that decay on detector timescales.
+Together, these two types of analyses cover a wide range of lifetimes and topologies for LLPs that decay on detector timescales\fxnote{dangerous as hell.
+Be really good at giving a quantitative explanation of this sentence}.
 
-    Slow and stopped particle searches are both sensitive to LLPs that are detector-stable but far more massive than any stable SM particle.
-Searches for low-velocity particles use ionization energy loss per unit distance (dE/dX) and time-of-flight (TOF) measurements to look for particles that are moving more slowly than the expected SM particles \fxnote{redundant}, which normally \fxnote{quantify} have $\beta=\frac{v}{c} > \num{0.9}$.
+    Slow and stopped particle searches, on the other hand, are sensitive to detector-stable\fxnote{define?} LLPs that are far more massive\fxnote{be able to quantify} than any stable SM particle.
+The lower velocity of these high-mass particles shows up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) and longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
@@
     \fxnote{cite CONF-2017-026}
-    LLPs that decay before reaching the inner tracker but still live longer than the vast majority of SM particles can be identified with a displaced vertex (DV).
-That is, a reconstructed vertex far from the nominal interaction point.
-ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity.
-The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range.
+    LLPs that live longer than most SM particles but decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}.
+ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity.\fxnote{make sure I can explain why met and multiplicity} The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range\fxnote{Am I defining sensitivity range consistently across analyses?}.
 
-    This search uses a simplified model in the split SUSY paradigm as a benchmark.
-In the simplified model, gluinos are kinematically accessible while squarks are not.
-The relevant process, then, is pair produced gluinos that decay to a quark and virtual squark, which then decays to a quark and the LSP, which is presumed to be a neutralino \fxnote{steal diagram from andrew's preapproval.
+    This search\fxnote{repetative wording} uses a simplified benchmark model in the split SUSY paradigm where gluinos are kinematically accessible but squarks are not.
+The relevant process, shown in \fxnote{reference figure}, is pair-produced gluinos that decay to a quark-\fxnote{how to punctuate?}virtual squark pair.
+The virtual squark then decays to a quark and the LSP, presumed to be a neutralino\fxnote{have I defined neutralino?}\fxnote{why is this a reasonable assumption?} \fxnote{steal diagram from andrew's preapproval.
 I can't access it - ask andrew}.
-Because the squark mass is so high, the gluino lives long enough to form an R-hadron \fxnote{first use.
-Define here if not in LLP section} with SM partons and propogate some measureable distance away from the IP before decaying.
+The large mass of the intermediate squark suppresses the gluino decay, giving the gluino enough time to form an R-hadron\fxnote{first use.
+Define here if not in LLP section} that propagates some measureable distance before decaying.
 
-    Jets and MET are reconstructed as in standard analyses, but special care must be taken when looking for displaced tracks.
-The standard ATLAS tracking algorithm constrains the transverse and longitudinal impact parameters of potential tracks, so the authors employ an additional algorithm, referred to as large-radius tracking (LRT).
+    Jets and MET are reconstructed as in conventional analyses, but dispaced vertices demand special care when identifying tracks.
+The standard ATLAS tracking algorithm constrains the transverse and longitudinal impact parameters ($\mathrm{d}_0$ and $\mathrm{z}_0$, respectively) of potential tracks, so the authors employ an additional algorithm, referred to as large-radius tracking (LRT).
 LRT is run after the standard tracking algorithm and uses only hits that were not used in standard track reconstruction.
-By relaxing d0, z0,\fxnote{define} and number of hits requirements, LRT is able to reconstruct tracks that point back to DVs.
+By relaxing requirements on $\mathrm{d}_0$, $\mathrm{z}_0$, and number of hits, LRT is able to reconstruct tracks that point back to DVs.
 
-    Because no SM process will produce events that meet the mass and track multiplicity requirements on the DV, only instrumental backgrounds are considered.
-Specifically, the authors consider hadronic interactions in detector material, incorrectly combined vertices from short-lived SM particles, and incorrectly added hits from unrelated tracks to low-mass vertices.
+    Because no SM process produces events that meet the mass and track multiplicity requirements on the DV, only instrumental backgrounds are considered.
+Specifically, the authors consider hadronic interactions in detector material, incorrectly combined vertices from short-lived SM particles, and hits from unrelated tracks that are incorrectly added to low-mass vertices\fxnote{unnecessary details?
+I need to get better at explaining this} .
 
-    The authors minimize the effect of hadronic interactions by vetoing the material-dense regions of the detector and estimate the residual background by extrapolating from the low-mass region, which is dominated by hadronic interactions.
+    The authors minimize the effect of hadronic interactions by vetoing the material-dense regions of the detector\fxnote{cool figure to steal} and estimate the residual background by extrapolating from the low-mass region, which is dominated by hadronic interactions.
 After a dedicated study, the background from merged vertices was found to be negligable.

### 2017-07-29 tex/draft.tex
Edit analyses and edit/expand viability

@@
 
-\title{Naturalness and Long-lived Beyond the Standard Model Particles}
+\title{Naturalness and Long-Lived Beyond the Standard Model Particles}
 \author{Bryan Cardwell}
@@
 In its simplest form, SUSY results in one new boson for every SM fermion, one new fermion for every SM boson, and one new Higgs doublet.\fxnote{make sure I understand the new Higgs doublet} The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
-stop or smuon), and the spin-$\frac{1}{2}$ superpartners to the SM bosons are given the name of their SM counterpart with "ino" tacked on to the end (e.g.
+stop or smuon), and the spin-$\frac{1}{2}$ superpartners to the SM bosons are given the name of their SM counterpart with ``ino" tacked on to the end (e.g.
 Higgsino or wino).
@@
     The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenemena.
-A handful of models with particular approaches to SUSY breaking that are particularly prominant or particularly relevant to naturalness or long-lived particles are gauge-mediated susy breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating SUSY (RPV).
+A handful of models with particular approaches to SUSY breaking that are particularly prominant or particularly relevant to naturalness or long-lived particles are gauge-mediated susy breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), split\fxnote{capitalize} SUSY, and R-parity violating SUSY (RPV).
 The details of these models will be explored as needed throughout this paper.
 
-\section{Long-lived Particles}
+\section{Long-Lived Particles}
     The SUSY variants most relevant to this discussion are those that are motivated by naturalness and \fxnote{and/or?} produce a signal that could be missed by common SUSY search techniques.
@@
 The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
-Combining MS and tracker measurements improves the muon pT\fxnote{define} resolution at high momenta where the tracker pT resolution declines \fxnote{quantify or show std plot?}.
+Combining MS and tracker measurements improves the muon pT\fxnote{define} resolution at high momenta where the tracker $\pT$ resolution declines \fxnote{quantify or show std plot?}.
 
@@
 \subsection{Overview}
+    \fxnote{steal jamie's cartoon?}  
     LLPs leave distinct signatures that differentiate them from SM backgrounds but also add complexity to LLP analyses.
-CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays, so LLP searches are often forced to stray from the traditional analysis path in terms of object reconstruction\fxnote{really reconstruction?
+CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays, so LLP searches are often forced\fxnote{the searchers are forced, not the searches} to stray from the traditional analysis path in terms of object reconstruction\fxnote{really reconstruction?
 Maybe object definition?} and background estimation.
-This report focuses on four complementary LLP signatures: displaced vertices, disappearing tracks, low-velocity particles, and particles that stop completely before decaying.
+This report focuses on four complementary LLP signatures: displaced vertices, disappearing tracks, low-velocity particles, and particles that come to a stop before decaying.
 
-    Displaced vertex and disappearing track analyses both look for particles that are unstable on detector timescales.
+    Displaced vertex and disappearing track analyses both look for\fxnote{again, analysts look, not analyses} particles that are unstable on detector timescales.
 Displaced vertex searches are sensitive to LLPs that decay to visible particles within the inner volume \fxnote{specify} of the detector, leaving tracks that point back to a vertex some measurable distance from the nominal interaction point (IP).
@@
     Slow and stopped particle searches, on the other hand, are sensitive to detector-stable\fxnote{define?} LLPs that are far more massive\fxnote{be able to quantify} than any stable SM particle.
-The lower velocity of these high-mass particles shows up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) and longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$.
-Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
-These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings that could be due to the decay of stopped particles.
+The lower velocity of these high-mass particles shows up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$\fxnote{cite something}.
+Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy\fxnote{how long and how small?}.
+These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings.
 
-    These four approaches cover a wide range of LLP lifetimes that would be missed in traditional searches.
+    These\fxnote{I've been saying `these' a lot recently} four approaches cover a wide\fxnote{how wide} range of LLP lifetimes that would be missed in traditional searches.
 The next section will look  at a recent example of each analysis type from either ATLAS or CMS.
@@
     \fxnote{cite CONF-2017-026}
-    LLPs that live longer than most SM particles but decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}.
+    \fxnote{Specify dataset}
+    LLPs that decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}\fxnote{Is it still a DV if it decays in active material somewhere?}.
 ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity.\fxnote{make sure I can explain why met and multiplicity} The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range\fxnote{Am I defining sensitivity range consistently across analyses?}.
@@
     \fxnote{nice cartoon feynman diagrams of signal processes}
+    \fxnote{Specify dataset}
     Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
-Specifically, models with winos as the lightest gauginos, such as many AMSB models, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate) that eventaully decays to the neutralino LSP and, commonly, a pion.
+Specifically, models with winos as the lightest gauginos\fxnote{have these words been defined?}, such as many AMSB models\fxnote{why amsb?
+what is amsb?}, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate\fxnote{why?
+how typical?}) that eventaully decays to the neutralino LSP and, commonly, a pion\fxnote{why?}.
 The nearly-degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
-The low-momentum pion is then unlikely to be constructed, which results in a disappearing track.
+The low-momentum pion is then unlikely to be reconstructed, which results in a disappearing track.
 
     Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 datataking and CMS before 2017 datataking should increase sensitivity to decays at shorter radii \fxnote{I haven't mentioned previous iterations when talking about other analyses}.
-The ALTAS search presented here is sensitive to LLP lifetimes of approximated \SI{10}{\pico\s} to \SI{10}{\nano\s} \fxnote{make sure I'm talking about lifetime sensitivity in the same way across analyses}.
+The ALTAS search presented here is sensitive to LLP lifetimes of approximately \SI{10}{\pico\s} to \SI{10}{\nano\s} \fxnote{make sure I'm talking about lifetime sensitivity in the same way across analyses}.
 
-    The authors consider two signal processes: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET.
-Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically unaccessable, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
-The ISR jet in process (1) gives the gauginos something to recoil off of so the MET signal isn't lost \fxnote{My interpretation.
-Run it by someone who knows stuff.
-Maybe just leave this out but be prepared to explain it?}.
+    The authors consider two signal processes: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET\fxnote{add diagrams}.
+Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically unaccessable\fxnote{why?}, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
 
     Disappearing track candidates, called pixel tracklets, are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard reconstruction algorithm.
-The pixel tracklets are required to pass several isolation, pT, and quality requirements such as number of pixel layer hits.
-Finally, the disappearing criteria is enforced by requiring exactly zero associated hits in the subsequent tracking layer.
-Event selection requires one pixel tracklet, no electron or muon candidates (to suppress ttbar W/Z+j processes), and the MET and jet requirements associated with either of the two production modes described above.
+The pixel tracklets are required to pass several isolation, $\pT$\fxnote{has $\pT$ been defined?}, and quality requirements such as number of pixel layer hits.
+Finally, the disappearing tracks are selected by requiring exactly zero associated hits in the subsequent tracking layer.
+Event selection requires one pixel tracklet, no electron or muon candidates (to suppress $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes\fxnote{why?
+be able to explain}), and the $\MET$ and jet requirements associated with either of the two production modes described above\fxnote{be able to explain} .
 
-    Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by pixel hits that don't have the proper hits from the next tracking layer associated to them, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon \fxnote{lots of words}.
-These backgrounds come primarily from ttbar and W+jets processes, and estimates for each type of background are obtained from data.
+    Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
+These backgrounds come primarily from $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and estimates for each type of background are obtained from data.
 \fxnote{I initially wrote a whole big thing about how each bg was estimated, but I'm thinking it was overkill}
 
-    No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass gluon mass plane for the QCD production process \fxnote{hopefully will be way clearer after texing in sparticle symbols}.
+    No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass-gluon mass plane for the QCD production process \fxnote{hopefully will be way clearer after texing in sparticle symbols}.
 \fxnote{Either include plots or say numbers}
@@
     \fxnote{Add calorimeter search?}  
+    \fxnote{Specify dataset}
     \fxnote{cite CMS PAS EXO-17-004}
@@
     This analysis is interpreted in the context of two potential LLPs: gluinos and multiply charged massive particles (mchamps).
-Long-lived gluinos can appear in models such as Split SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light.
-After being pair produced, gluinos could form R-hadrons and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.
+Long-lived gluinos can appear in models such as split\fxnote{capitalize?} SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light.
+After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.
 The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.
@@
 The main backgrounds to such a signal are cosmic muons, beam halo\fxnote{explain}, and muon system noise.
-Beam halo and muon system noise are easily removed by the selection criteria, but distinguishing signal from cosmic muons requires a more nuanced approach.
-After generating signal MC and modeling cosmic muons from data obtained in dedicated cosmic runs, the authors found that cosmic muons and signal could be differentiated using time-of-flight information from the muon system RPCs and DTs.
+Beam halo and muon system noise are easily removed by selection criteria, but distinguishing signal from cosmic muons requires a more nuanced approach.
+After generating signal MC\fxnote{defined?} and modeling cosmic muons from data obtained in dedicated cosmic runs, the authors found that cosmic muons and signal could be differentiated using TOF information from the muon system RPCs and DTs.
 Essentially, the direction of muon momentum could be gleaned from the timing information, and the authors required outgoing muons in both the upper and lower hemispheres.\fxnote{Get cartoon from Juliette}
@@
     In addition to the above criteria, the authors developed a new muon reconstruction algorithm, called displaced standalone (DSA), that uses only muon system hits and does not constrain the location of the primary vertex in any way.
-The full selection requires exactly one good DSA track in each hemisphere with pT greater than \SI{50}{\giga\electronvolt}, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement.
-Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0) minimize background from beam halo and cosmics.
+The full selection requires exactly one good DSA track in each hemisphere with $\pT$ greater than \SI{50}{\giga\electronvolt}, no reconstructed vertices\fxnote{why?}, and several criteria related to the quality of the reconstructed track and timing measurement.
+Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0) minimize background from beam halo and cosmic muons\fxnote{be able to explain how}.
 
-    After estimating the background by extrapolating data from the cosmic-enriched region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculated the expected background for LLP lifetimes ranging from \SI{100}{\nano\s} to \SI{1}{\micro\s}.
-In all cases, the expected background was less then one event.
+    After estimating the background by extrapolating data from the cosmic-enriched\fxnote{enriched how?
+be able to explain} region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculate the expected background for LLP lifetimes ranging from \SI{100}{\nano\s} to \SI{1}{\micro\s}.
+In all cases, the expected background is less then one event.
 Exactly zero events are observed in every lifetime scenario.
@@
     \fxnote{cite CMS EXO7-010}
+    \fxnote{Specify dataset}
     \fxnote{nice dE/dx plot (fig 1)}
-    Particles that live for more than a couple ns \fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
+    Particles that live for more than a couple ns\fxnote{how do I typeset standalone units?} \fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
 If such a particle is also sufficiently massive, it can be catigorized as a heavy stable charged particle (HSCP).
-HSCPs are characterterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material.
+HSCPs are characterterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material\fxnote{redundant w/ overview.
+Probably better explained here than there}.
 Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss.
 
-    HSCPs will often be misidentified or unobserved by standard reconstruction algorithms and analysis criteria, which tend to assume $\beta \approx \num{1}$ and $\lvert q \rvert = e$.
-Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge.
-This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY.
+    HSCPs will often be misidentified or missed entirely by standard reconstruction algorithms and analysis criteria, which tend to assume $\beta \approx \num{1}$ and $\lvert q \rvert = e$.
+Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge\fxnote{insert feynman diagrams}.
+This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY\fxnote{why?}.
 
@@
 Zig-zag offset is used to estimate beta.
-Not sure where to fit it in.} \fxnote{Worth mentioning tracker-only vs tracker+TOF}
+Not sure where to fit it in.} \fxnote{Worth mentioning tracker-only vs tracker+TOF?}
 
-    The trigger requires all events to have either a high-pT muon or large MET.
-The high-pT muon trigger is more efficient for all benchmark models except the case where the R-hadron becomes neutral before reaching the MS.
-In the case where the R-hadron does not leave a track in the MS, the large MET trigger should recover some events.
+    The trigger requires all events to have either a high-$\pT$ muon or large $\MET$.
+The high-$\pT$ muon trigger is more efficient for all benchmark models except the case where the R-hadron becomes neutral before reaching the MS.
+In the case where the R-hadron does not leave a track in the MS, the large MET trigger should recover some events.\fxnote{Clunky wording}
 
     The authors estimate the signal-region background using an ABCD method in which events are binned in a 2-D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region \fxnote{Do I need to explain this?
-If I do, I should be more clear}.
+I glossed over the fact that they used both an ABCD and an ABCDEFGHI}.
 Systematic uncertainties are introduced in background estimation, signal acceptance, and integrated luminosity.
@@
 By comparing the observed limits and theoretical predictions, the authors also extract mass limits for the gluinos, stops, and staus in various models.
-\fxnote{Include plots - table is too big and too many numbers to list}
+\fxnote{Include plots}
 
@@
 
+    Interpreting current limits in the context of naturalness requires some set of criteria that determine if a model is natural.
+No well-defined, universally-agreed-upon criteria exist, but certain themes recur in many discussions of natural model building\fxnote{better be able to confidently cite several sources}.
+The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of naturalness in light of current experimental limits\fxnote{Did I just steal Chris's langauge?}.
+
     When building a natural SUSY model, certain constraints are nearly unavoidable\fxnote{Dangerous.
@@
 Specifically, the Higgsino\fxnote{careful, there could be multiple Higgsinos.
-Do I mean 'lightest Higgsino'?}, which affects mH at tree level; the stop\fxnote{mention that stop is more important than other sfermions b/c large yukawa coupling?
-I'll have to clarify that somewhere}, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be light enough to avoid excessive fine tuning.\fxnote{diagrams?} Furthermore, the stop and gluino masses are correlated --- a large difference between the two would itself be unnatural.
+Do I mean 'lightest Higgsino'?}, which corrects $m_H$ at tree level; the stop\fxnote{mention that stop is more important than other sfermions b/c large yukawa coupling?
+I'll have to clarify that somewhere}, which corrects $m_H$ at one loop; and the gluino, which corrects mStop at one loop and therefore $m_H$ at two, must all be light enough to avoid excessive fine tuning.\fxnote{Need diagrams and correction terms for sure} Furthermore, the stop and gluino masses are correlated --- a large difference between the two would itself be unnatural.
 
     Natural SUSY scenarios, then, are most likely to be constrained by limits on the stop, gluino, and Higgsino masses.
-The Higgsino, however, does not carry color charge and is far less likely to be produced at the LHC,\fxnote{things get wordy and repetative after this} which means that stop and gluino limits will be the most important experimental constraints on natural SUSY.
-Demanding naturalness also constrains the messenger scale of SUSY breaking\fxnote{Make sure I understand this.
-Messenger scale != breaking scale?}.
-Corrections to the Higgs mass from stops and gluinos depend of the messenger scale\fxnote{reference eqs}, so natural SUSY generally prefers a lower scale.\fxnote{Either explain more thoroughly or drop completely.
+The Higgsino, however, does not carry color charge and is far less likely\fxnote{be able to quantify} to be produced at the LHC, leaving stop and gluino mass limits as the most important contraints on natural SUSY models.
+As shown in \fxnote{reference correction terms}, the size of stop and gluino corrections also depends on the messenger scale of SUSY breaking.\fxnote{Make sure I understand this.
+Messenger scale != breaking scale?}\fxnote{Either explain more thoroughly or drop completely.
 What are the consequences of a lower messenger scale?}
+
+    Two qualitative decisions must be made when analyzing the state of naturalness: (1) How best to define the degree of fine tuning in a particular model and (2) what degree of fine tuning is acceptable?
+A common, but not universal, definition for (1) is \fxnote{insert Delta eq.}, where $\alpha_i$ is a particular parameter and $\Delta_i$ is the degree of fine tuning from variations in that parameter.
+The overall degree of fine tuning for the model can then be assigned as $\max{\left(\Delta_i\right)}$, the product of $\Delta_i$, or all $\Delta_i$ added in quadrature.
+Determining the acceptable degree of fine tuning is even more open ended.
+Before null results and serious constraints started rolling in, it was common\fxnote{cite something} to refer to the $\Delta \lesssim 10$ regions of parameter space as natural.
+As models are constrained, physicists seem willing to accept greater degrees of fine tuning.
+Instead of asking, ``what degree of fine tuning should be considered natural?", Feng\fxnote{cite} proposes physicists ask themselves, ``If SUSY were discovered with such-and-such degree of fine tuning, would I consider the naturalness problem solved and move on to different research questions?" Anecdotally, Feng reports that acceptable levels of fine tuning tend to increase when the question is posed in this way.\fxnote{break into two paragraphs?}
+
+    Figure \fxnote{reference atlas SUSY limits} summarizes limits on SUSY models from ATLAS searches.
+CMS limits are generally similar\fxnote{make sure this is true}, but a recent plot was not available.
 
@@
 
-    Despite strong contraints, SUSY remains one of the least-tuned options for BSM naturalness\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.\fxnote{Good place for Feng "how much tuning is acceptable?
+    Despite strong contraints, SUSY remains one of the least-tuned options for BSM naturalness\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.\fxnote{Good place for Feng ``how much tuning is acceptable?
 discussion}
@@
 \section{Conclusion and Important Searches for 2017}
+
+\fxnote{When should symbols be italicized and when should they be mathrm'd?}
 

### 2017-07-29 tex/draft.tex
fix ^M newlines
start adding figures, eqs

@@
 \usepackage[left]{lineno}
-\usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx,cancel}
+\usepackage[demo]{graphicx}
+\usepackage{amsmath,amsthm,amssymb,mathtools,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx,cancel}
 \usepackage{fullpage}
@@
 
-\section{The Standard Model}
+\section{The Standard Model} \label{SM}
     The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing \fxnote{weak word} accuracy.
@@
 
-    All SM particles transform according to the gauged symmetry group $\SUthreecSUtwoLUoneY$, where $\SUthreec$ is associated with color charge, $\SUtwoL$ is associated with weak isospin, and $\UoneY$ is associated with weak hypercharge.
-The gauge bosons are associated with the generators of these groups, thus there are \num{8} gluons associated with $\SUthreec$, three W bosons associated with $\SUtwoL$, and one B boson associated with $\UoneY$.
+    All SM particles transform according to the gauged symmetry group\fxnote{be good at describing the meaning of `gauged symmetry group'} $\SUthreecSUtwoLUoneY$, where $\SUthreec$ is associated with color charge, $\SUtwoL$ is associated with weak isospin, and $\UoneY$ is associated with weak hypercharge.
+The gauge bosons are associated with the generators of these groups, thus there are eight gluons associated with $\SUthreec$, three W bosons associated with $\SUtwoL$, and one B boson associated with $\UoneY$.
 The physical gauge bosons, which are linear combinations of the Ws and B, are the $\Wp$, $\Wm$, $\Z$, and photon ($\gamma$).
-The fermions are catagorized by which representation of each group they fit into.
+The fermions are catagorized by which representation of each group they fit into\fxnote{make sure I'm good at explaining this}.
 For example, $\SUthreec$ distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and $\SUtwoL$ distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
@@
 How?}, are corrected by interactions with virtual particles through loop diagrams.
-Figure\fxnote{make and reference diagrams}, for example, shows the potential corrections to the Higgs and electron masses.
+Fig.~\ref{loop_diagrams}, for example, shows the potential corrections to the Higgs and electron masses.
 Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid.
@@
 
-    \fxnote{Feynman diagrams go here}
+    \noindent \begin{figure}[htbp] \begin{center}
+    \includegraphics[width=0.8\textwidth]{images/loop_diagrams}
+    \caption{Caption!\fxnote{cite something}}
+    \label{loop_diagrams}
+    \end{center} \end{figure}
 
@@
     As a fundamental scalar, the Higgs is doubly cursed.
-As explained in \fxnote{reference SM section}, $\mHiggs$ is quadratically sensitive to $\Lambda$, but that's not all: the Higgs field also lacks the chiral and gauge symmetries enjoyed by the fermions and gauge bosons.
+As explained in section \ref{SM}, $\mHiggs$ is quadratically sensitive to $\Lambda$, but that's not all: the Higgs field also lacks the chiral and gauge symmetries enjoyed by the fermions and gauge bosons.
 These symmetries act as the custodial symmetries mentioned in naturalness statement (3) in that they protect the fermion and gauge boson masses from large corrections.
@@
 That is, if the fermions and gauge bosons were massless at tree level, the chiral and gauge symmetries would cause their masses to be uncorrected to all orders in perturbation theory.
-As massive particles, however, the chiral and gauge symmetries instead guarantee that any corrections to their tree-level masses are proportional to their tree-level masses, preventing any large fine tuning between correction terms.
+As massive particles, however, the chiral and gauge symmetries instead guarantee that any corrections to their tree-level masses are proportional to their tree-level masses, preventing any large fine tuning between correction terms.\fxnote{wordy as hell}
 
@@
 Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to the apparently unnatural Higgs mass\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
-Arguments against naturalness often involve the anthropic principle, which claims that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
+Arguments against naturalness often involve the anthropic principle, which posits that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
 Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck mass itself.
-Finally, the dominant BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below.
+Finally, the dominant\fxnote{what do I mean by dominant?} BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below.
 
@@
 stop or smuon), and the spin-$\frac{1}{2}$ superpartners to the SM bosons are given the name of their SM counterpart with ``ino" tacked on to the end (e.g.
-Higgsino or wino).
-Collectively the superpartners to the SM particles are known as sparticles.\fxnote{cite martin}
+Higgsino or wino).\fxnote{describe charginos, neutralinos?} Collectively the superpartners to the SM particles are known as sparticles.\fxnote{cite martin}
 
     When calculating contributions from loop diagrams, one finds that fermion loops differ in sign from boson loops, which means that in SUSY every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
-In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory, as shown below.
+In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory, as shown in Fig.~\ref{exact_susy_correction} below.
 
-    \fxnote{exact SUSY diagrams and correction term goes here}
+    \noindent \begin{figure}[htbp] \begin{center}
+    \includegraphics[width=0.8\textwidth]{images/exact_susy_correction}
+    \caption{Caption!\fxnote{cite something}}
+    \label{exact_susy_correction}
+    \end{center} \end{figure}
 
@@
 
-    \fxnote{broken SUSY correction term goes here}
+    \noindent \begin{equation}
+    \delta \mHiggs = .
+    \label{higgs_susy_correction}
+    \end{equation}\fxnote{look up}
 
@@
 
-    Figure \fxnote{reference atlas SUSY limits} summarizes limits on SUSY models from ATLAS searches.
-CMS limits are generally similar\fxnote{make sure this is true}, but a recent plot was not available.
+    Fig.~\ref{atlas_susy_searches} summarizes limits on SUSY models from ATLAS searches. CMS limits are generally similar\fxnote{make sure this is true}, but a recent plot was not available.
+
+    \fxnote{legible when printed?}  
+    \noindent \begin{figure}[htbp] \begin{center}
+    \includegraphics[width=0.8\textwidth]{images/atlas_susy_summary}
+    \caption{Summary of current experimental limits on SUSY models from ATLAS searches.\fxnote{cite something}}
+    \label{atlas_susy_summary}
+    \end{center} \end{figure}
 

### 2017-07-29 tex/draft.tex
Add placeholders for all figures

@@
 Conserving the product of R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
-A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional searches.
+A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches.
 
-    \fxnote{Diagrams showing some combination of proton decay, stable LSP, and RPV LSP}
+    On the other hand, models with weakly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs.
+Fig.~\ref{rp_and_rpv_diagrams} shows two possible processes, one where R-parity gaurantees a stable LSP and one where RPV produces a long-lived but stable LSP.
+A similar situation arises in GMSB models\fxnote{should I describe GMSB?} where the gravitino is the LSP.
+The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs.\fxnote{cite dimopoulos low energy}\fxnote{}
 
-    On the other hand, models with weakkly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs.
-Luckily, RPV models can still avoid proton decay by allowing either terms that violate baryon number or terms that violate lepton number, but not both\fxnote{cite something}.
-A similar situation arises in GMSB models where the gravitino is the LSP.
-The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs.
-\fxnote{is now a good time to explain GMSB?}\fxnote{cite dimopoulos low energy}
+    \noindent \begin{figure}[htbp] \begin{center}
+    \includegraphics[width=0.8\textwidth]{images/rp_and_rpv_diagrams}
+        \caption{R-parity and RPV diagrams}
+    \label{rp_and_rpv_diagrams}
+    \end{center} \end{figure}
 
@@
 All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}.
-The subdetectors that make up CMS are described below.
+The subdetectors that make up CMS are shown in Fig.~\ref{cms} and described below.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/cms}
+            \caption{CMS}
+        \label{cms}
+        \end{center} \end{figure}
 
@@
         In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
-The tracker is subdivided into two regions: at $\mathrm{r}<\SI{20}{cm}$, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near \SI{0.1}{\percent}.
-Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.
+The tracker is subdivided into two regions.
+Inside \SI{20}{cm}, the pixel tracker  uses smaller\fxnote{than what?} silicon pixels to keep the occupancy near \SI{0.1}{\percent} despite the high\fxnote{specify} particle flux.
+Outside \SI{20}{\cm}, the silicon strip tracker (SST) achieves similar occupancy with larger silicon strips.\fxnote{check occupacy numbers}
 
@@
 This report focuses on four complementary LLP signatures: displaced vertices, disappearing tracks, low-velocity particles, and particles that come to a stop before decaying.
+See Fig.~\ref{jamie_cartoon} for a cartoon of several possible LLP signatures\fxnote{probably a better way to word this sentence}.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/jamie_cartoon}
+            \caption{Diagram of several LLP spectra}
+        \label{jamie_cartoon}
+        \end{center} \end{figure}
 
@@
         This search\fxnote{repetative wording} uses a simplified benchmark model in the split SUSY paradigm where gluinos are kinematically accessible but squarks are not.
-The relevant process, shown in \fxnote{reference figure}, is pair-produced gluinos that decay to a quark-\fxnote{how to punctuate?}virtual squark pair.
+The relevant process, shown in Fig.~\ref{displaced_process}, is pair-produced gluinos that decay to a quark-\fxnote{how to punctuate?}virtual squark pair.
 The virtual squark then decays to a quark and the LSP, presumed to be a neutralino\fxnote{have I defined neutralino?}\fxnote{why is this a reasonable assumption?} \fxnote{steal diagram from andrew's preapproval.
@@
 
-    Jets and MET are reconstructed as in conventional analyses, but dispaced vertices demand special care when identifying tracks.
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/displaced_process_diagram}
+        \caption{Process.}
+        \label{displaced_process}
+        \end{center} \end{figure}
+
+        Jets and $\MET$ are reconstructed as in conventional analyses, but dispaced vertices demand special care when identifying tracks.
 The standard ATLAS tracking algorithm constrains the transverse and longitudinal impact parameters ($\mathrm{d}_0$ and $\mathrm{z}_0$, respectively) of potential tracks, so the authors employ an additional algorithm, referred to as large-radius tracking (LRT).
@@
 
-    The authors minimize the effect of hadronic interactions by vetoing the material-dense regions of the detector\fxnote{cool figure to steal} and estimate the residual background by extrapolating from the low-mass region, which is dominated by hadronic interactions.
+        The authors minimize the effect of hadronic interactions by vetoing the material-dense regions of the detector (see Fig.~\ref{material_map}) and estimate the residual background by extrapolating from the low-mass region, which is dominated by hadronic interactions.
 After a dedicated study, the background from merged vertices was found to be negligable.
@@
 
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/material_map}
+        \caption{Map of material dense regions of the ATLAS detector.\fxnote{cite analysis}}
+        \label{material_map}
+        \end{center} \end{figure}
+
         After estimating $\num{0.02} \pm \num{0.02}$ background events, exactly zero are observed.
-The result is then interpreted as an upper limit on the gluino mass and pair-production cross section as a function of gluino lifetime.
+The result is then interpreted as an upper limit on the gluino mass and pair-production cross section as a function of gluino lifetime, shown in Fig.~\ref{displaced_limit}.
 For an LSP neutralino mass of \SI{100}{\giga\electronvolt}, the gluino mass limit is approximately \SI{2000}{\giga\electronvolt} for lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range.
 \fxnote{Include plots}
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/displaced_limit}
+        \caption{Limit.}
+        \label{displaced_limit}
+        \end{center} \end{figure}
 
@@
 
-    The authors consider two signal processes: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET\fxnote{add diagrams}.
+        The authors consider two signal processes, both shown in Fig.\ref{disappearing_processes}: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET\fxnote{add diagrams}.
 Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically unaccessable\fxnote{why?}, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/disappearing_processes}
+        \caption{Processes.}
+        \label{disappearing_processes}
+        \end{center} \end{figure}
 
@@
         No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass-gluon mass plane for the QCD production process \fxnote{hopefully will be way clearer after texing in sparticle symbols}.
-\fxnote{Either include plots or say numbers}
+Fig.~\ref{disappearing_limits} shows the limits for both processes.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/disappearing_limits}
+        \caption{Limits.}
+        \label{disappearing_limits}
+        \end{center} \end{figure}
 
@@
 Long-lived gluinos can appear in models such as split\fxnote{capitalize?} SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light.
-After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.
+After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs, as shown in Fig.~\ref{stopped_process}.
 The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/stopped_process}
+            \caption{Long-lived gluino proces.\fxnote{cite analysis}}
+        \label{stopped_process}
+        \end{center} \end{figure}
 
@@
 After generating signal MC\fxnote{defined?} and modeling cosmic muons from data obtained in dedicated cosmic runs, the authors found that cosmic muons and signal could be differentiated using TOF information from the muon system RPCs and DTs.
-Essentially, the direction of muon momentum could be gleaned from the timing information, and the authors required outgoing muons in both the upper and lower hemispheres.\fxnote{Get cartoon from Juliette}
+Essentially, the direction of muon momentum could be gleaned from the timing information, and the authors required outgoing muons in both the upper and lower hemispheres.
+Fig.~\ref{stopped_muon_differentiation} shows how muons from stopped particles are differentiated from cosmic muons.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/stopped_muon_differentiation}
+            \caption{Cosmic muon rejection with MS.\fxnote{cite analysis}}
+        \label{stopped_muon_differentiation}
+        \end{center} \end{figure}
 
@@
 Exactly zero events are observed in every lifetime scenario.
-These results are then interpreted as upper limits on the signal production cross section\fxnote{and mass limits}\fxnote{include limit plots or table}, which are the first limits for stopped particles that decay to muons at the LHC.
+As shown in Fig.~\ref{stopped_limits}, these results are then interpreted as upper limits on the signal production cross section and mass\fxnote{mass of what?}, which are the first limits for stopped particles that decay to muons at the LHC.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/stopped_limits}
+            \caption{Limits.\fxnote{cite analysis}}
+        \label{stopped_limits}
+        \end{center} \end{figure}
 
@@
 Probably better explained here than there}.
-Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss.
+Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss, as shown in Fig.~\ref{hscp_dedx}.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/hscp_dedx}
+            \caption{Ionization energy loss.\fxnote{cite analysis}}
+        \label{hscp_dedx}
+        \end{center} \end{figure}
 
         HSCPs will often be misidentified or missed entirely by standard reconstruction algorithms and analysis criteria, which tend to assume $\beta \approx \num{1}$ and $\lvert q \rvert = e$.
-Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge\fxnote{insert feynman diagrams}.
+Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models\fxnote{do I need figures for these?}: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge\fxnote{insert feynman diagrams}.
 This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY\fxnote{why?}.
@@
         No significant excess over predicted background is observed, so the results are interpreted as upper limits in the production cross section - mass plane for the considered models.
-By comparing the observed limits and theoretical predictions, the authors also extract mass limits for the gluinos, stops, and staus in various models.
-\fxnote{Include plots}
+By comparing the observed limits and theoretical predictions, the authors also extract mass limits for the gluinos, stops, and staus in various models, as shown in Fig.~\ref{hscp_limits}.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/hscp_limits}
+            \caption{Limits.\fxnote{cite analysis}}
+        \label{hscp_limits}
+        \end{center} \end{figure}
 

### 2017-07-30 tex/draft.tex
Add most figures

@@
 
+\usepackage[final]{graphicx}
 \usepackage[final]{fixme}
@@
 \usepackage[left]{lineno}
-\usepackage[demo]{graphicx}
+\usepackage{tikz-feynman}
 \usepackage{amsmath,amsthm,amssymb,mathtools,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx,cancel}
@@
 How?}, are corrected by interactions with virtual particles through loop diagrams.
-Fig.~\ref{loop_diagrams}, for example, shows the potential corrections to the Higgs and electron masses.
+Fig.~\ref{loop_diagrams}, for example, shows corrections to the Higgs and electron masses.
 Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid.
@@
     \noindent \begin{figure}[htbp] \begin{center}
-    \includegraphics[width=0.8\textwidth]{images/loop_diagrams}
-    \caption{Caption!\fxnote{cite something}}
+        \feynmandiagram [layered layout, horizontal=b to c] {
+            a -- [scalar] b,
+            b -- [fermion, half left] c,
+            c -- [fermion, half left] b,
+            c -- [scalar] d,
+        };
+        \qquad
+        \feynmandiagram [layered layout, horizontal=b to c] {
+            a -- [fermion] b,
+            b -- [fermion] c,
+            b -- [photon, half left] c,
+            c -- [opacity=0.0, half left] b,
+            c -- [fermion] d,
+        };
+        \caption{Higgs mass (left) corrected by fermion loop and fermion mass (right) corrected by photon loop.\fxnote{cite tikz-feyman}}
         \label{loop_diagrams}
@@
     \noindent \begin{figure}[htbp] \begin{center}
-    \includegraphics[width=0.8\textwidth]{images/exact_susy_correction}
+        \feynmandiagram [inline=(d.base), layered layout, horizontal=b to c] {
+        a -- [scalar] b,
+        b -- [fermion, half left] c,
+        c -- [fermion, half left] b,
+        c -- [scalar] d,
+    };
+    \quad + \quad
+    \feynmandiagram [baseline={(current bounding box.center)}, layered layout, horizontal=b to c] {
+        a -- [scalar] b,
+        b -- [charged scalar, half left] c,
+        c -- [charged scalar, half left] b,
+        c -- [scalar] d,
+    };
+    \quad = \quad 0 \quad
     \caption{Caption!\fxnote{cite something}}
@@
     \noindent \begin{figure}[htbp] \begin{center}
-    \includegraphics[width=0.8\textwidth]{images/rp_and_rpv_diagrams}
+    \includegraphics[width=0.3\textwidth]{images/rp_and_rpv_diagrams}
         \caption{R-parity and RPV diagrams}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/cms}
+        \includegraphics[width=0.7\textwidth]{images/cms}
             \caption{CMS}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/jamie_cartoon}
+        \includegraphics[width=0.7\textwidth]{images/jamie_cartoon}
             \caption{Diagram of several LLP spectra}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/displaced_process_diagram}
+        \feynmandiagram [layered layout, horizontal=a to b] {
+            a -- [plain, gluon] b,
+            b -- [anti charged scalar] c,
+            b -- [fermion] d,
+            c -- [anti fermion] e,
+            c -- [plain, boson] f,
+        };
         \caption{Process.}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/material_map}
+        \includegraphics[width=0.6\textwidth]{images/material_map}
         \caption{Map of material dense regions of the ATLAS detector.\fxnote{cite analysis}}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/displaced_limit}
+        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/displaced_cross_section_limit}
+        \end{center} \end{subfigure}
+        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/displaced_mass_limit}
+        \end{center} \end{subfigure}
         \caption{Limit.}
@@
 
+        \fxnote{ugh, this is too hard. just steal diagram from paper or make in jaxodraw. Maybe even use simulated event instead, but make sure I can draw these if asked?}  
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/disappearing_processes}
+        \feynmandiagram [layered layout] {
+            i1 -- [plain] a [blob],
+            i2 -- [plain] a,
+            a -- [plain, boson] b [blob],
+            a -- [plain] f1,
+            a -- [plain, boson] f2,
+            b -- [plain, boson] f3,
+            b -- [scalar] f4,
+        };
         \caption{Processes.}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/disappearing_limits}
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/disappearing_ew_limit}
+        \end{center} \end{subfigure}
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/disappearing_strong_200ps_limit}
+        \end{center} \end{subfigure}
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/disappearing_strong_1ns_limit}
+        \end{center} \end{subfigure}
         \caption{Limits.}
@@
 Long-lived gluinos can appear in models such as split\fxnote{capitalize?} SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light.
-After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs, as shown in Fig.~\ref{stopped_process}.
+After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.
+This process is exactly the same as in Fig.~\ref{displaced_process}, but in this case the gluino has enough time to form R-hadrons\fxnote{double check}.
 The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.
-
-        \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/stopped_process}
-            \caption{Long-lived gluino proces.\fxnote{cite analysis}}
-        \label{stopped_process}
-        \end{center} \end{figure}
 
@@
 
+        \fxnote{check if tof, beta, or bx is better} 
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/stopped_muon_differentiation}
+        \includegraphics[width=\textwidth]{images/stopped_reject_cosmic_tof}
         \caption{Cosmic muon rejection with MS.\fxnote{cite analysis}}
@@
 
+        \fxnote{ok to skip mchamp? Be able to explain why} 
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/stopped_limits}
+        \begin{subfigure}[htbp]{0.5\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/stopped_limit_gluino_cross_section}
+        \end{center} \end{subfigure}
+        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/stopped_limit_gluino_mass}
+        \end{center} \end{subfigure}
         \caption{Limits.\fxnote{cite analysis}}
@@
     \subsection{Heavy Stable Charged Particles}
-        \fxnote{cite CMS EXO7-010}
+        \fxnote{cite CMS EXO-15-010}
         \fxnote{Specify dataset}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/hscp_dedx}
+        \includegraphics[width=0.5\textwidth]{images/hscp_dedx}
             \caption{Ionization energy loss.\fxnote{cite analysis}}
@@
 
+        \fxnote{I show seperate trk, trk+tof limits but never explain that in text} 
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/hscp_limits}
+        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/hscp_limit_tracker_only}
+        \end{center} \end{subfigure}
+        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/hscp_limit_tracker_tof}
+        \end{center} \end{subfigure}
         \caption{Limits.\fxnote{cite analysis}}

### 2017-07-31 tex/draft.tex
add equations

@@
 
-\usepackage[final]{graphicx}
+\usepackage[draft]{graphicx}
 \usepackage[final]{fixme}
@@
 The remaining degree of freedom is the physical Higgs boson.
-Expanding the Higgs field about its VEV produces Yukawa interactions such as those shown below.
-These terms are interpreted as giving the quarks and charged leptons mass, where the mass of each particle is given by the product of the Higgs VEV and the coupling constant.
+Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}.
+These terms are interpreted as giving mass to the quarks and charged leptons mass, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $Y$.
 
-    \fxnote{Yukawa terms go here}
+    \noindent \begin{equation}
+        \mathcal{L} = -\frac{Yv}{\sqrt{2}}\bar{\psi}\psi 
+        \label{yukawa_terms}
+    \end{equation}
 
@@
 \section{Supersymmetry}
-    \fxnote{seems like I should mention that naturalness favors lighter sparticles}  
+    \fxnote{seems like I should explicitly mention that naturalness favors lighter sparticles}  
     Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions\fxnote{I need to be better at explaining exactly what this means}.
@@
     \noindent \begin{figure}[htbp] \begin{center}
-        \feynmandiagram [inline=(d.base), layered layout, horizontal=b to c] {
+        \feynmandiagram [inline=(d.base), layered layout, medium, horizontal=b to c] {
         a -- [scalar] b,
@@
     \quad + \quad
-    \feynmandiagram [baseline={(current bounding box.center)}, layered layout, horizontal=b to c] {
+    \feynmandiagram [baseline={(current bounding box.center)}, layered layout, medium, horizontal=b to c] {
         a -- [scalar] b,
@@
     Exact SUSY also requires that sparticles have the same mass as their SM counterparts, so the lack of sparticles in collider searches implies that SUSY must be broken.
-With broken susy, the same diagram as above produces a correction of the form
+With broken susy, the same diagram as above produces a correction of the form\fxnote{cite feng}
 
     \noindent \begin{equation}
-    \delta \mHiggs = .
+        \delta \mHiggs^2 = \frac{3Y^2}{8\pi^2}\left(m_{\sfermion}^2 - m_{\f}^2 \right)\ln(\Lambda^2/m_{\sfermion}^2).
     \label{higgs_susy_correction}
-    \end{equation}\fxnote{look up}
+    \end{equation}
 
@@
 A similar situation arises in GMSB models\fxnote{should I describe GMSB?} where the gravitino is the LSP.
-The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs.\fxnote{cite dimopoulos low energy}\fxnote{}
+The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs.\fxnote{cite dimopoulos low energy}
 
@@
         \fxnote{cite CMS TDR}
-        \fxnote{I define EE & EB but never use those definitions}
+        \fxnote{I define EE \& EB but never use those definitions}
         After traversing the inner tracker, particles next encounter the electromagnetic calorimeter (ECAL).
@@
         \fxnote{cite CMS TDR}
-        \fxnote{define HB & HF never to be used}
+        \fxnote{define HB \& HF never to be used}
         The hadronic calorimeter (HCAL) uses \SI{3.7}{mm} plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers.
@@
 \section{LHC Searches for Long-lived Particles}
-        \fxnote{Include diagrams for signal models} 
         \fxnote{mention which data was used for each search} 
-        \fxnote{Steal limit plots and any cool figures from papers} 
     \subsection{Overview}
@@
         \fxnote{cite CONF-2017-026}
-        \fxnote{Specify dataset}
         LLPs that decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}\fxnote{Is it still a DV if it decays in active material somewhere?}.
@@
 For an LSP neutralino mass of \SI{100}{\giga\electronvolt}, the gluino mass limit is approximately \SI{2000}{\giga\electronvolt} for lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range.
-\fxnote{Include plots}
 
@@
         \fxnote{nice cartoon feynman diagrams of signal processes}
-        \fxnote{Specify dataset}
         Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
@@
 
-        The authors consider two signal processes, both shown in Fig.\ref{disappearing_processes}: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET\fxnote{add diagrams}.
+        The authors consider two signal processes, both shown in Fig.\ref{disappearing_processes}: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET.
 Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically unaccessable\fxnote{why?}, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
@@
         \fxnote{Add calorimeter search?}  
-        \fxnote{Specify dataset}
         \fxnote{cite CMS PAS EXO-17-004}
@@
         \fxnote{cite CMS EXO-15-010}
-        \fxnote{Specify dataset}
         \fxnote{nice dE/dx plot (fig 1)}
@@
         HSCPs will often be misidentified or missed entirely by standard reconstruction algorithms and analysis criteria, which tend to assume $\beta \approx \num{1}$ and $\lvert q \rvert = e$.
-Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models\fxnote{do I need figures for these?}: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge\fxnote{insert feynman diagrams}.
+Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models\fxnote{do I need figures for these?}: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge.
 This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY\fxnote{why?}.
@@
 
-    \fxnote{legible when printed?}  
     \noindent \begin{figure}[htbp] \begin{center}

### 2017-07-31 tex/draft.tex
add sm-llp and disappearing diagrams

@@
 
-\usepackage[draft]{graphicx}
+\usepackage[final]{graphicx}
 \usepackage[final]{fixme}
@@
 In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the the lightest particles carrying their respective conserved quantities.
-Neutrons and muons, on the other hand, are long-lived for reasons (2), (3), and (4).
+Neutrons and muons, whose decays are shown in Fig.\ref{sm_llp_processes}, are long-lived for reasons (2), (3), and (4).
 Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay.
 \fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}\fxnote{Add diagrams?}
+
+        \noindent \begin{figure}[htbp] \begin{center}
+            \begin{tikzpicture}
+            \begin{feynman}
+                \vertex (n1a) {\(d\)};
+                \vertex[right=2cm of n1a] (n1b);
+                \vertex[right=2cm of n1b] (p1) {\(u\)};
+
+                \vertex[below=0.3cm of n1a] (n2) {\(u\)};
+                \vertex[below=0.3cm of n2] (n3) {\(d\)};
+
+                \vertex[below=0.3cm of p1] (p2) {\(u\)};
+                \vertex[below=0.3cm of p2]  (p3) {\(d\)};
+
+                \vertex[above=of n1b] (w);
+
+                \vertex[above=of p1] (ln) {\(\nu_l\)}; 
+                \vertex[above=of ln] (lc) {\(l^{-}\)};
+
+                \diagram* {
+                    (n1a) -- [fermion] (n1b) -- [fermion] (p1),
+                    (n2) -- [fermion] (p2),
+                    (n3) -- [fermion] (p3),
+                    (n1b) -- [boson, edge label=\(\W^{-}\)] (w),
+                    (w) -- [fermion] (lc),
+                    (ln) -- [fermion] (w),
+                };
+                \draw [decoration={brace}, decorate] (n3.south west) -- (n1a.north west)
+                node [pos=0.5, left] {\(n\)};
+                \draw [decoration={brace}, decorate] (p1.north east) -- (p3.south east)
+                node [pos=0.5, right] {\(p\)};
+            \end{feynman}
+            \end{tikzpicture}
+            \qquad\qquad
+            \feynmandiagram [layered layout, horizontal=a to b] {
+                a [particle=\(\mu\)] -- [fermion] b,
+                b -- [fermion] d [particle=\(\nu_{\mu}\)],
+                b -- [boson, edge label=\(\W^{-}\)] c,
+                c -- [fermion] e [particle=\(e\)],
+                c -- [anti fermion] f [particle=\(\nu_{e}\)],
+            };
+            \caption{Neutron and muon decays.}
+            \label{sm_llp_process}
+        \end{center} \end{figure}
 
@@
     \subsection{Overview}
-        \fxnote{steal jamie's cartoon?}  
         LLPs leave distinct signatures that differentiate them from SM backgrounds but also add complexity to LLP analyses.
@@
         \includegraphics[width=0.7\textwidth]{images/jamie_cartoon}
-            \caption{Diagram of several LLP spectra}
+            \caption{Diagram of several LLP topologies.\fxnote{cite Jamie or twiki}}
         \label{jamie_cartoon}
@@
         \fxnote{cite CONF-2017-017}
-        \fxnote{nice disappearing track cartoon}
-        \fxnote{nice cartoon feynman diagrams of signal processes}
         Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \feynmandiagram [layered layout] {
-            i1 -- [plain] a [blob],
-            i2 -- [plain] a,
-            a -- [plain, boson] b [blob],
-            a -- [plain] f1,
-            a -- [plain, boson] f2,
-            b -- [plain, boson] f3,
-            b -- [scalar] f4,
-        };
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/disappearing_ew_process}
+        \end{center} \end{subfigure}
+        \qquad
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/disappearing_qcd_process}
+        \end{center} \end{subfigure}
+        \fxnote{Can't get it to work in tikz-feynman. Just take from paper for now.} 
+        %\feynmandiagram [layered layout] {
+        %    i1 -- [plain] a [blob],
+        %    i2 -- [plain] a,
+        %    a -- [plain, boson] b [blob],
+        %    a -- [plain] f1,
+        %    a -- [plain, boson] f2,
+        %    b -- [plain, boson] f3,
+        %    b -- [scalar] f4,
+        %};
         \caption{Processes.}
@@
         \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
-        \includegraphics[width=\textwidth]{images/disappearing_strong_200ps_limit}
+        \includegraphics[width=\textwidth]{images/disappearing_qcd_200ps_limit}
         \end{center} \end{subfigure}
         \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
-        \includegraphics[width=\textwidth]{images/disappearing_strong_1ns_limit}
+        \includegraphics[width=\textwidth]{images/disappearing_qcd_1ns_limit}
         \end{center} \end{subfigure}

### 2017-07-31 tex/draft.tex
Add pixel figure, edit llp section

@@
     The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenemena.
-A handful of models with particular approaches to SUSY breaking that are particularly prominant or particularly relevant to naturalness or long-lived particles are gauge-mediated susy breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), split\fxnote{capitalize} SUSY, and R-parity violating SUSY (RPV).
+A handful of models with particular approaches to SUSY breaking that are particularly prominant or particularly relevant to naturalness or long-lived particles are gauge-mediated susy breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating SUSY (RPV).
 The details of these models will be explored as needed throughout this paper.
@@
     On the other hand, models with weakly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs.
-Fig.~\ref{rp_and_rpv_diagrams} shows two possible processes, one where R-parity gaurantees a stable LSP and one where RPV produces a long-lived but stable LSP.
 A similar situation arises in GMSB models\fxnote{should I describe GMSB?} where the gravitino is the LSP.
@@
 
-    \noindent \begin{figure}[htbp] \begin{center}
-    \includegraphics[width=0.3\textwidth]{images/rp_and_rpv_diagrams}
-        \caption{R-parity and RPV diagrams}
-    \label{rp_and_rpv_diagrams}
-    \end{center} \end{figure}
+    \fxnote{diagram or eqs for R-parity / RPV?}
 
     LLPs can also arise from particular SUSY mass spectra.
-Models in the Split\fxnote{capitalize?}  SUSY paradigm, for example, propose that the scalar sparticles are significantly more massive than the gauginos.
+Models in the Split SUSY paradigm, for example, propose that the scalar sparticles are significantly more massive than the gauginos.
 In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark.
-\fxnote{cite kilian} \fxnote{mention that split throws out naturalness motivation?}\fxnote{Add diagrams} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the zino\fxnote{no such thing.
-Maybe I meant bino or general neutralino?} and wino are the LSP and NLSP, respectively, and are nearly degenerate in mass.
-The wino then becomes long-lived when its decay is suppressed by the lack of available phase space.
-\fxnote{cite R\&S out of this world}
-    \fxnote{Andrew says don't worry about mentioning models that don't come up in the searches, but be prepared to explain the basic ideas behind HV, dark sector and how they result in LLP}
+\fxnote{cite kilian} \fxnote{mention that Split throws out naturalness motivation?} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the winos as the lightest gauginos, which leads to nearly-degenerate LSP and NLSP.
+The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space.
+\fxnote{cite R\&S out of this world via disappearing}
+
+    \fxnote{show a few SUSY spectra?}
 
@@
 The pixels are spread between four barrel layers (BPix) at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks (FPix) at $\num{29} < \mathrm{z} < \SI{52}{cm}$.
-The upgraded pixel tracker should provide 4-hit tracking out to $\eta < \num{2.4}$ and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
+The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\eta < \num{2.4}$ and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+            \includegraphics[width=0.5\textwidth]{images/pixel_old_new}
+            \caption{Diagram showing barrel pixel layers before and after the winter 2016/17 upgrade.\fxnote{cite website found through Andrew's citations}}
+            \label{cms}
+        \end{center} \end{figure}
 
@@
 
-        This search\fxnote{repetative wording} uses a simplified benchmark model in the split SUSY paradigm where gluinos are kinematically accessible but squarks are not.
+        This search\fxnote{repetative wording} uses a simplified benchmark model in the Split SUSY paradigm where gluinos are kinematically accessible but squarks are not.
 The relevant process, shown in Fig.~\ref{displaced_process}, is pair-produced gluinos that decay to a quark-\fxnote{how to punctuate?}virtual squark pair.
@@
         This analysis is interpreted in the context of two potential LLPs: gluinos and multiply charged massive particles (mchamps).
-Long-lived gluinos can appear in models such as split\fxnote{capitalize?} SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light.
+Long-lived gluinos can appear in models such as Split SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light.
 After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.

### 2017-08-01 tex/draft.tex
Major edit of Viability

@@
 Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}.
-These terms are interpreted as giving mass to the quarks and charged leptons mass, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $Y$.
+These terms are interpreted as giving mass to the quarks and charged leptons mass, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$.
 
     \noindent \begin{equation}
-        \mathcal{L} = -\frac{Yv}{\sqrt{2}}\bar{\psi}\psi 
+        \mathcal{L} = -\frac{yv}{\sqrt{2}}\bar{\psi}\psi 
         \label{yukawa_terms}
@@
     The naturalness criterion can be formulated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of the higher-energy theory, and (3) any dimensionless parameter much smaller than unity must be protected by a custodial symmetry.
-Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory\fxnote{This is my weakest point because I don't understand it as well as I'd like to.
+Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates\fxnote{verb-subject agreement} the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory\fxnote{This is my weakest point because I don't understand it as well as I'd like to.
 It's also wordy and maybe repetative}.
@@
 
+    \fxnote{Fix diagram} 
     \noindent \begin{figure}[htbp] \begin{center}
@@
     \quad + \quad
-    \feynmandiagram [baseline={(current bounding box.center)}, layered layout, medium, horizontal=b to c] {
+        \begin{tikzpicture}
+            \begin{feynman}
+                \diagram [baseline={(current bounding box.center)}, horizontal=a to c] {
                     a -- [scalar] b,
-        b -- [charged scalar, half left] c,
-        c -- [charged scalar, half left] b,
-        c -- [scalar] d,
+                    b -- [scalar] c,
             };
+                \draw (b) arc [charged scalar, start angle=270, end angle=90, radius=0.7cm];
+            \end{feynman}
+        \end{tikzpicture}
     \quad = \quad 0 \quad
-    \caption{Caption!\fxnote{cite something}}
+    \caption{Broken!\fxnote{cite something}}
     \label{exact_susy_correction}
@@
     \noindent \begin{equation}
-        \delta \mHiggs^2 = \frac{3Y^2}{8\pi^2}\left(m_{\sfermion}^2 - m_{\f}^2 \right)\ln(\Lambda^2/m_{\sfermion}^2).
+        \delta \mHiggs^2 = \frac{3y_t^2}{8\pi^2}\left(m_{\sfermion}^2 - m_{\f}^2 \right)\ln(\Lambda^2/m_{\sfermion}^2).
     \label{higgs_susy_correction}
@@
 The nearly-degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
-The low-momentum pion is then unlikely to be reconstructed, which results in a disappearing track.
+The low-momentum pion is then unlikely to be reconstructed, which results in a disappearing track~\cite{atlas_disappearing}.
 
@@
 No well-defined, universally-agreed-upon criteria exist, but certain themes recur in many discussions of natural model building\fxnote{better be able to confidently cite several sources}.
-The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of naturalness in light of current experimental limits\fxnote{Did I just steal Chris's langauge?}.
+The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits\fxnote{Did I just steal Chris's langauge?}.
 
@@
 
+    \fxnote{cite cornering} 
+    \fxnote{make sure these are logically and notationally consistent w/ earlier higgs corrections} 
+    \noindent \begin{equation}
+        \delta \mHiggs^2 = \mu^2
+        \label{higgsino_correction}
+    \end{equation}
+    \noindent \begin{equation}
+        \delta \mHiggs^2 \approx - \frac{3}{8\pi^2} y_t^2 m_{\tilde{t}}^2 \ln{\left(\frac{\Lambda}{Q}\right)}
+        \label{stop_correction}
+    \end{equation}
+    \noindent \begin{equation}
+        \delta \mHiggs^2 \approx - \frac{g_3^2 y_t^2}{4\pi^4} M_3^2 \ln{\left(\frac{\Lambda}{Q}\right)}^2
+        \label{gluino_correction}
+    \end{equation}
+
     Natural SUSY scenarios, then, are most likely to be constrained by limits on the stop, gluino, and Higgsino masses.
 The Higgsino, however, does not carry color charge and is far less likely\fxnote{be able to quantify} to be produced at the LHC, leaving stop and gluino mass limits as the most important contraints on natural SUSY models.
-As shown in \fxnote{reference correction terms}, the size of stop and gluino corrections also depends on the messenger scale of SUSY breaking.\fxnote{Make sure I understand this.
+As shown in Eqs.~\ref{stop_correction} and~\ref{gluino_correction}, the size of stop and gluino corrections also depends on $\Lambda$, the messenger scale of SUSY breaking.\fxnote{Make sure I understand this.
 Messenger scale != breaking scale?}\fxnote{Either explain more thoroughly or drop completely.
@@
     Two qualitative decisions must be made when analyzing the state of naturalness: (1) How best to define the degree of fine tuning in a particular model and (2) what degree of fine tuning is acceptable?
-A common, but not universal, definition for (1) is \fxnote{insert Delta eq.}, where $\alpha_i$ is a particular parameter and $\Delta_i$ is the degree of fine tuning from variations in that parameter.
-The overall degree of fine tuning for the model can then be assigned as $\max{\left(\Delta_i\right)}$, the product of $\Delta_i$, or all $\Delta_i$ added in quadrature.
+A common, but not universal, definition for (1) is
+
+    \fxnote{cite cornering} 
+    \noindent \begin{equation}
+        \Delta_i = \frac{\partial \ln{\mHiggs^2}}{\partial \ln{\alpha_i}} \quad ,
+        \label{fine_tuning}
+    \end{equation}
+
+    \noindent where $\alpha_i$ is a particular parameter and $\Delta_i$ is the degree of fine tuning from variations in that parameter.
+The overall degree of fine tuning for the model can then be assigned as $\max{\left(\Delta_i\right)}$.
 Determining the acceptable degree of fine tuning is even more open ended.
@@
 
-    Fig.~\ref{atlas_susy_searches} summarizes limits on SUSY models from ATLAS searches. CMS limits are generally similar\fxnote{make sure this is true}, but a recent plot was not available.
+    So, how is natural SUSY fairing?
+Fig.~\ref{atlas_susy_searches} summarizes limits on many SUSY models and topologies from ATLAS searches.
+CMS limits are generally similar\fxnote{make sure this is true}, but a recent plot was not available.\fxnote{give general summary}
 
@@
 
-    Indeed, limits on mStop and mGluino from conventional SUSY searches wipe out much of the natural parameter space from prompt decays\fxnote{quantify?
-That would require getting into how one quantifies fine tuning} for many models with decoupled first and second geration fermions, baryonic RPV, or compressed spectra that minimize missing energy while the natural MSSM is completely excluded.\fxnote{Good spot for sweet Cornering plots}\fxnote{Use ATLAS SUSY summary plot too.
-CMS's isn't updated}
+    It's often helpful to look at limits in the context of simplified models.
+Fig.~\ref{cornering_limits} does just this for the cases of Effective SUSY, RPV SUSY, Hidden Valley SUSY, and a model that combines RPV with Effective SUSY.
 
@@
 
-    Despite strong contraints, SUSY remains one of the least-tuned options for BSM naturalness\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.\fxnote{Good place for Feng ``how much tuning is acceptable?
-discussion}
+    Despite strong contraints, SUSY remains one of the least-tuned options for BSM naturalness\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.
 
@@
 \singlespacing
-\bibliography{candidacy}{}
-\bibliographystyle{auto}
+\bibliography{draft}{}
+\bibliographystyle{unsrt}
 

### 2017-08-02 tex/draft.tex
Add most references

@@
 For example, $\SUthreec$ distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and $\SUtwoL$ distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
-Finally, weak hypercharge further distignuishes SM particles according to the Gell-Mann--Nishijima formula, $Y=Q-I_3$, where Q is electric charge and $I_3$ is the third component of weak isospin.
+Finally, weak hypercharge further distignuishes SM particles according to the Gell-Mann--Nishijima formula, $Y=Q-I_3$, where Q is electric charge and $I_3$ is the third component of weak isospin~\cite{sm_intro}.
 
@@
 Explicit mass terms for the fermions or gauge bosons would violate the chiral and gauge symmetries of the SM Lagrangian, however, so $\SUtwoLUoneY$ must be broken.
-Specifically, the nonzero vacuum expectation value (VEV) of the Higgs field spontaneously breaks $\SUtwoLUoneY$ to $\UoneQ$.
+Specifically, the nonzero vacuum expectation value (VEV)\fxnote{maybe just use $v$} of the Higgs field spontaneously breaks $\SUtwoLUoneY$ to $\UoneQ$.
 In the process, three of the four degrees of freedom associated with the complex Higgs doublet become the longitudinal polarizations of $\Wpm$ and $\Z$, giving them mass.
@@
 Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}.
-These terms are interpreted as giving mass to the quarks and charged leptons mass, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$.
+These terms are interpreted as giving mass to the quarks and charged leptons mass, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$~\cite{sm_intro}.
 
@@
 
-    SM parameters, such as particle masses\fxnote{what else is corrected.
-How?}, are corrected by interactions with virtual particles through loop diagrams.
-Fig.~\ref{loop_diagrams}, for example, shows corrections to the Higgs and electron masses.
+    SM parameters, such as masses and couplings, are corrected by interactions with virtual particles through loop diagrams.
+Fig.~\ref{loop_diagrams}, for example, shows interactions that correct the Higgs and electron masses.
 Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid.
 The fermions and gauge bosons, on the other hand, only depend logarithmically\fxnote{check.
-be able to work out example} on $\Lambda$.
+be able to work out example} on $\Lambda$~\cite{dine_naturalness}.
 The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the bare Higgs mass and the terms that correct it.
@@
         };
-        \caption{Higgs mass (left) corrected by fermion loop and fermion mass (right) corrected by photon loop.\fxnote{cite tikz-feyman}}
+        \caption{Higgs mass (left) corrected by fermion loop and fermion mass (right) corrected by photon loop. Diagram created with~\cite{tikz}}
         \label{loop_diagrams}
@@
 \section{Naturalness and the Higgs mass}
-    \fxnote{cite guidice naturally and t'hooft naturalness}
-    \fxnote{Never mentioned dimensional analysis}
+    The naturalness criterion can be formulated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of the higher-energy theory, and (3) any dimensionless parameter much smaller than unity must be protected by a custodial symmetry~\cite{giudice_naturally, thooft_naturalness}.
+Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory.
+\fxnote{wordy and maybe repetative}.
+This discussion focuses on statement (3), which is in some ways a more nuanced version of (1) that also explains cases where dimensional analysis fails.
 
-    The naturalness criterion can be formulated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of the higher-energy theory, and (3) any dimensionless parameter much smaller than unity must be protected by a custodial symmetry.
-Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates\fxnote{verb-subject agreement} the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory\fxnote{This is my weakest point because I don't understand it as well as I'd like to.
-It's also wordy and maybe repetative}.
-This discussion focuses on statement (3), which is in some ways a more nuanced version of (1) that explains cases where dimensional analysis fails.
-
-    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$.
-Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}\fxnote{cite CMS, ATLAS}, a value that must be achieved by the sum of the bare mass and all corrections.
+    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$~\cite{dine_naturalness}\fxnote{show diagrams and terms?}.
+Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}~\cite{cms_higgs, atlas_higgs}, a value that must be achieved by the sum of the bare mass and all corrections.
 Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely.
-In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important.
+In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important~\cite{giudice_naturally}.
 While it's possible that the bare mass and corrections just so happen to almost perfectly cancel, such miraculous fine tuning could also be a hint that some deeper physical mechanism is at work.
-That is, either some previously unknown symmetry is protecting the Higgs mass or the cutoff scale is order(TeV).
+That is, either some previously unknown symmetry is protecting the Higgs mass or the cutoff scale is $\mathcal{O}\left(\SI{}{\tera\electronvolt}\right)$\fxnote{explain better and cite something}.
 
@@
 That is, if the fermions and gauge bosons were massless at tree level, the chiral and gauge symmetries would cause their masses to be uncorrected to all orders in perturbation theory.
-As massive particles, however, the chiral and gauge symmetries instead guarantee that any corrections to their tree-level masses are proportional to their tree-level masses, preventing any large fine tuning between correction terms.\fxnote{wordy as hell}
+As massive particles, however, the chiral and gauge symmetries instead guarantee that any corrections to their tree-level masses are proportional to their tree-level masses, preventing any large fine tuning between correction terms~\cite{giudice_naturally}.\fxnote{wordy as hell}
 
@@
 Nature might just be that way.
-Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to the apparently unnatural Higgs mass\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass.
+Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to the apparently unnatural Higgs mass\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass~\cite{craig}.
 Arguments against naturalness often involve the anthropic principle, which posits that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
 Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck mass itself.
-Finally, the dominant\fxnote{what do I mean by dominant?} BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below.
+Finally, the dominant\fxnote{what do I mean by dominant?} BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below~\cite{dine_naturalness}.
 
 \section{Supersymmetry}
-    \fxnote{seems like I should explicitly mention that naturalness favors lighter sparticles}  
+    \fxnote{seems like I should explicitly mention that naturalness favors lighter sparticles and why the stop correction is so important}
+
     Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions\fxnote{I need to be better at explaining exactly what this means}.
@@
 stop or smuon), and the spin-$\frac{1}{2}$ superpartners to the SM bosons are given the name of their SM counterpart with ``ino" tacked on to the end (e.g.
-Higgsino or wino).\fxnote{describe charginos, neutralinos?} Collectively the superpartners to the SM particles are known as sparticles.\fxnote{cite martin}
+Higgsino or wino).\fxnote{describe charginos, neutralinos?} Collectively the superpartners to the SM particles are known as sparticles~\cite{primer}.
 
     When calculating contributions from loop diagrams, one finds that fermion loops differ in sign from boson loops, which means that in SUSY every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
-In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory, as shown in Fig.~\ref{exact_susy_correction} below.
+In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory, as shown in Fig.~\ref{exact_susy_correction} below~\cite{primer}.
 
     \fxnote{Fix diagram} 
+    \fxnote{Add particle labels} 
     \noindent \begin{figure}[htbp] \begin{center}
@@
     \quad = \quad 0 \quad
-    \caption{Broken!\fxnote{cite something}}
+        \caption{Broken! Corrections to the Higgs mass from the top (left) and stop (right) cancel in exact SUSY. Diagram created with~\cite{tikz}}
     \label{exact_susy_correction}
@@
     Exact SUSY also requires that sparticles have the same mass as their SM counterparts, so the lack of sparticles in collider searches implies that SUSY must be broken.
-With broken susy, the same diagram as above produces a correction of the form\fxnote{cite feng}
+With broken SUSY, the same diagram as above produces a correction of the form~\cite{feng}
 
@@
 Specifically, we are interested in SUSY models that predict new long-lived particles (LLPs), which are defined as particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
-This category includes everything from particles that decay at \fxnote{give ballparky number ($\approx$100um?)} to particles that propagate through the entire detector.
+This category includes everything from particles that decay at 100um to particles that propagate through the entire detector\fxnote{I made up 100um.
+Find real number and cite source}.
 
-    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
+    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay\fxnote{find source to cite}.
 In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the the lightest particles carrying their respective conserved quantities.
 Neutrons and muons, whose decays are shown in Fig.\ref{sm_llp_processes}, are long-lived for reasons (2), (3), and (4).
-Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay.
-\fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}\fxnote{Add diagrams?}
+Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay\fxnote{find something to cite}.
+\fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}
 
@@
             };
-            \caption{Neutron and muon decays.}
-            \label{sm_llp_process}
+            \caption{Long-lived decays of the neutron and muon. Diagram created with~\cite{tikz}}
+            \label{sm_llp_processes}
         \end{center} \end{figure}
@@
 Conserving the product of R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
-A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches.
+A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches~\cite{primer}.
 
-    On the other hand, models with weakly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs.
+    On the other hand, models with weakly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs\fxnote{find something to cite}.
 A similar situation arises in GMSB models\fxnote{should I describe GMSB?} where the gravitino is the LSP.
-The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs.\fxnote{cite dimopoulos low energy}
+The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs~\cite{dimopoulos_low_energy}.
 
@@
 Models in the Split SUSY paradigm, for example, propose that the scalar sparticles are significantly more massive than the gauginos.
-In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark.
-\fxnote{cite kilian} \fxnote{mention that Split throws out naturalness motivation?} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the winos as the lightest gauginos, which leads to nearly-degenerate LSP and NLSP.
-The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space.
-\fxnote{cite R\&S out of this world via disappearing}
+In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark~\cite{kilian_split}.
+\fxnote{mention that Split throws out naturalness motivation?} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the winos as the lightest gauginos, which leads to nearly-degenerate LSP and NLSP.
+The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space~\cite{randall_sundrum_out_of_this_world}.
 
@@
         \fxnote{Maybe mention PDFs. Definitely know about them, says Andrew}  
-        \fxnote{cite cms experiment at the cern lhc}
-        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), which is a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 to the present.
+        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), which is a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 to the present\fxnote{say better}\fxnote{cite something?}.
 To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{4}{\tesla} superconducting solenoid.
 All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}.
-The subdetectors that make up CMS are shown in Fig.~\ref{cms} and described below.
+The subdetectors that make up CMS are shown in Fig.~\ref{cms} and described below~\cite{cms_experiment}.
 
@@
         \includegraphics[width=0.7\textwidth]{images/cms}
-            \caption{CMS}
+            \caption{The CMS detector\fxnote{Cite that website from Andrew's paper}}
         \label{cms}
@@
 Inside \SI{20}{cm}, the pixel tracker  uses smaller\fxnote{than what?} silicon pixels to keep the occupancy near \SI{0.1}{\percent} despite the high\fxnote{specify} particle flux.
-Outside \SI{20}{\cm}, the silicon strip tracker (SST) achieves similar occupancy with larger silicon strips.\fxnote{check occupacy numbers}
+Outside \SI{20}{\cm}, the silicon strip tracker (SST) achieves similar occupancy with larger silicon strips~\cite{cms_tdr}.\fxnote{check occupacy numbers}
 
@@
 The pixels are spread between four barrel layers (BPix) at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks (FPix) at $\num{29} < \mathrm{z} < \SI{52}{cm}$.
-The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\eta < \num{2.4}$ and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.
+The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\eta < \num{2.4}$ and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017~\cite{cms_pixel_upgrade}.
 
@@
             \caption{Diagram showing barrel pixel layers before and after the winter 2016/17 upgrade.\fxnote{cite website found through Andrew's citations}}
-            \label{cms}
+            \label{pixel_old_new}
         \end{center} \end{figure}
@@
 Composed of \num{9.3} million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly \SI{196}{m^2}.
-At each trigger, the strip output voltage is read out via optical link.
+At each trigger, the strip output voltage is read out via optical link~\cite{cms_pixel_upgrade}.
 
@@
 Lead tungstate crystals allow for a fast (\SI{80}{\percent} of light within \SI{25}{ns}), compact (radiation length = \SI{0.89}{cm}), fine-grained (Moli\`ere radius = \SI{2.2}{cm}), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
-The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necesitates photodetectors with intrinsic gain that work in magnetic fields.
+The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necesitates photodetectors with intrinsic gain that work in magnetic fields\cite{cms_experiment, cms_tdr}.
 
@@
         The hadronic calorimeter (HCAL) uses \SI{3.7}{mm} plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers.
-Embedded wavelength-shifting fibers capture the scintillation light and transfer it to clear fibers to be read out by hybrid photodiodes.
+Embedded wavelength-shifting fibers capture the scintillation light and transfer it to clear fibers to be read out by hybrid photodiodes\cite{cms_experiment, cms_tdr}.
 
@@
 The flux returns through an iron yoke that also houses the muon system.
-The significant \fxnote{quantify?} bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of \SI{10}{\percent} for muons up to \SI{1}{\tera\electronvolt}.
+The significant \fxnote{quantify?} bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of \SI{10}{\percent} for muons up to \SI{1}{\tera\electronvolt}\cite{cms_experiment}.
 
@@
 The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
-Combining MS and tracker measurements improves the muon pT\fxnote{define} resolution at high momenta where the tracker $\pT$ resolution declines \fxnote{quantify or show std plot?}.
+Combining MS and tracker measurements improves the muon pT\fxnote{define} resolution at high momenta where the tracker $\pT$ resolution declines \fxnote{quantify or show std plot?}\cite{cms_experiment, cms_tdr}.
 
@@
 L1 uses input from ECAL, HCAL, and MS that represents physics objects ($\mathrm{e}$/$\gamma$, $\tau$, jets, $\mu$, and $\MET$) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
-The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz.
+The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz\cite{cms_experiment, cms_trigger_upgrade}.
 
-\section{LHC Searches for Long-lived Particles}
+\section{LHC Searches for Long-lived Particles} \label {analyses}
     \fxnote{mention which data was used for each search} 
@@
         LLPs leave distinct signatures that differentiate them from SM backgrounds but also add complexity to LLP analyses.
-CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays, so LLP searches are often forced\fxnote{the searchers are forced, not the searches} to stray from the traditional analysis path in terms of object reconstruction\fxnote{really reconstruction?
+CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays\fxnote{find something to cite}, so LLP searches are often forced\fxnote{the searchers are forced, not the searches} to stray from the traditional analysis path in terms of object reconstruction\fxnote{really reconstruction?
 Maybe object definition?} and background estimation.
@@
         \includegraphics[width=0.7\textwidth]{images/jamie_cartoon}
-            \caption{Diagram of several LLP topologies.\fxnote{cite Jamie or twiki}}
+        \caption{Diagram of several LLP topologies. Image curtesy of Jamie Antonelli}
         \label{jamie_cartoon}
@@
         Displaced vertex and disappearing track analyses both look for\fxnote{again, analysts look, not analyses} particles that are unstable on detector timescales.
-Displaced vertex searches are sensitive to LLPs that decay to visible particles within the inner volume \fxnote{specify} of the detector, leaving tracks that point back to a vertex some measurable distance from the nominal interaction point (IP).
-Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed.
+Displaced vertex searches are sensitive to LLPs that decay to visible particles within the inner volume \fxnote{specify} of the detector, leaving tracks that point back to a vertex some measurable distance from the nominal interaction point (IP)~\cite{atlas_displaced}.
+Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed~\cite{atlas_disappearing}.
 Together, these two types of analyses cover a wide range of lifetimes and topologies for LLPs that decay on detector timescales\fxnote{dangerous as hell.
-Be really good at giving a quantitative explanation of this sentence}.
+Be really good at giving a quantitative explanation of this sentence}\fxnote{find something to cite}.
 
         Slow and stopped particle searches, on the other hand, are sensitive to detector-stable\fxnote{define?} LLPs that are far more massive\fxnote{be able to quantify} than any stable SM particle.
-The lower velocity of these high-mass particles shows up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$\fxnote{cite something}.
+The lower velocity of these high-mass particles shows up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$\fxnote{check this number}~\cite{cms_hscp}.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy\fxnote{how long and how small?}.
-These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings.
+These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings~\cite{cms_stopped}.
 
@@
         LLPs that decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}\fxnote{Is it still a DV if it decays in active material somewhere?}.
-ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity.\fxnote{make sure I can explain why met and multiplicity} The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range\fxnote{Am I defining sensitivity range consistently across analyses?}.
+ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity~\cite{atlas_displaced}.\fxnote{make sure I can explain why met and multiplicity} The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range\fxnote{Am I defining sensitivity range consistently across analyses?}.
 
@@
 
+        \fxnote{Add particle labels} 
         \noindent \begin{figure}[htbp] \begin{center}
@@
         };
-        \caption{Process.}
+        \caption{Long-lived gluino decay through highly virtual squark. Diagram created with~\cite{tikz}}
         \label{displaced_process}
@@
         \includegraphics[width=0.6\textwidth]{images/material_map}
-        \caption{Map of material dense regions of the ATLAS detector.\fxnote{cite analysis}}
+            \caption{Map of material dense regions of the ATLAS detector.\fxnote{explain more}~\cite{atals_displaced}}
         \label{material_map}
@@
         \end{center} \end{subfigure}
-        \caption{Limit.}
+        \caption{Limit\fxnote{explain}.~\cite{atlas_displaced}}
         \label{displaced_limit}
@@
         %};
-        \caption{Processes.}
+            \caption{Processes\fxnote{explain}.~\cite{atlas_disappearing}}
         \label{disappearing_processes}
@@
         \end{center} \end{subfigure}
-        \caption{Limits.}
+            \caption{Limits\fxnote{explain}.~\cite{atlas_disappearing}}
         \label{disappearing_limits}
@@
     \fxnote{cite cornering} 
+    \fxnote{define \mu, Q?} 
     \fxnote{make sure these are logically and notationally consistent w/ earlier higgs corrections} 
@@
     Natural SUSY scenarios, then, are most likely to be constrained by limits on the stop, gluino, and Higgsino masses.
-The Higgsino, however, does not carry color charge and is far less likely\fxnote{be able to quantify} to be produced at the LHC, leaving stop and gluino mass limits as the most important contraints on natural SUSY models.
+The Higgsino, however, does not carry color charge and is far less likely\fxnote{be able to quantify} to be produced at the LHC, leaving stop and gluino mass limits as the most important general contraints on natural SUSY models.
 As shown in Eqs.~\ref{stop_correction} and~\ref{gluino_correction}, the size of stop and gluino corrections also depends on $\Lambda$, the messenger scale of SUSY breaking.\fxnote{Make sure I understand this.
-Messenger scale != breaking scale?}\fxnote{Either explain more thoroughly or drop completely.
+Messenger scale != breaking scale?
 What are the consequences of a lower messenger scale?}
@@
     Two qualitative decisions must be made when analyzing the state of naturalness: (1) How best to define the degree of fine tuning in a particular model and (2) what degree of fine tuning is acceptable?
-A common, but not universal, definition for (1) is
+A common, but not universal, way to quantify fine tuning is
 
@@
 
-    \noindent where $\alpha_i$ is a particular parameter and $\Delta_i$ is the degree of fine tuning from variations in that parameter.
+    \noindent where $\alpha_i$ is a particular model parameter and $\Delta_i$ is the degree of fine tuning from variations in that parameter.
 The overall degree of fine tuning for the model can then be assigned as $\max{\left(\Delta_i\right)}$.
+
     Determining the acceptable degree of fine tuning is even more open ended.
@@
 As models are constrained, physicists seem willing to accept greater degrees of fine tuning.
-Instead of asking, ``what degree of fine tuning should be considered natural?", Feng\fxnote{cite} proposes physicists ask themselves, ``If SUSY were discovered with such-and-such degree of fine tuning, would I consider the naturalness problem solved and move on to different research questions?" Anecdotally, Feng reports that acceptable levels of fine tuning tend to increase when the question is posed in this way.\fxnote{break into two paragraphs?}
+Instead of asking, ``what degree of fine tuning should be considered natural?", Feng proposes physicists ask themselves, ``If SUSY were discovered with such-and-such degree of fine tuning, would I consider the naturalness problem solved and move on to different research questions?" Anecdotally, Feng reports that acceptable levels of fine tuning tend to increase when the question is posed in this way~\cite{feng}.
 
     So, how is natural SUSY fairing?
-Fig.~\ref{atlas_susy_searches} summarizes limits on many SUSY models and topologies from ATLAS searches.
+Fig.~\ref{atlas_susy_summary} summarizes limits on many SUSY models and topologies from ATLAS searches.
 CMS limits are generally similar\fxnote{make sure this is true}, but a recent plot was not available.\fxnote{give general summary}
@@
 
-    It's often helpful to look at limits in the context of simplified models.
-Fig.~\ref{cornering_limits} does just this for the cases of Effective SUSY, RPV SUSY, Hidden Valley SUSY, and a model that combines RPV with Effective SUSY.
+    Each of the limits in Fig.~\ref{atlas_susy_summary} comes with a particular set of assumptions, making it difficult to draw general conclusions.
+Some authors try to solve this problem by recasting analyses in terms of a few general models that illustrate much of the natural SUSY landscape.
+Fig.~\ref{cornering_limits} does just this with several searches using $\approx \SI{15}{\femto\barn^{-1}}$ of \SI{13}{\tera\electronvolt} data for the cases of Effective SUSY, RPV SUSY, Hidden Valley SUSY, and a model that combines RPV with Effective SUSY.
+The authors find that for $\mu \leq \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space remains viable in all cases.\fxnote{mention that HL-LHC should rule everything out?}
 
-    \fxnote{How do LLPs open doors to naturalness and which of those doors have we already closed?} 
-    Opening to the possibility of long-lived sparticles increases the parameter space in which natural SUSY could be hiding. LLP analyses such as the ones described in \fxnote{Section whatever}
+        \noindent \begin{figure}[htbp] \begin{center}
+        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/cornering_effective_100}
+        \end{center} \end{subfigure}
+        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/cornering_rpv_100}
+        \end{center} \end{subfigure}
+        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/cornering_hv_100}
+        \end{center} \end{subfigure}
+        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \includegraphics[width=\textwidth]{images/cornering_rpv_effective_100}
+        \end{center} \end{subfigure}
+        \caption{Limits.\fxnote{cite cornering}}
+        \label{cornering_limits}
+        \end{center} \end{figure}
 
-    Despite strong contraints, SUSY remains one of the least-tuned options for BSM naturalness\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.
+    As viable parameter space for natural SUSY continues to shrink, it is important to identify and fill in the gaps left by conventional analyses.
+LLP searches such as those in Sec.~\ref{analyses} do just that by opening up sensitivity to lifetimes that would otherwise be missed.
+Fig.~\ref{fate_limits} shows stop mass limits from several Run I LLP searches that have been recast using a simple RPV model\fxnote{cite fate}.
+By combining results from several analyses, the authors constrain the stop mass for a broad and continuous range of lifetimes.
+LLP searches are slowly excluding the natural parameter space
 
-\section{Conclusion and Important Searches for 2017}
+    Despite increasing contraints, SUSY remains one of the least-tuned options for natural BSM physics\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.\fxnote{Add exotica summary plot to show how constrained everything else is?}
 
 \fxnote{When should symbols be italicized and when should they be mathrm'd?} 
+\fxnote{fine-tuning or fine tuning?}
 

### 2017-08-02 tex/draft.tex
full draft of viability

@@
 \pagenumbering{arabic}
+
+% Things to check
+\fxnote{When should symbols be italicized and when should they be mathrm'd?} 
+\fxnote{fine-tuning or fine tuning?}
 
@@
         \noindent \begin{figure}[htbp] \begin{center}
-            \includegraphics[width=0.5\textwidth]{images/pixel_old_new}
+            \includegraphics[width=0.4\textwidth]{images/pixel_old_new}
             \caption{Diagram showing barrel pixel layers before and after the winter 2016/17 upgrade.\fxnote{cite website found through Andrew's citations}}
@@
         \includegraphics[width=0.6\textwidth]{images/material_map}
-            \caption{Map of material dense regions of the ATLAS detector.\fxnote{explain more}~\cite{atals_displaced}}
+            \caption{Map of material dense regions of the ATLAS detector.\fxnote{explain more}~\cite{atlas_displaced}}
         \label{material_map}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.2\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/disappearing_ew_process}
@@
         \qquad
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.2\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/disappearing_qcd_process}
@@
         \fxnote{Add calorimeter search?}  
-        \fxnote{cite CMS PAS EXO-17-004}
-        \fxnote{mention how stopped particles complement HSCP search?}
         \fxnote{too redundant with overview?}
@@
 The eventual decay would then lead to energy deposits in the calorimeters or hits in the muon system that could be out of time with proton bunch crossings.
-A recent CMS analysis looked for such a signal in dimuon final states using the full 2015 and 2016 datasets.
+A recent CMS analysis looked for such a signal in dimuon final states using the full 2015 and 2016 datasets~\cite{cms_stopped}.
 
@@
         \includegraphics[width=\textwidth]{images/stopped_reject_cosmic_tof}
-        \caption{Cosmic muon rejection with MS.\fxnote{cite analysis}}
+            \caption{Cosmic muon rejection using time-of-flight information from the muon system.~\cite{cms_stopped}}
         \label{stopped_muon_differentiation}
@@
         \end{center} \end{subfigure}
-        \caption{Limits.\fxnote{cite analysis}}
+            \caption{Upper limits on production cross section as a function of gluino lifetime (left) and mass (right)~\cite{cms_stopped}}
         \label{stopped_limits}
@@
     \subsection{Heavy Stable Charged Particles}
-        \fxnote{cite CMS EXO-15-010}
         \fxnote{nice dE/dx plot (fig 1)}
-        Particles that live for more than a couple ns\fxnote{how do I typeset standalone units?} \fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
+        Particles that live for more than a couple \SI{}{ns}\fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
 If such a particle is also sufficiently massive, it can be catigorized as a heavy stable charged particle (HSCP).
@@
 Probably better explained here than there}.
-Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss, as shown in Fig.~\ref{hscp_dedx}.
+Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss, as shown in Fig.~\ref{hscp_dedx}~\cite{cms_hscp}.
 
@@
         \includegraphics[width=0.5\textwidth]{images/hscp_dedx}
-            \caption{Ionization energy loss.\fxnote{cite analysis}}
+            \caption{Ionization energy loss as a function of momentum for paticles of varying mass and charge~\cite{cms_hscp}}
         \label{hscp_dedx}
@@
         \end{center} \end{subfigure}
-        \caption{Limits.\fxnote{cite analysis}}
+        \caption{Production cross section limits on several particles as a function of mass for the tracker-only and tracker+TOF analyses~\cite{cms_hscp}}
         \label{hscp_limits}
@@
 \section{Experimental Viability of Natural SUSY}
-    \fxnote{Andrew says: This should really be your most important section.
-You should try to bring together the results of the searches you talked about (and of other long-lived particle searches and even of more general SUSY searches) and explain what they mean for a possible natural explanation of EWSB.
-At what point can we claim that there is no natural solution, or at least that there is no natural solution in terms of SUSY?
-Essentially, nobody cares about what you talked about in Section 6; what's important is that you can give these results a meaningful context in the bigger picture of a natural explanation of EWSB.}
-
     Interpreting current limits in the context of naturalness requires some set of criteria that determine if a model is natural.
-No well-defined, universally-agreed-upon criteria exist, but certain themes recur in many discussions of natural model building\fxnote{better be able to confidently cite several sources}.
+No well-defined, universally-agreed-upon criteria exist, but certain themes recur in many discussions of natural model building~\cite{craig, vestiges, evans_toward_full, feng, cornering, kim}.
 The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits\fxnote{Did I just steal Chris's langauge?}.
 
-    When building a natural SUSY model, certain constraints are nearly unavoidable\fxnote{Dangerous.
-What if Linda knows how to avoid them?}.
-Specifically, the Higgsino\fxnote{careful, there could be multiple Higgsinos.
-Do I mean 'lightest Higgsino'?}, which corrects $m_H$ at tree level; the stop\fxnote{mention that stop is more important than other sfermions b/c large yukawa coupling?
-I'll have to clarify that somewhere}, which corrects $m_H$ at one loop; and the gluino, which corrects mStop at one loop and therefore $m_H$ at two, must all be light enough to avoid excessive fine tuning.\fxnote{Need diagrams and correction terms for sure} Furthermore, the stop and gluino masses are correlated --- a large difference between the two would itself be unnatural.
+    \fxnote{I should be able to combine or reorganize the next two paragraphs to flow better} 
+    The parameters of interest are the Higgsino\fxnote{careful - do I mean lightest higgsino?}, stop, and gluino masses, which correct the Higgs mass at tree-level, one-loop, and two-loops, respectively (see Eqs.~\ref{higgsino_correction}-~\ref{gluino_correction}).
+Furthermore, the stop and gluino masses are correlated --- a large difference between the two would itself be unnatural~\cite{cornering}.
 
-    \fxnote{cite cornering} 
     \fxnote{define \mu, Q?} 
@@
 
-    \fxnote{cite cornering} 
     \noindent \begin{equation}
@@
 
-    \noindent where $\alpha_i$ is a particular model parameter and $\Delta_i$ is the degree of fine tuning from variations in that parameter.
-The overall degree of fine tuning for the model can then be assigned as $\max{\left(\Delta_i\right)}$.
+    \noindent where $\alpha_i$ is a particular model parameter and $\Delta_i$ is the degree of fine tuning assoicated with that parameter.
+The overall degree of fine tuning for the model can then be assigned as $\max{\left(\Delta_i\right)}$~\cite{cornering}.
 
     Determining the acceptable degree of fine tuning is even more open ended.
-Before null results and serious constraints started rolling in, it was common\fxnote{cite something} to refer to the $\Delta \lesssim 10$ regions of parameter space as natural.
-As models are constrained, physicists seem willing to accept greater degrees of fine tuning.
-Instead of asking, ``what degree of fine tuning should be considered natural?", Feng proposes physicists ask themselves, ``If SUSY were discovered with such-and-such degree of fine tuning, would I consider the naturalness problem solved and move on to different research questions?" Anecdotally, Feng reports that acceptable levels of fine tuning tend to increase when the question is posed in this way~\cite{feng}.
+Before null results and serious constraints started rolling in, it was common\fxnote{feng} to refer to the $\Delta \lesssim 10$ regions of parameter space as natural, but as models are constrained, physicists seem willing to accept greater degrees of fine tuning.
+Feng proposes an interesting way to recast this problem: instead of asking which regions of parameter space are most natural, physicists should instead ask themselves, ``If superpartners were discovered, what level of fine fine-tuning would be sufficient to convince me that the gauge hierarchy problem is solved by sypersymmetry and I should move on to researhing other problems?"\fxnote{paraphrase for brevity?} Anecdotally, acceptable levels of fine tuning tend to increase when the question is posed in this way~\cite{feng}.
 
-    So, how is natural SUSY fairing?
-Fig.~\ref{atlas_susy_summary} summarizes limits on many SUSY models and topologies from ATLAS searches.
-CMS limits are generally similar\fxnote{make sure this is true}, but a recent plot was not available.\fxnote{give general summary}
+    Exact upper limits on natural sparticle masses are therefore hard to come by.
+A reasonable and somewhat typical set of values is given in~\cite{drees_kim}: $m_{\tilde{H}} \lesssim \SI{500}{\giga\electronvolt}$, $m_{\tilde{t}} \lesssim \SI{1.5}{\tera\electronvolt}$, and $m_{\tilde{g}} \lesssim \SI{3}{\tera\electronvolt}$.
+Fig.~\ref{atlas_susy_summary} summarizes current SUSY limits from ATLAS searches (CMS limits are generally similar, but a recent plot was not available).
+Upon inspection, one sees that experimental limits are starting to push on naturalness bounds in many scenarios.
 
+    \fxnote{what do I cite?}  
     \noindent \begin{figure}[htbp] \begin{center}
     \includegraphics[width=0.8\textwidth]{images/atlas_susy_summary}
-    \caption{Summary of current experimental limits on SUSY models from ATLAS searches.\fxnote{cite something}}
+    \caption{Summary of current experimental limits on SUSY models from ATLAS searches.}
     \label{atlas_susy_summary}
@@
 Some authors try to solve this problem by recasting analyses in terms of a few general models that illustrate much of the natural SUSY landscape.
-Fig.~\ref{cornering_limits} does just this with several searches using $\approx \SI{15}{\femto\barn^{-1}}$ of \SI{13}{\tera\electronvolt} data for the cases of Effective SUSY, RPV SUSY, Hidden Valley SUSY, and a model that combines RPV with Effective SUSY.
-The authors find that for $\mu \leq \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space remains viable in all cases.\fxnote{mention that HL-LHC should rule everything out?}
+Fig.~\ref{cornering_limits} shows the results from one such attempt using $\approx \SI{15}{\femto\barn^{-1}}$ of \SI{13}{\tera\electronvolt} data for the cases of Effective SUSY, RPV SUSY, Hidden Valley SUSY, and a model that combines RPV with Effective SUSY.
+The authors find that for $\mu \leq \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space remains viable in all cases but project that all considered $\Delta < 10$ parameter space will be excluded within the next few years\fxnote{check}.
 
         \noindent \begin{figure}[htbp] \begin{center}
-        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/cornering_effective_100}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/cornering_rpv_100}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/cornering_hv_100}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/cornering_rpv_effective_100}
         \end{center} \end{subfigure}
-        \caption{Limits.\fxnote{cite cornering}}
+        \caption{Limits.~\cite{cornering}}
         \label{cornering_limits}
@@
 LLP searches such as those in Sec.~\ref{analyses} do just that by opening up sensitivity to lifetimes that would otherwise be missed.
-Fig.~\ref{fate_limits} shows stop mass limits from several Run I LLP searches that have been recast using a simple RPV model\fxnote{cite fate}.
-By combining results from several analyses, the authors constrain the stop mass for a broad and continuous range of lifetimes.
-LLP searches are slowly excluding the natural parameter space
+Fig.~\ref{fate_limits}, for example, shows stop mass limits from several Run I LLP searches that have been recast using a simple RPV model~\cite{fate}.
+By combining results from several analyses, the authors constrain the stop mass for a broad and continuous range of lifetimes that would have been invisible to conventional searches.
 
-    Despite increasing contraints, SUSY remains one of the least-tuned options for natural BSM physics\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.\fxnote{Add exotica summary plot to show how constrained everything else is?}
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=\textwidth]{images/fate_limits}
+        \caption{Limits.~\cite{fate}}
+        \label{fate_limits}
+        \end{center} \end{figure}
 
-\fxnote{When should symbols be italicized and when should they be mathrm'd?} 
-\fxnote{fine-tuning or fine tuning?}
+    CMS and ATLAS should be able to exclude or discover a wide range of natural SUSY models over the next several years~\cite{cornering}.
+In the absence of a discovery, physicists will have to look long and hard at the role of naturalness in the SM.
+In the meantime, however, SUSY remains one of the least-tuned options for natural BSM physics\fxnote{double check, then cite cornering, feng, nate, and/or giudice}\fxnote{Should I include exo summary plot to show how constrained compositeness and extra dimensions are?}.
+In the final years of the hunt for natrual SUSY, CMS and ATLAS will need to apply a combination of conventional and LLP searches in order to cover natural parameter space.
+\fxnote{need to answer, "which searches are important?}
 

### 2017-08-03 tex/draft.tex
First real full draft

@@
 Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid.
-The fermions and gauge bosons, on the other hand, only depend logarithmically\fxnote{check.
-be able to work out example} on $\Lambda$~\cite{dine_naturalness}.
+The fermions and gauge bosons, on the other hand, only depend logarithmically\fxnote{be able to work out example} on $\Lambda$~\cite{dine_naturalness}.
 The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the bare Higgs mass and the terms that correct it.
@@
 While it's possible that the bare mass and corrections just so happen to almost perfectly cancel, such miraculous fine tuning could also be a hint that some deeper physical mechanism is at work.
-That is, either some previously unknown symmetry is protecting the Higgs mass or the cutoff scale is $\mathcal{O}\left(\SI{}{\tera\electronvolt}\right)$\fxnote{explain better and cite something}.
 
@@
 Specifically, we are interested in SUSY models that predict new long-lived particles (LLPs), which are defined as particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
-This category includes everything from particles that decay at 100um to particles that propagate through the entire detector\fxnote{I made up 100um.
-Find real number and cite source}.
+This category includes everything from particles that decay before reaching the inner tracker to particles that propagate through the entire detector.
 
-    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay\fxnote{find source to cite}.
+    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
 In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the the lightest particles carrying their respective conserved quantities.
 Neutrons and muons, whose decays are shown in Fig.\ref{sm_llp_processes}, are long-lived for reasons (2), (3), and (4).
-Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay\fxnote{find something to cite}.
+Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay.
 \fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}
@@
 
-    On the other hand, models with weakly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs\fxnote{find something to cite}.
+    On the other hand, models with weakly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs~\cite{fate}.
 A similar situation arises in GMSB models\fxnote{should I describe GMSB?} where the gravitino is the LSP.
@@
         \fxnote{Mention that ATLAS is similar, says Andrew}  
-        \fxnote{Maybe mention PDFs. Definitely know about them, says Andrew}  
-        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), which is a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 to the present\fxnote{say better}\fxnote{cite something?}.
+        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), which is a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 to the present\fxnote{say better}.
 To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{4}{\tesla} superconducting solenoid.
@@
         \includegraphics[width=0.7\textwidth]{images/cms}
-            \caption{The CMS detector\fxnote{Cite that website from Andrew's paper}}
+        \caption{The CMS detector~\cite{cms_image}}
         \label{cms}
@@
     \subsection{Tracker}
-        \fxnote{cite CMS TDR, jinst 12 c02033}
         \fxnote{mention that analyses below used pre-upgrade tracker}
@@
             \includegraphics[width=0.4\textwidth]{images/pixel_old_new}
-            \caption{Diagram showing barrel pixel layers before and after the winter 2016/17 upgrade.\fxnote{cite website found through Andrew's citations}}
+            \caption{Diagram showing barrel pixel layers before and after the winter 2016/17 upgrade.~\cite{pixel_old_new}}
             \label{pixel_old_new}
@@
     \subsection{Electromagnetic Calorimeter}
-        \fxnote{cite CMS TDR}
         \fxnote{I define EE \& EB but never use those definitions}
@@
     \subsection{Hadronic Calorimeter}
-        \fxnote{cite CMS TDR}
         \fxnote{define HB \& HF never to be used}
@@
     \subsection{Solenoid}
-        \fxnote{cite cms experiment at the cern lhc}
         CMS employs a \SI{4}{T} superconducting solenoid to aid in the measurement of charged particle momenta.
@@
     \subsection{Muon System}
-        \fxnote{cite CMS TDR}
         \fxnote{Specifically mention CMS design specs to meet physics goals?}
@@
     \subsection{Trigger}
-        \fxnote{cite CMS TDR, jinst 12 c03021}
         \fxnote{Is entire detector read out at L1?}
@@
         LLPs leave distinct signatures that differentiate them from SM backgrounds but also add complexity to LLP analyses.
-CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays\fxnote{find something to cite}, so LLP searches are often forced\fxnote{the searchers are forced, not the searches} to stray from the traditional analysis path in terms of object reconstruction\fxnote{really reconstruction?
-Maybe object definition?} and background estimation.
+CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays, so LLP searches are often forced\fxnote{the searchers are forced, not the searches} to stray from the traditional analysis path in terms of object reconstruction and background estimation.
 This report focuses on four complementary LLP signatures: displaced vertices, disappearing tracks, low-velocity particles, and particles that come to a stop before decaying.
@@
     \subsection{Displaced Vertices}
-        \fxnote{cite CONF-2017-026}
         LLPs that decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}\fxnote{Is it still a DV if it decays in active material somewhere?}.
@@
 The relevant process, shown in Fig.~\ref{displaced_process}, is pair-produced gluinos that decay to a quark-\fxnote{how to punctuate?}virtual squark pair.
-The virtual squark then decays to a quark and the LSP, presumed to be a neutralino\fxnote{have I defined neutralino?}\fxnote{why is this a reasonable assumption?} \fxnote{steal diagram from andrew's preapproval.
-I can't access it - ask andrew}.
+The virtual squark then decays to a quark and the LSP, presumed to be a neutralino\fxnote{have I defined neutralino?}\fxnote{why is this a reasonable assumption?}.
 The large mass of the intermediate squark suppresses the gluino decay, giving the gluino enough time to form an R-hadron\fxnote{first use.
@@
         \end{center} \end{subfigure}
-        \caption{Limit\fxnote{explain}.~\cite{atlas_displaced}}
+            \caption{Limits on the gluino pair-production cross section (left) and gluino mass as a function of lifetime (right)~\cite{atlas_displaced}.}
         \label{displaced_limit}
@@
     \subsection{Disappearing Tracks}
-        \fxnote{cite CONF-2017-017}
         Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
@@
         %};
-            \caption{Processes\fxnote{explain}.~\cite{atlas_disappearing}}
+            \caption{Benchmark signal processes: electroweak gaugino production (left) and gluino pair-production (right)~\cite{atlas_disappearing}.}
         \label{disappearing_processes}
@@
 
-        No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass-gluon mass plane for the QCD production process \fxnote{hopefully will be way clearer after texing in sparticle symbols}.
+        No excess over expected background is observed, so upper limits are placed in the NLSP chargino mass-lifetime plane for the EW signal process and in the NLSP chargino mass-gluon mass plane for the QCD production process.
 Fig.~\ref{disappearing_limits} shows the limits for both processes.
@@
         \end{center} \end{subfigure}
-            \caption{Limits\fxnote{explain}.~\cite{atlas_disappearing}}
+            \caption{Limits on chargino mass and lifetime in the electroweak production channel (left) and gluino and chargino masses in the gluon pair-production channel with a \SI{0.2}{\nano\s} (center) and \SI{1.0}{\nano\s} chargino lifetime.~\cite{atlas_disappearing}}
         \label{disappearing_limits}
@@
     \subsection{Heavy Stable Charged Particles}
-        \fxnote{nice dE/dx plot (fig 1)}
         Particles that live for more than a couple \SI{}{ns}\fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.5\textwidth]{images/hscp_dedx}
+        \includegraphics[width=0.4\textwidth]{images/hscp_dedx}
             \caption{Ionization energy loss as a function of momentum for paticles of varying mass and charge~\cite{cms_hscp}}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/hscp_limit_tracker_only}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/hscp_limit_tracker_tof}
@@
 
-    Determining the acceptable degree of fine tuning is even more open ended.
-Before null results and serious constraints started rolling in, it was common\fxnote{feng} to refer to the $\Delta \lesssim 10$ regions of parameter space as natural, but as models are constrained, physicists seem willing to accept greater degrees of fine tuning.
-Feng proposes an interesting way to recast this problem: instead of asking which regions of parameter space are most natural, physicists should instead ask themselves, ``If superpartners were discovered, what level of fine fine-tuning would be sufficient to convince me that the gauge hierarchy problem is solved by sypersymmetry and I should move on to researhing other problems?"\fxnote{paraphrase for brevity?} Anecdotally, acceptable levels of fine tuning tend to increase when the question is posed in this way~\cite{feng}.
+    Determining the acceptable degree of fine tuning is even more subjective.
+Before null results and serious constraints started rolling in, it was common to refer to the $\Delta \lesssim 10$ regions of parameter space as natural, but as models are constrained, physicists seem willing to accept greater degrees of fine tuning.
+Feng proposes an interesting way to recast this problem: instead of asking which regions of parameter space are most natural, physicists should instead ask themselves, ``If superpartners were discovered, what level of fine fine-tuning would be sufficient to convince me that the gauge hierarchy problem is solved by sypersymmetry and I should move on to researching other problems?"\fxnote{paraphrase for brevity?} Anecdotally, fine tuning thresholds tend to increase when the question is posed in this way~\cite{feng}.
 
     Exact upper limits on natural sparticle masses are therefore hard to come by.
-A reasonable and somewhat typical set of values is given in~\cite{drees_kim}: $m_{\tilde{H}} \lesssim \SI{500}{\giga\electronvolt}$, $m_{\tilde{t}} \lesssim \SI{1.5}{\tera\electronvolt}$, and $m_{\tilde{g}} \lesssim \SI{3}{\tera\electronvolt}$.
-Fig.~\ref{atlas_susy_summary} summarizes current SUSY limits from ATLAS searches (CMS limits are generally similar, but a recent plot was not available).
+A somewhat typical set of values is given in~\cite{drees_kim}: $m_{\tilde{H}} \lesssim \SI{500}{\giga\electronvolt}$, $m_{\tilde{t}} \lesssim \SI{1.5}{\tera\electronvolt}$, and $m_{\tilde{g}} \lesssim \SI{3}{\tera\electronvolt}$.
+Fig.~\ref{atlas_susy_summary} summarizes current SUSY limits from ATLAS searches (CMS limits are generally similar, but a recent plot is not available).
 Upon inspection, one sees that experimental limits are starting to push on naturalness bounds in many scenarios.
@@
     \noindent \begin{figure}[htbp] \begin{center}
-    \includegraphics[width=0.8\textwidth]{images/atlas_susy_summary}
+    \includegraphics[width=0.7\textwidth]{images/atlas_susy_summary}
     \caption{Summary of current experimental limits on SUSY models from ATLAS searches.}
@@
     Each of the limits in Fig.~\ref{atlas_susy_summary} comes with a particular set of assumptions, making it difficult to draw general conclusions.
-Some authors try to solve this problem by recasting analyses in terms of a few general models that illustrate much of the natural SUSY landscape.
-Fig.~\ref{cornering_limits} shows the results from one such attempt using $\approx \SI{15}{\femto\barn^{-1}}$ of \SI{13}{\tera\electronvolt} data for the cases of Effective SUSY, RPV SUSY, Hidden Valley SUSY, and a model that combines RPV with Effective SUSY.
-The authors find that for $\mu \leq \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space remains viable in all cases but project that all considered $\Delta < 10$ parameter space will be excluded within the next few years\fxnote{check}.
+Some authors try to solve this problem by recasting analyses in terms of a few simplified models that illustrate much of the natural SUSY landscape.
+Fig.~\ref{cornering_limits} shows the results from one such attempt using $\approx \SI{15}{\femto\barn^{-1}}$ of \SI{13}{\tera\electronvolt} data for the cases of Effective SUSY, RPV SUSY, and a model that combines RPV with Effective SUSY.
+The authors find that for $\mu \leq \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space remains viable in all cases but also project that all considered $\Delta < 10$ parameter space can be excluded within the next few years\fxnote{check}.
 
@@
         \includegraphics[width=\textwidth]{images/cornering_rpv_100}
-        \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
-        \includegraphics[width=\textwidth]{images/cornering_hv_100}
         \end{center} \end{subfigure}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=\textwidth]{images/fate_limits}
+        \includegraphics[width=0.4\textwidth]{images/fate_limits}
         \caption{Limits.~\cite{fate}}
@@
 
-    CMS and ATLAS should be able to exclude or discover a wide range of natural SUSY models over the next several years~\cite{cornering}.
-In the absence of a discovery, physicists will have to look long and hard at the role of naturalness in the SM.
-In the meantime, however, SUSY remains one of the least-tuned options for natural BSM physics\fxnote{double check, then cite cornering, feng, nate, and/or giudice}\fxnote{Should I include exo summary plot to show how constrained compositeness and extra dimensions are?}.
-In the final years of the hunt for natrual SUSY, CMS and ATLAS will need to apply a combination of conventional and LLP searches in order to cover natural parameter space.
-\fxnote{need to answer, "which searches are important?}
+    Many LLP searches are motivated by and interpreted within specific models that predict unique signatures.
+Approaching analyses is this way often results in nearly background-free searches with good signal acceptance for the model in question, but it can be difficult to draw general conclusions or assess the complementarity (or redundancy) of different searches~\cite{fate}.
+As the number of LLP searches grows, it will be important to for researchers to design their searches around simplified models that encourage combining results to draw general conclusions~\cite{evans_talk}.
+
+    Combining results from several searches can also elucidate new directions for important searches.
+By recasting several LLP searches similar to those described in Sec.~\ref{analyses}, Evans and Shelter looked at the current viability of several SUSY spectra that predict long-lived staus.
+They identified significant gaps in coverage for models with displaced taus or same-sign displaced leptons, which appear in several well-motivated models such as GMSB, which frequently predicts NLSP staus that can become long-lived or certain RPV couplings that lead to same-flavor leptons~\cite{ll_staus}.
+
+    The uniqueness of LLP signatures and idosyncrasy of LLP analyses leads to a broad and diverse set of analyses that will surely grow as viable natural parameter space shrinks and more imaginations are turned to filling in the gaps.
+Fully covering natural SUSY parameter space will take a dedicated effort from the LLP community, both to maximize the reach of individual searches and to design complementary analyses that can be used to draw general conclusions.
+Although natural SUSY is under pressure from conventional and long-lived null results, it remains one of the least-tuned options for natural BSM physics\fxnote{double check, then cite cornering, feng, nate, and/or giudice}.
+The next several years will be decisive~\cite{cornering}, and physicists will have to be clever to probe every corner of natural parameter space.
 

### 2017-08-03 tex/draft.tex
First edited draft

@@
 \doublespacing
-%\linenumbers
+\linenumbers
 \pagenumbering{arabic}
@@
 The physical gauge bosons, which are linear combinations of the Ws and B, are the $\Wp$, $\Wm$, $\Z$, and photon ($\gamma$).
-The fermions are catagorized by which representation of each group they fit into\fxnote{make sure I'm good at explaining this}.
+The fermions are categorized by which representation of each group they fit into\fxnote{make sure I'm good at explaining this}.
 For example, $\SUthreec$ distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and $\SUtwoL$ distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
-Finally, weak hypercharge further distignuishes SM particles according to the Gell-Mann--Nishijima formula, $Y=Q-I_3$, where Q is electric charge and $I_3$ is the third component of weak isospin~\cite{sm_intro}.
+Finally, weak hypercharge further distinguishes SM particles according to the Gell-Mann--Nishijima formula, $Y=Q-I_3$, where $Q$ is electric charge and $I_3$ is the third component of weak isospin~\cite{sm_intro}.
 
@@
 Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}.
-These terms are interpreted as giving mass to the quarks and charged leptons mass, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$~\cite{sm_intro}.
+These terms are interpreted as giving mass to the quarks and charged leptons, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$~\cite{sm_intro}.
 
@@
     The naturalness criterion can be formulated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of the higher-energy theory, and (3) any dimensionless parameter much smaller than unity must be protected by a custodial symmetry~\cite{giudice_naturally, thooft_naturalness}.
-Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory.
-\fxnote{wordy and maybe repetative}.
+Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory\fxnote{wordy and maybe repetitive}.
 This discussion focuses on statement (3), which is in some ways a more nuanced version of (1) that also explains cases where dimensional analysis fails.
@@
     All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$~\cite{dine_naturalness}\fxnote{show diagrams and terms?}.
-Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}~\cite{cms_higgs, atlas_higgs}, a value that must be achieved by the sum of the bare mass and all corrections.
+Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}~\cite{cms_higgs, atlas_higgs}, a value that must be equal to the sum of the bare mass and all corrections.
 Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely.
 In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important~\cite{giudice_naturally}.
-While it's possible that the bare mass and corrections just so happen to almost perfectly cancel, such miraculous fine tuning could also be a hint that some deeper physical mechanism is at work.
+While it's possible that the bare mass and all corrections just so happen to cancel so perfectly, such miraculous fine tuning could also be a hint that a deeper physical mechanism is at work.
 
@@
 That is, if the fermions and gauge bosons were massless at tree level, the chiral and gauge symmetries would cause their masses to be uncorrected to all orders in perturbation theory.
-As massive particles, however, the chiral and gauge symmetries instead guarantee that any corrections to their tree-level masses are proportional to their tree-level masses, preventing any large fine tuning between correction terms~\cite{giudice_naturally}.\fxnote{wordy as hell}
+As massive particles, however, the chiral and gauge symmetries instead guarantee that any corrections to their tree-level masses are proportional to their tree-level masses, preventing any large fine tuning between correction terms~\cite{giudice_naturally}.\fxnote{confusing paragraph.
+Rewrite and add math}
 
@@
 Arguments against naturalness often involve the anthropic principle, which posits that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
-Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck mass itself.
+Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck mass.
 Finally, the dominant\fxnote{what do I mean by dominant?} BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below~\cite{dine_naturalness}.
@@
 
-    Exact SUSY also requires that sparticles have the same mass as their SM counterparts, so the lack of sparticles in collider searches implies that SUSY must be broken.
-With broken SUSY, the same diagram as above produces a correction of the form~\cite{feng}
+    Exact SUSY also requires that sparticles have the same mass as their SM counterparts, so the uniformly null results in collider searches imply SUSY must be broken.
+With broken SUSY, the sum of diagrams in Fig.~\ref{exact_susy_correction} produces a correction of the form~\cite{feng}
 
@@
 
-    The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenemena.
-A handful of models with particular approaches to SUSY breaking that are particularly prominant or particularly relevant to naturalness or long-lived particles are gauge-mediated susy breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating SUSY (RPV).
+    The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenomena.
+A handful of models with particular approaches to SUSY breaking that are particularly prominent or particularly relevant to naturalness or long-lived particles are gauge-mediated SUSY breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating (RPV) SUSY.
 The details of these models will be explored as needed throughout this paper.
@@
 \section{Long-Lived Particles}
-    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and \fxnote{and/or?} produce a signal that could be missed by common SUSY search techniques.
+    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and \fxnote{and/or?} produce a signal that would be missed by common SUSY search techniques.
 Specifically, we are interested in SUSY models that predict new long-lived particles (LLPs), which are defined as particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
@@
     In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
-In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the the lightest particles carrying their respective conserved quantities.
+In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the lightest particles carrying their respective conserved quantities.
 Neutrons and muons, whose decays are shown in Fig.\ref{sm_llp_processes}, are long-lived for reasons (2), (3), and (4).
@@
     In SUSY models, LLPs arise for the same basic reasons, and different SUSY models produce LLPs in different ways.
-The most straightforward SUSY LLP occurs in models with conserved R-partity, a proposed symmetry that prevents proton decay\fxnote{Be prepared to show this.
+The most straightforward SUSY LLP occurs in models with conserved R-parity, a proposed symmetry that prevents proton decay~\cite{primer}\fxnote{Be prepared to show this.
 Maybe add some diagrams illustrating proton decay w/o R-parity}.
 In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1.
-Conserving the product of R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
+Conserving the product of R-parity at each vertex has two immediate phenomenological consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
 A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches~\cite{primer}.
@@
 A similar situation arises in GMSB models\fxnote{should I describe GMSB?} where the gravitino is the LSP.
-The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which supresses the NSLP decay rate and can lead to LLPs~\cite{dimopoulos_low_energy}.
+The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which suppresses the NSLP decay rate and can lead to LLPs~\cite{dimopoulos_low_energy}.
 
@@
         \fxnote{Mention that ATLAS is similar, says Andrew}  
-        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), which is a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 to the present\fxnote{say better}.
+        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}.
 To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{4}{\tesla} superconducting solenoid.
-All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}.
-The subdetectors that make up CMS are shown in Fig.~\ref{cms} and described below~\cite{cms_experiment}.
+All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}~\cite{cms_experiment}.
+The subdetectors that make up CMS are shown in Fig.~\ref{cms} and described below.
 
@@
 Inside \SI{20}{cm}, the pixel tracker  uses smaller\fxnote{than what?} silicon pixels to keep the occupancy near \SI{0.1}{\percent} despite the high\fxnote{specify} particle flux.
-Outside \SI{20}{\cm}, the silicon strip tracker (SST) achieves similar occupancy with larger silicon strips~\cite{cms_tdr}.\fxnote{check occupacy numbers}
+Outside \SI{20}{\cm}, the silicon strip tracker (SST) achieves similar occupancy with larger silicon strips~\cite{cms_tdr}.\fxnote{check occupancy numbers}
 
@@
         Just outside the pixel tracker, the silicon strip tracker (SST) occupies the $\num{20} < r < \SI{116}{cm}$ and $\lvert z \rvert < \SI{282}{cm}$ region of CMS.
-Composed of \num{9.3} million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly \SI{196}{m^2}.
+Composed of \num{9.3} million silicon strips that vary in size \fxnote{look up and specify} depending on particle flux in the region, the SST covers an active area of roughly \SI{196}{m^2}.
 At each trigger, the strip output voltage is read out via optical link~\cite{cms_pixel_upgrade}.
@@
         After traversing the inner tracker, particles next encounter the electromagnetic calorimeter (ECAL).
-As a homogeneous scintillation calorimeter, ECAL uses \num{61200} lead tunstate crystals in the barrel and \num{7324} in each endcap to reconstruct the energy deposited during electromagnetic showers.
-Lead tungstate crystals allow for a fast (\SI{80}{\percent} of light within \SI{25}{ns}), compact (radiation length = \SI{0.89}{cm}), fine-grained (Moli\`ere radius = \SI{2.2}{cm}), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
-The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necesitates photodetectors with intrinsic gain that work in magnetic fields\cite{cms_experiment, cms_tdr}.
+As a homogeneous scintillation calorimeter, ECAL uses \num{61200} lead tungstate crystals in the barrel and \num{7324} in each endcap to reconstruct the energy deposited during electromagnetic showers.
+Lead tungstate crystals allow for a fast (\SI{80}{\percent} of light within \SI{25}{\nano\s}), compact (radiation length = \SI{0.89}{cm}), fine-grained (Moli\`ere radius = \SI{2.2}{cm}), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
+The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necessitates photodetectors with intrinsic gain that work in magnetic fields\cite{cms_experiment, cms_tdr}.
 
@@
 
-        The barrel section (HB) spans a pseudorapidty range of \num{-1.4} to \num{1.4} and has \num{2304} towers \fxnote{check}, each of which contains \num{14} \fxnote{check} brass plates and covers an area of \num{0.087} x \SI{0.087}{in} $\eta-\phi$ \fxnote{get a feel for this area}.
-In addition, an extra layer (or two at $\eta = \num{0}$)of scintillator tiles sits just outside the solenoid.
-This extra layer, known as hadron outer (HO), spans a pseudorapidty range of \num{-1.26} to \num{1.26} and increases the minimum effective HCAL interaction length to greater than \num{11.8}.
+        The barrel section (HB) spans a pseudorapidity range of \num{-1.4} to \num{1.4} and has \num{2304} towers \fxnote{check}, each of which contains \num{14} \fxnote{check} brass plates and covers an area of \num{0.087} x \SI{0.087}{in} $\eta-\phi$ \fxnote{get a feel for this area}.
+In addition, an extra layer (or two at $\eta = \num{0}$) of scintillator tiles sits just outside the solenoid.
+This extra layer, known as hadron outer (HO), spans a pseudorapidity range of \num{-1.26} to \num{1.26} and increases the minimum effective HCAL interaction length to greater than \num{11.8}.
 
         Each endcap spans a pseudorapidity range of \num{1.3} to \num{3.0} with \num{14} towers in eta and \num{5} to \SI{10}{\degree} $\phi$ segmentation.
-Also, a steel and quartz fiber forward calorimeter (HF) sits \SI{11.2}{m} from the interaction pipe in a pseudorapidty range of \num{3.0} to \num{5.0}.
+Also, a steel and quartz fiber forward calorimeter (HF) sits \SI{11.2}{m} from the interaction pipe in a pseudorapidity range of \num{3.0} to \num{5.0}.
 In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline.
@@
 The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
-Combining MS and tracker measurements improves the muon pT\fxnote{define} resolution at high momenta where the tracker $\pT$ resolution declines \fxnote{quantify or show std plot?}\cite{cms_experiment, cms_tdr}.
+Combining MS and tracker measurements improves the muon momentum resolution at high momenta where the tracker resolution declines \fxnote{quantify or show std plot?}\cite{cms_experiment, cms_tdr}.
 
-        In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at \num{4.0}, \num{4.9}, \num{5.9}, and \SI{7.9}{m}.
+        In the barrel detector (BD), four layers of DTs and RPCs are embedded in the solenoid return yoke at \num{4.0}, \num{4.9}, \num{5.9}, and \SI{7.9}{m}.
 The maximum drift length is \SI{2}{\cm} and the single point resolution is \SI{200}{\cm}.
@@
 
-        Each muon endcap detector (ME) is composed of \num{234} CSCs and four RPC stations \fxnote{figure out exactly what RPC station means and say that instead}.
-Each CSC has six gas gaps with radial cathode strips and nearly perpendicualar planes of anode wires.
-The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements.
+        Each muon endcap detector (ME) is composed of four layers of CSCs and three layers of RPCs.
+Each CSC has six gas gaps with radial cathode strips and nearly perpendicular planes of anode wires.
+The wire signal from the ionization-induced electron avalanche is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements.
 All in all, the CSC spacial resolution is approximately \SI{200}{\micro\m} and the angular resolution is approximately \SI{10}{\milli\radian}.
@@
 The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT).
-L1 uses input from ECAL, HCAL, and MS that represents physics objects ($\mathrm{e}$/$\gamma$, $\tau$, jets, $\mu$, and $\MET$) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
+L1 analyzes input from ECAL, HCAL, and MS with custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
 The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz\cite{cms_experiment, cms_trigger_upgrade}.
@@
         \includegraphics[width=0.7\textwidth]{images/jamie_cartoon}
-        \caption{Diagram of several LLP topologies. Image curtesy of Jamie Antonelli}
+        \caption{Diagram of several LLP topologies. Image courtesy of Jamie Antonelli}
         \label{jamie_cartoon}
@@
         Slow and stopped particle searches, on the other hand, are sensitive to detector-stable\fxnote{define?} LLPs that are far more massive\fxnote{be able to quantify} than any stable SM particle.
-The lower velocity of these high-mass particles shows up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$\fxnote{check this number}~\cite{cms_hscp}.
+The lower velocity of these high-mass particles can show up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$\fxnote{check this number}~\cite{cms_hscp}.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy\fxnote{how long and how small?}.
@@
         These\fxnote{I've been saying `these' a lot recently} four approaches cover a wide\fxnote{how wide} range of LLP lifetimes that would be missed in traditional searches.
-The next section will look  at a recent example of each analysis type from either ATLAS or CMS.
+The next sections will examine a recent example of each analysis type from either ATLAS or CMS.
 
@@
 
-        This search\fxnote{repetative wording} uses a simplified benchmark model in the Split SUSY paradigm where gluinos are kinematically accessible but squarks are not.
+        This search\fxnote{repetitive wording} uses a simplified benchmark model in the Split SUSY paradigm where gluinos are kinematically accessible but squarks are not.
 The relevant process, shown in Fig.~\ref{displaced_process}, is pair-produced gluinos that decay to a quark-\fxnote{how to punctuate?}virtual squark pair.
@@
 The large mass of the intermediate squark suppresses the gluino decay, giving the gluino enough time to form an R-hadron\fxnote{first use.
-Define here if not in LLP section} that propagates some measureable distance before decaying.
+Define here if not in LLP section} that propagates some measurable distance before decaying.
 
@@
 
-        Jets and $\MET$ are reconstructed as in conventional analyses, but dispaced vertices demand special care when identifying tracks.
+        Jets and $\MET$ are reconstructed as in conventional analyses, but displaced vertices demand special care when identifying tracks.
 The standard ATLAS tracking algorithm constrains the transverse and longitudinal impact parameters ($\mathrm{d}_0$ and $\mathrm{z}_0$, respectively) of potential tracks, so the authors employ an additional algorithm, referred to as large-radius tracking (LRT).
@@
         The authors minimize the effect of hadronic interactions by vetoing the material-dense regions of the detector (see Fig.~\ref{material_map}) and estimate the residual background by extrapolating from the low-mass region, which is dominated by hadronic interactions.
-After a dedicated study, the background from merged vertices was found to be negligable.
-Finally, the background from crossing tracks is determined with a model that adds pseudo-tracks to data vertices and is normalized by comparing the sample of 3-track vertices in data to (2+1)-track vertices in the model.
+After a dedicated study, the background from merged vertices was found to be negligible.
+Finally, the background from crossing tracks is determined from a model that adds pseudo-tracks to data vertices.
 
@@
 what is amsb?}, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate\fxnote{why?
-how typical?}) that eventaully decays to the neutralino LSP and, commonly, a pion\fxnote{why?}.
+how typical?}) that eventually decays to the neutralino LSP and, commonly, a pion\fxnote{why?}.
 The nearly-degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
@@
         Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 datataking and CMS before 2017 datataking should increase sensitivity to decays at shorter radii \fxnote{I haven't mentioned previous iterations when talking about other analyses}.
-The ALTAS search presented here is sensitive to LLP lifetimes of approximately \SI{10}{\pico\s} to \SI{10}{\nano\s} \fxnote{make sure I'm talking about lifetime sensitivity in the same way across analyses}.
+The ATLAS search presented here is sensitive to LLP lifetimes of approximately \SI{10}{\pico\s} to \SI{10}{\nano\s} \fxnote{make sure I'm talking about lifetime sensitivity in the same way across analyses}.
 
         The authors consider two signal processes, both shown in Fig.\ref{disappearing_processes}: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET.
-Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically unaccessable\fxnote{why?}, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
+Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically inaccessible\fxnote{why?}, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
 
@@
         Disappearing track candidates, called pixel tracklets, are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard reconstruction algorithm.
-The pixel tracklets are required to pass several isolation, $\pT$\fxnote{has $\pT$ been defined?}, and quality requirements such as number of pixel layer hits.
+The pixel tracklets are required to pass several isolation, transverse momentum ($\pT$), and quality requirements such as number of pixel layer hits.
 Finally, the disappearing tracks are selected by requiring exactly zero associated hits in the subsequent tracking layer.
@@
 
-        Pixel tracklets can be faked by random combinations of unrealted hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
+        Pixel tracklets can be faked by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
 These backgrounds come primarily from $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and estimates for each type of background are obtained from data.
@@
 This process is exactly the same as in Fig.~\ref{displaced_process}, but in this case the gluino has enough time to form R-hadrons\fxnote{double check}.
-The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.
+The gluino decay is suppressed by the large squark mass, which leads to its appreciable lifetime.
 
@@
     \subsection{Heavy Stable Charged Particles}
-        Particles that live for more than a couple \SI{}{ns}\fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
-If such a particle is also sufficiently massive, it can be catigorized as a heavy stable charged particle (HSCP).
-HSCPs are characterterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material\fxnote{redundant w/ overview.
+        Particles that live for more than a couple \SI{}{nano\s}\fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
+If such a particle is also sufficiently massive, it can be categorized as a heavy stable charged particle (HSCP).
+HSCPs are characterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material\fxnote{redundant w/ overview.
 Probably better explained here than there}.
@@
         \includegraphics[width=0.4\textwidth]{images/hscp_dedx}
-            \caption{Ionization energy loss as a function of momentum for paticles of varying mass and charge~\cite{cms_hscp}}
+            \caption{Ionization energy loss as a function of momentum for particles of varying mass and charge~\cite{cms_hscp}}
         \label{hscp_dedx}
@@
         HSCPs will often be misidentified or missed entirely by standard reconstruction algorithms and analysis criteria, which tend to assume $\beta \approx \num{1}$ and $\lvert q \rvert = e$.
-Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models\fxnote{do I need figures for these?}: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived leptonlike fermions with arbitrary electric charge.
+Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models\fxnote{do I need figures for these?}: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived lepton-like fermions with arbitrary electric charge.
 This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY\fxnote{why?}.
@@
 
-        \fxnote{I show seperate trk, trk+tof limits but never explain that in text} 
+        \fxnote{I show separate trk, trk+tof limits but never explain that in text} 
         \noindent \begin{figure}[htbp] \begin{center}
@@
 No well-defined, universally-agreed-upon criteria exist, but certain themes recur in many discussions of natural model building~\cite{craig, vestiges, evans_toward_full, feng, cornering, kim}.
-The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits\fxnote{Did I just steal Chris's langauge?}.
+The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits\fxnote{Did I just steal Chris's language?}.
 
     \fxnote{I should be able to combine or reorganize the next two paragraphs to flow better} 
-    The parameters of interest are the Higgsino\fxnote{careful - do I mean lightest higgsino?}, stop, and gluino masses, which correct the Higgs mass at tree-level, one-loop, and two-loops, respectively (see Eqs.~\ref{higgsino_correction}-~\ref{gluino_correction}).
+    The parameters of interest are the Higgsino\fxnote{careful - do I mean lightest higgsino?}, stop, and gluino masses, which correct the Higgs mass at tree-level, one-loop, and two-loops, respectively (see Eqs.~\ref{higgsino_correction}-\ref{gluino_correction}).
 Furthermore, the stop and gluino masses are correlated --- a large difference between the two would itself be unnatural~\cite{cornering}.
@@
     Natural SUSY scenarios, then, are most likely to be constrained by limits on the stop, gluino, and Higgsino masses.
-The Higgsino, however, does not carry color charge and is far less likely\fxnote{be able to quantify} to be produced at the LHC, leaving stop and gluino mass limits as the most important general contraints on natural SUSY models.
+The Higgsino, however, does not carry color charge and is far less likely\fxnote{be able to quantify} to be produced at the LHC, leaving stop and gluino mass limits as the most important general constraints on natural SUSY models.
 As shown in Eqs.~\ref{stop_correction} and~\ref{gluino_correction}, the size of stop and gluino corrections also depends on $\Lambda$, the messenger scale of SUSY breaking.\fxnote{Make sure I understand this.
@@
     \noindent \begin{equation}
-        \Delta_i = \frac{\partial \ln{\mHiggs^2}}{\partial \ln{\alpha_i}} \quad ,
+        \Delta_i = \frac{\partial \ln{\mHiggs^2}}{\partial \ln{\alpha_i}} ,
         \label{fine_tuning}
@@
 
-    \noindent where $\alpha_i$ is a particular model parameter and $\Delta_i$ is the degree of fine tuning assoicated with that parameter.
+    \noindent where $\alpha_i$ is a particular model parameter and $\Delta_i$ is the degree of fine tuning associated with that parameter.
 The overall degree of fine tuning for the model can then be assigned as $\max{\left(\Delta_i\right)}$~\cite{cornering}.
@@
 Before null results and serious constraints started rolling in, it was common to refer to the $\Delta \lesssim 10$ regions of parameter space as natural, but as models are constrained, physicists seem willing to accept greater degrees of fine tuning.
-Feng proposes an interesting way to recast this problem: instead of asking which regions of parameter space are most natural, physicists should instead ask themselves, ``If superpartners were discovered, what level of fine fine-tuning would be sufficient to convince me that the gauge hierarchy problem is solved by sypersymmetry and I should move on to researching other problems?"\fxnote{paraphrase for brevity?} Anecdotally, fine tuning thresholds tend to increase when the question is posed in this way~\cite{feng}.
+Feng proposes an interesting way to recast this problem: instead of asking which regions of parameter space are most natural, physicists should instead ask themselves, ``If superpartners were discovered, what level of fine tuning would be sufficient to convince me that the gauge hierarchy problem is solved by supersymmetry and I should move on to researching other problems?"\fxnote{paraphrase for brevity?} Anecdotally, fine tuning thresholds tend to increase when the question is posed in this way~\cite{feng}.
 
@@
 Fig.~\ref{cornering_limits} shows the results from one such attempt using $\approx \SI{15}{\femto\barn^{-1}}$ of \SI{13}{\tera\electronvolt} data for the cases of Effective SUSY, RPV SUSY, and a model that combines RPV with Effective SUSY.
-The authors find that for $\mu \leq \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space remains viable in all cases but also project that all considered $\Delta < 10$ parameter space can be excluded within the next few years\fxnote{check}.
+The authors find that for $\mu = \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space is currently viable in all cases but, barring discovery, will be excluded within the next few years\fxnote{check}.
 
@@
         \end{center} \end{subfigure}
-        \caption{Limits.~\cite{cornering}}
+            \caption{Comparing experimental limits to $\Delta < 10$ naturalness bounds for Effective (left), RPV (center), and Effective+RPV (right) SUSY models ~\cite{cornering}.}
         \label{cornering_limits}
@@
 Approaching analyses is this way often results in nearly background-free searches with good signal acceptance for the model in question, but it can be difficult to draw general conclusions or assess the complementarity (or redundancy) of different searches~\cite{fate}.
-As the number of LLP searches grows, it will be important to for researchers to design their searches around simplified models that encourage combining results to draw general conclusions~\cite{evans_talk}.
+As the number of LLP searches grows, it will be important to design searches around simplified models that enable researchers to combine and compare results to draw general conclusions.~\cite{evans_talk}.
 
@@
 By recasting several LLP searches similar to those described in Sec.~\ref{analyses}, Evans and Shelter looked at the current viability of several SUSY spectra that predict long-lived staus.
-They identified significant gaps in coverage for models with displaced taus or same-sign displaced leptons, which appear in several well-motivated models such as GMSB, which frequently predicts NLSP staus that can become long-lived or certain RPV couplings that lead to same-flavor leptons~\cite{ll_staus}.
+They identified significant gaps in coverage for models with displaced taus or same-sign displaced leptons, signals that appear in several well-motivated models such as GMSB, where staus are commonly the NLSP, and RPV, where certain couplings lead to same-flavor leptons~\cite{ll_staus}.
 
-    The uniqueness of LLP signatures and idosyncrasy of LLP analyses leads to a broad and diverse set of analyses that will surely grow as viable natural parameter space shrinks and more imaginations are turned to filling in the gaps.
+    The uniqueness of LLP signatures and idiosyncrasy of LLP analyses leads to a broad and diverse set of analyses that will surely grow as viable natural parameter space shrinks and more imaginations are turned to filling in the gaps.
 Fully covering natural SUSY parameter space will take a dedicated effort from the LLP community, both to maximize the reach of individual searches and to design complementary analyses that can be used to draw general conclusions.

### 2017-08-03 tex/draft.tex
Fix and label diagrams; other small fixes

@@
         \feynmandiagram [layered layout, horizontal=b to c] {
-            a -- [scalar] b,
-            b -- [fermion, half left] c,
+            a [particle=\(H\)] -- [scalar] b,
+            b -- [fermion, half left, edge label=\(f\)] c,
             c -- [fermion, half left] b,
-            c -- [scalar] d,
+            c -- [scalar] d [particle=\(H\)],
         };
@@
         \feynmandiagram [layered layout, horizontal=b to c] {
-            a -- [fermion] b,
+            a [particle=\(f\)] -- [fermion] b,
             b -- [fermion] c,
-            b -- [photon, half left] c,
+            b -- [photon, half left, edge label=\(\gamma\)] c,
             c -- [opacity=0.0, half left] b,
-            c -- [fermion] d,
+            c -- [fermion] d [particle=\(f\)],
         };
@@
         \feynmandiagram [inline=(d.base), layered layout, medium, horizontal=b to c] {
-        a -- [scalar] b,
-        b -- [fermion, half left] c,
+            a [particle=\(H\)] -- [scalar] b,
+            b -- [fermion, half left, edge label=\(t\)] c,
             c -- [fermion, half left] b,
-        c -- [scalar] d,
+            c -- [scalar] d [particle=\(H\)],
     };
     \quad + \quad
-        \begin{tikzpicture}
-            \begin{feynman}
-                \diagram [baseline={(current bounding box.center)}, horizontal=a to c] {
-                    a -- [scalar] b,
-                    b -- [scalar] c,
+        \feynmandiagram [inline=(d.base), horizontal=a to b, layered layout, medium] {
+            a [particle=\(H\)] -- [scalar] b [dot] 
+            -- [out=135, in=45, loop, min distance=2.5cm, charged scalar, edge label=\(\tilde{t}\)] b 
+            -- [scalar] c [particle=\(H\)],
         };
-                \draw (b) arc [charged scalar, start angle=270, end angle=90, radius=0.7cm];
-            \end{feynman}
-        \end{tikzpicture}
         \quad = \quad 0 \quad
-        \caption{Broken! Corrections to the Higgs mass from the top (left) and stop (right) cancel in exact SUSY. Diagram created with~\cite{tikz}}
+        \caption{Corrections to the Higgs mass from the top (left) and stop (right) cancel in exact SUSY. Diagram created with~\cite{tikz}}
         \label{exact_susy_correction}
@@
         \feynmandiagram [layered layout, horizontal=a to b] {
-            a -- [plain, gluon] b,
-            b -- [anti charged scalar] c,
-            b -- [fermion] d,
-            c -- [anti fermion] e,
-            c -- [plain, boson] f,
+            a [particle=\(\tilde{g}\)] -- [plain, gluon] b,
+            b -- [anti charged scalar, edge label=\(\tilde{q}\)] c,
+            b -- [fermion] d [particle=\(q\)],
+            c -- [anti fermion] e [particle=\(q\)],
+            c -- [plain, boson] f [particle=\(\tilde{\chi}_1^0\)],
         };
@@
     \subsection{Heavy Stable Charged Particles}
-        Particles that live for more than a couple \SI{}{nano\s}\fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
+        Particles that live for more than a couple \SI{}{\nano\s}\fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
 If such a particle is also sufficiently massive, it can be categorized as a heavy stable charged particle (HSCP).
@@
         The trigger requires all events to have either a high-$\pT$ muon or large $\MET$.
-The high-$\pT$ muon trigger is more efficient for all benchmark models except the case where the R-hadron becomes neutral before reaching the MS.
-In the case where the R-hadron does not leave a track in the MS, the large MET trigger should recover some events.\fxnote{Clunky wording}
+The high-$\pT$ muon trigger is more efficient for all benchmark models except the when the R-hadron becomes neutral before reaching the MS.
+In that case, the large MET trigger should recover some events.
 
@@
 A somewhat typical set of values is given in~\cite{drees_kim}: $m_{\tilde{H}} \lesssim \SI{500}{\giga\electronvolt}$, $m_{\tilde{t}} \lesssim \SI{1.5}{\tera\electronvolt}$, and $m_{\tilde{g}} \lesssim \SI{3}{\tera\electronvolt}$.
-Fig.~\ref{atlas_susy_summary} summarizes current SUSY limits from ATLAS searches (CMS limits are generally similar, but a recent plot is not available).
+Fig.~\ref{atlas_susy_summary} summarizes current SUSY limits from ATLAS searches.
 Upon inspection, one sees that experimental limits are starting to push on naturalness bounds in many scenarios.
@@
     Combining results from several searches can also elucidate new directions for important searches.
-By recasting several LLP searches similar to those described in Sec.~\ref{analyses}, Evans and Shelter looked at the current viability of several SUSY spectra that predict long-lived staus.
+By recasting several LLP searches similar to those described in Sec.~\ref{analyses}, Evans and Shelten looked at the current viability of several SUSY spectra that predict long-lived staus.
 They identified significant gaps in coverage for models with displaced taus or same-sign displaced leptons, signals that appear in several well-motivated models such as GMSB, where staus are commonly the NLSP, and RPV, where certain couplings lead to same-flavor leptons~\cite{ll_staus}.

### 2017-08-04 tex/draft.tex
Address comments

@@
 
-    Experimentally, the $\Wpm$, $\Z$, quarks, and charged leptons are massive\fxnote{Gloss over neutrino mass?}.
-Explicit mass terms for the fermions or gauge bosons would violate the chiral and gauge symmetries of the SM Lagrangian, however, so $\SUtwoLUoneY$ must be broken.
+    Experimentally, the $\Wpm$, $\Z$, quarks, and leptons are massive.
+Explicit mass terms for the fermions or gauge bosons would violate the chiral and gauge symmetries of the SM Lagrangian, however, so $\SUtwoLUoneY$ must be broken\fxnote{why can't you explicitly break gauge symmetry?}.
 Specifically, the nonzero vacuum expectation value (VEV)\fxnote{maybe just use $v$} of the Higgs field spontaneously breaks $\SUtwoLUoneY$ to $\UoneQ$.
@@
 The remaining degree of freedom is the physical Higgs boson.
-Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}.
+Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}\fxnote{This still doesn't sound right to me.
+The Yukawa interactions aren't produced by anything other than somebody ad-hoc adding the terms to the Lagrangian.
+Masses for the gauge bosons are an inherent feature of the Higgs mechanism, masses for the fermions are an ad-hoc extension, says Andrew}.
 These terms are interpreted as giving mass to the quarks and charged leptons, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$~\cite{sm_intro}.
@@
 Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely.
-In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important~\cite{giudice_naturally}.
-While it's possible that the bare mass and all corrections just so happen to cancel so perfectly, such miraculous fine tuning could also be a hint that a deeper physical mechanism is at work.
+In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Planck scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important~\cite{giudice_naturally}.
+While it is possible that the bare mass and all corrections just so happen to cancel so perfectly, such miraculous fine tuning could also be a hint that a deeper physical mechanism is at work\fxnote{be prepared to offer historical examples of times when fine tuning was a hint of some deeper theory and times when it was not}.
 
@@
 
-    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay.
+    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly virtual intermediate states, or (4) limited phase space in which to decay.
 In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the lightest particles carrying their respective conserved quantities.
 Neutrons and muons, whose decays are shown in Fig.\ref{sm_llp_processes}, are long-lived for reasons (2), (3), and (4).
-Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay.
-\fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}
+Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay\fxnote{Alan doesn't think the muon-electron mass difference is that small...}.
 
@@
 Conserving the product of R-parity at each vertex has two immediate phenomenological consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
-A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches~\cite{primer}.
+A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches~\cite{primer}\fxnote{could mention DM as well}\fxnote{Andrew says define met and maybe explain how weakly interacting stable particles produce met}.
 
@@
 Models in the Split SUSY paradigm, for example, propose that the scalar sparticles are significantly more massive than the gauginos.
-In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark~\cite{kilian_split}.
-\fxnote{mention that Split throws out naturalness motivation?} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the winos as the lightest gauginos, which leads to nearly-degenerate LSP and NLSP.
-The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space~\cite{randall_sundrum_out_of_this_world}.
+In these models, the gluino becomes long-lived when its decay to a quark-antiquark pair and neutralino is mediated by a highly virtual squark~\cite{kilian_split}.
+\fxnote{mention that Split throws out naturalness motivation?} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the winos as the lightest gauginos, which leads to nearly degenerate LSP and NLSP.
+The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space~\cite{randall_sundrum_out_of_this_world}\fxnote{the winos, binos, and higgsinos are not mass eigenstates, so they are not what we search for in an experiment.
+We search for charginos and neutralinos, which are linear combinations of winos, binos, and higgsinos, says andrew}.
 
@@
         \fxnote{Mention that ATLAS is similar, says Andrew}  
-        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}.
-To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{4}{\tesla} superconducting solenoid.
+        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC)\fxnote{Make sure you are able to simply explain how the LHC works during your talk: how does it accelerate protons, how does it curve their trajectories in a circle, etc, says andrew}, a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}.
+To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{3.8}{\tesla} superconducting solenoid.
 All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}~\cite{cms_experiment}.
@@
         The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately \num{124} million silicon pixels, each of which covers an active area of \num{100} by \SI{150}{\micro\meter^2}.
-The pixels are spread between four barrel layers (BPix) at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks (FPix) at $\num{29} < \mathrm{z} < \SI{52}{cm}$.
-The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\eta < \num{2.4}$ and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017~\cite{cms_pixel_upgrade}.
+The pixels are spread between four barrel layers at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks at $\num{29} < \mathrm{z} < \SI{52}{cm}$.
+The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\lvert\eta\rvert < \num{2.4}$\fxnote{define eta} and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017~\cite{cms_pixel_upgrade}.
 
@@
 
-        The barrel section (EB) extends radially from \num{129} to \SI{177}{cm} and covers a pseudorapidity range of \num{0} to \num{1.479}.
+        The barrel section extends radially from \num{129} to \SI{177}{cm} and covers a pseudorapidity range of \num{0} to \num{1.479}.
 The crystals are tapered to approximately project back to the IP\fxnote{define if not already} but not so perfectly that likely particle trajectories align with cracks.
-Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.
+Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.\fxnote{Why do electrons and photons shower in the ECAL but not (usually) hadrons?, asks andrew}
 
-        The crystals in each endcap section (EE) are arranged in an x-y grid that starts at $\lvert z \rvert = \SI{315}{cm}$ and covers a pseudorapidity range of \num{1.479} to \num{3.0}.
+        The crystals in each endcap section are arranged in an x-y grid that starts at $\lvert z \rvert = \SI{315}{cm}$ and covers a pseudorapidity range of \num{1.479} to \num{3.0}.
 Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals.
@@
 
-        In the barrel detector (BD), four layers of DTs and RPCs are embedded in the solenoid return yoke at \num{4.0}, \num{4.9}, \num{5.9}, and \SI{7.9}{m}.
-The maximum drift length is \SI{2}{\cm} and the single point resolution is \SI{200}{\cm}.
+        In the barrel detector, four layers of DTs and RPCs are embedded in the solenoid return yoke at \num{4.0}, \num{4.9}, \num{5.9}, and \SI{7.9}{m}.
+The maximum drift length is \SI{2}{\centi\m} and the single point resolution is \SI{200}{\micro\m}.
 When reconstructing a vector describing the muon momentum, the $\phi$ precision is better than \SI{100}{\micro\m} in position and \SI{1}{\milli\radian} in direction.
 
-        Each muon endcap detector (ME) is composed of four layers of CSCs and three layers of RPCs.
+        Each muon endcap detector is composed of four layers of CSCs and three layers of RPCs.
 Each CSC has six gas gaps with radial cathode strips and nearly perpendicular planes of anode wires.
@@
 L1 analyzes input from ECAL, HCAL, and MS with custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us.
-The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz\cite{cms_experiment, cms_trigger_upgrade}.
+With input from all subdetectors, the HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz\cite{cms_experiment, cms_trigger_upgrade}.
 
@@
         Slow and stopped particle searches, on the other hand, are sensitive to detector-stable\fxnote{define?} LLPs that are far more massive\fxnote{be able to quantify} than any stable SM particle.
-The lower velocity of these high-mass particles can show up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$\fxnote{check this number}~\cite{cms_hscp}.
+The lower velocity of these high-mass particles can show up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta = \frac{v}{c} > \num{0.9}$\fxnote{check this number}~\cite{cms_hscp}.
 Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy\fxnote{how long and how small?}.
@@
 how typical?}) that eventually decays to the neutralino LSP and, commonly, a pion\fxnote{why?}.
-The nearly-degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
+The nearly degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
 The low-momentum pion is then unlikely to be reconstructed, which results in a disappearing track~\cite{atlas_disappearing}.
@@
 
-        Pixel tracklets can be faked by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
+        Pixel tracklets can be faked\fxnote{don't use faked, says CMS} by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
 These backgrounds come primarily from $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and estimates for each type of background are obtained from data.
@@
         This analysis is interpreted in the context of two potential LLPs: gluinos and multiply charged massive particles (mchamps).
-Long-lived gluinos can appear in models such as Split SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light.
+Sticking with the natural SUSY theme, this discussion will focus on long-lived gluinos, which appear in models such as Split SUSY when squarks and sleptons are quite heavy, but the gluinos are relatively light.
 After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.
@@
         After estimating the background by extrapolating data from the cosmic-enriched\fxnote{enriched how?
-be able to explain} region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculate the expected background for LLP lifetimes ranging from \SI{100}{\nano\s} to \SI{1}{\micro\s}.
+be able to explain} region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculate the expected background for LLP lifetimes ranging from $10^{-7}$ to $10^6$ s.
 In all cases, the expected background is less then one event.
@@
     \subsection{Heavy Stable Charged Particles}
-        Particles that live for more than a couple \SI{}{\nano\s}\fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
+        Particles that live for more than about \SI{25}{\nano\s} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying.
 If such a particle is also sufficiently massive, it can be categorized as a heavy stable charged particle (HSCP).
@@
     Interpreting current limits in the context of naturalness requires some set of criteria that determine if a model is natural.
-No well-defined, universally-agreed-upon criteria exist, but certain themes recur in many discussions of natural model building~\cite{craig, vestiges, evans_toward_full, feng, cornering, kim}.
+No well-defined, universally agreed upon criteria exist, but certain themes recur in many discussions of natural model building~\cite{craig, vestiges, evans_toward_full, feng, cornering, kim}.
 The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits\fxnote{Did I just steal Chris's language?}.

### 2017-08-04 tex/draft.tex
Integrate Stan's comments

@@
 
-    Experimentally, the $\Wpm$, $\Z$, quarks, and leptons are massive.
+    Experimentally, the $\Wpm$, $\Z$, quarks, and leptons are massive\fxnote{know about the weinberg angle, first measured precisely in neutrino electron elastic scattering}.
 Explicit mass terms for the fermions or gauge bosons would violate the chiral and gauge symmetries of the SM Lagrangian, however, so $\SUtwoLUoneY$ must be broken\fxnote{why can't you explicitly break gauge symmetry?}.
@@
         \fxnote{Mention that ATLAS is similar, says Andrew}  
-        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC)\fxnote{Make sure you are able to simply explain how the LHC works during your talk: how does it accelerate protons, how does it curve their trajectories in a circle, etc, says andrew}, a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}.
-To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{3.8}{\tesla} superconducting solenoid.
+        \fxnote{Know about the beam, says stan}  
+        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC)\fxnote{Make sure you are able to simply explain how the LHC works during your talk: how does it accelerate protons, how does it curve their trajectories in a circle, etc, says andrew}, a circular collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}.
+To reconstuct final-state particles, CMS uses a particle-flow algorithm that combines information from several subdetectors nested radially in and around a \SI{3.8}{\tesla} superconducting solenoid.
 All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}~\cite{cms_experiment}.
@@
 The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necessitates photodetectors with intrinsic gain that work in magnetic fields\cite{cms_experiment, cms_tdr}.
+Energy resolution is varies from approximately \num{1}-\SI{5}{\percent} depending on the amount of material traversed before reaching ECAL~\cite{ecal_performance}.
 
@@
 The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
-Combining MS and tracker measurements improves the muon momentum resolution at high momenta where the tracker resolution declines \fxnote{quantify or show std plot?}\cite{cms_experiment, cms_tdr}.
+Combining MS and tracker measurements improves the muon momentum resolution at high momenta where the tracker resolution declines (see Fig.~\ref{muon_pt_resolution}\cite{cms_experiment, cms_tdr}.
+
+        \noindent \begin{figure}[htbp] \begin{center}
+        \includegraphics[width=0.5\textwidth]{images/muon_pt_resolution}
+            \caption{Transverse momentum resolution in the tracker and muon system for small (left) and large (right) pseudorapidity~\cite{cms_image}.}
+        \label{muon_pt_resolution}
+        \end{center} \end{figure}
 
@@
 
-    \subsection{Trigger}
+    \subsection{Trigger and Particle Reconstruction}
         \fxnote{Is entire detector read out at L1?}

### 2017-08-04 tex/draft.tex
Add draft

@@
 \begin{abstract}
-
-I'll write an abstract here.
+    In the standard model, the mass of the Higgs boson is unnaturally small.
+Beyond the standard model (BSM) theories, such as supersymmetry, explain the smallness of the Higgs boson mass while also predicting new phenomena that could potentially be observed at the Large Hadron Collider (LHC).
+As natural BSM models are increasingly constrained by null results, it becomes important to identify signals that would be missed in conventional analyses, such as long-lived BSM particles.
+This paper explores the motivation for natural BSM theories that predict long-lived particles, provides an overview of the CMS detector, reviews several recent long-lived particle searches, and discusses the current status and future prospects of natural BSM models.
 

### 2017-08-05 tex/draft.tex
Dumb down SM section

@@
 \doublespacing
-\linenumbers
+%\linenumbers
 \pagenumbering{arabic}
 
-% Things to check
-\fxnote{When should symbols be italicized and when should they be mathrm'd?} 
-\fxnote{fine-tuning or fine tuning?}
+\section{The Standard Model} \label{SM}
+    The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing accuracy.
+The SM consists of twelve spin-$\frac{1}{2}$ particles, the fermions, that make up all observed matter; twelve spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces; and one fundamental scalar, the Higgs boson, which breaks electroweak symmetry, giving mass to the gauge bosons and fermions.
 
-\section{The Standard Model} \label{SM}
-    The standard model of particle physics (SM) describes all known particles and their non-gravitational interactions and is experimentally verified to astonishing \fxnote{weak word} accuracy.
-The SM consists of \num{12} spin-$\frac{1}{2}$ particles, the fermions, that make up all observed matter; \num{12} spin-1 particles, the gauge bosons, that communicate the electromagnetic, weak, and strong forces; and one fundamental scalar, the Higgs boson, which will be described in detail below.
-
-    All SM particles transform according to the gauged symmetry group\fxnote{be good at describing the meaning of `gauged symmetry group'} $\SUthreecSUtwoLUoneY$, where $\SUthreec$ is associated with color charge, $\SUtwoL$ is associated with weak isospin, and $\UoneY$ is associated with weak hypercharge.
-The gauge bosons are associated with the generators of these groups, thus there are eight gluons associated with $\SUthreec$, three W bosons associated with $\SUtwoL$, and one B boson associated with $\UoneY$.
-The physical gauge bosons, which are linear combinations of the Ws and B, are the $\Wp$, $\Wm$, $\Z$, and photon ($\gamma$).
-The fermions are categorized by which representation of each group they fit into\fxnote{make sure I'm good at explaining this}.
-For example, $\SUthreec$ distinguishes the quarks (which live in the fundamental representation) from the leptons (which are singlets), and $\SUtwoL$ distinguishes the left-handed fermions (doublets) from the right-handed fermions (singlets).
-Finally, weak hypercharge further distinguishes SM particles according to the Gell-Mann--Nishijima formula, $Y=Q-I_3$, where $Q$ is electric charge and $I_3$ is the third component of weak isospin~\cite{sm_intro}.
-
-    Experimentally, the $\Wpm$, $\Z$, quarks, and leptons are massive\fxnote{know about the weinberg angle, first measured precisely in neutrino electron elastic scattering}.
-Explicit mass terms for the fermions or gauge bosons would violate the chiral and gauge symmetries of the SM Lagrangian, however, so $\SUtwoLUoneY$ must be broken\fxnote{why can't you explicitly break gauge symmetry?}.
-Specifically, the nonzero vacuum expectation value (VEV)\fxnote{maybe just use $v$} of the Higgs field spontaneously breaks $\SUtwoLUoneY$ to $\UoneQ$.
-In the process, three of the four degrees of freedom associated with the complex Higgs doublet become the longitudinal polarizations of $\Wpm$ and $\Z$, giving them mass.
-The remaining degree of freedom is the physical Higgs boson.
-Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}\fxnote{This still doesn't sound right to me.
-The Yukawa interactions aren't produced by anything other than somebody ad-hoc adding the terms to the Lagrangian.
-Masses for the gauge bosons are an inherent feature of the Higgs mechanism, masses for the fermions are an ad-hoc extension, says Andrew}.
-These terms are interpreted as giving mass to the quarks and charged leptons, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$~\cite{sm_intro}.
-
-    \noindent \begin{equation}
-        \mathcal{L} = -\frac{yv}{\sqrt{2}}\bar{\psi}\psi 
-        \label{yukawa_terms}
-    \end{equation}
-
-    SM parameters, such as masses and couplings, are corrected by interactions with virtual particles through loop diagrams.
-Fig.~\ref{loop_diagrams}, for example, shows interactions that correct the Higgs and electron masses.
-Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid.
-The fermions and gauge bosons, on the other hand, only depend logarithmically\fxnote{be able to work out example} on $\Lambda$~\cite{dine_naturalness}.
-The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the bare Higgs mass and the terms that correct it.
+    The fermions and gauge bosons can be classified according to the forces with which they interact.
+The fermions are further divided into six quarks, which carry color and interact via the strong force, and six leptons, which do not.
+Furthermore, all six quarks and three leptons (the electron, muon, and tau) carry electric charge and interact electromagnetically.
+All fermions interact via the weak force.
+The gauge bosons are comprised of the photon, which communicates the electromagnetic force; the $\mathrm{W}^+$, $\mathrm{W}^-$, and $\mathrm{Z}$, which communicate the weak force; and eight gluons that communicate the strong force.
+Of these, only the $\mathrm{W}^+$ and $\mathrm{W}^+$ are electrically charged and only the gluons carry color charge.
 
@@
 
+    SM parameters, such as masses and couplings, are corrected by interactions with virtual particles through loop diagrams.
+Fig.~\ref{loop_diagrams}, for example, shows interactions that correct the Higgs and electron masses.
+Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid.
+The fermions and gauge bosons, on the other hand, only depend logarithmically on $\Lambda$~\cite{dine_naturalness}.
+The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the bare Higgs mass and the terms that correct it.
+
 \section{Naturalness and the Higgs mass}
@@
 In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Planck scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important~\cite{giudice_naturally}.
-While it is possible that the bare mass and all corrections just so happen to cancel so perfectly, such miraculous fine tuning could also be a hint that a deeper physical mechanism is at work\fxnote{be prepared to offer historical examples of times when fine tuning was a hint of some deeper theory and times when it was not}.
+While it is possible that the bare mass and all corrections just so happen to cancel so perfectly, such miraculous fine tuning could also be a hint that a deeper physical mechanism is at work.
 
@@
 
-    Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions\fxnote{I need to be better at explaining exactly what this means}.
-In its simplest form, SUSY results in one new boson for every SM fermion, one new fermion for every SM boson, and one new Higgs doublet.\fxnote{make sure I understand the new Higgs doublet} The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
+    Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions.
+In its simplest form, SUSY results in one new boson for every SM fermion, one new fermion for every SM boson, and one new Higgs doublet.
+The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
 stop or smuon), and the spin-$\frac{1}{2}$ superpartners to the SM bosons are given the name of their SM counterpart with ``ino" tacked on to the end (e.g.
@@
 
-    \fxnote{Fix diagram} 
-    \fxnote{Add particle labels} 
     \noindent \begin{figure}[htbp] \begin{center}
@@
         \quad = \quad 0 \quad
-        \caption{Corrections to the Higgs mass from the top (left) and stop (right) cancel in exact SUSY. Diagram created with~\cite{tikz}}
+        \caption{Corrections to the Higgs mass from the top (left) and stop (right) cancel in exact SUSY. Diagram created with~\cite{tikz}.}
         \label{exact_susy_correction}
@@
             };
-            \caption{Long-lived decays of the neutron and muon. Diagram created with~\cite{tikz}}
+            \caption{Long-lived decays of the neutron and muon. Diagram created with~\cite{tikz}.}
             \label{sm_llp_processes}
@@
     In SUSY models, LLPs arise for the same basic reasons, and different SUSY models produce LLPs in different ways.
-The most straightforward SUSY LLP occurs in models with conserved R-parity, a proposed symmetry that prevents proton decay~\cite{primer}\fxnote{Be prepared to show this.
-Maybe add some diagrams illustrating proton decay w/o R-parity}.
+The most straightforward SUSY LLP occurs in models with conserved R-parity, a proposed symmetry that prevents proton decay~\cite{primer}.
 In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1.
@@
 The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which suppresses the NSLP decay rate and can lead to LLPs~\cite{dimopoulos_low_energy}.
-
-    \fxnote{diagram or eqs for R-parity / RPV?}
 
@@
         \fxnote{Mention that ATLAS is similar, says Andrew}  
-        \fxnote{Know about the beam, says stan}  
-        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC)\fxnote{Make sure you are able to simply explain how the LHC works during your talk: how does it accelerate protons, how does it curve their trajectories in a circle, etc, says andrew}, a circular collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}.
+        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC), a circular collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}.
 To reconstuct final-state particles, CMS uses a particle-flow algorithm that combines information from several subdetectors nested radially in and around a \SI{3.8}{\tesla} superconducting solenoid.
@@
         \includegraphics[width=0.7\textwidth]{images/cms}
-        \caption{The CMS detector~\cite{cms_image}}
+        \caption{The CMS detector~\cite{cms_image}.}
         \label{cms}
@@
             \includegraphics[width=0.4\textwidth]{images/pixel_old_new}
-            \caption{Diagram showing barrel pixel layers before and after the winter 2016/17 upgrade.~\cite{pixel_old_new}}
+            \caption{Diagram showing barrel pixel layers before and after the winter 2016/17 upgrade~\cite{pixel_old_new}.}
             \label{pixel_old_new}
@@
     \subsection{Electromagnetic Calorimeter}
-        \fxnote{I define EE \& EB but never use those definitions}
         After traversing the inner tracker, particles next encounter the electromagnetic calorimeter (ECAL).
 As a homogeneous scintillation calorimeter, ECAL uses \num{61200} lead tungstate crystals in the barrel and \num{7324} in each endcap to reconstruct the energy deposited during electromagnetic showers.
-Lead tungstate crystals allow for a fast (\SI{80}{\percent} of light within \SI{25}{\nano\s}), compact (radiation length = \SI{0.89}{cm}), fine-grained (Moli\`ere radius = \SI{2.2}{cm}), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter.
+Lead tungstate crystals allow for a fast (\SI{80}{\percent} of light within \SI{25}{\nano\s}), compact (radiation length = \SI{0.89}{cm}), fine-grained (Moli\`ere radius = \SI{2.2}{cm}), and radiation hard (up to 10 Mrad) calorimeter.
 The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necessitates photodetectors with intrinsic gain that work in magnetic fields\cite{cms_experiment, cms_tdr}.
@@
 The crystals are tapered to approximately project back to the IP\fxnote{define if not already} but not so perfectly that likely particle trajectories align with cracks.
-Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.\fxnote{Why do electrons and photons shower in the ECAL but not (usually) hadrons?, asks andrew}
-
+Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.
 The crystals in each endcap section are arranged in an x-y grid that starts at $\lvert z \rvert = \SI{315}{cm}$ and covers a pseudorapidity range of \num{1.479} to \num{3.0}.
-Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals.
-\fxnote{Say what the preshower is for?
-Is it for pi0 rejection?
-If so, how and why?}
 
     \subsection{Hadronic Calorimeter}
-        \fxnote{define HB \& HF never to be used}
         The hadronic calorimeter (HCAL) uses \SI{3.7}{mm} plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers.
@@
 
-        The barrel section (HB) spans a pseudorapidity range of \num{-1.4} to \num{1.4} and has \num{2304} towers \fxnote{check}, each of which contains \num{14} \fxnote{check} brass plates and covers an area of \num{0.087} x \SI{0.087}{in} $\eta-\phi$ \fxnote{get a feel for this area}.
+        The barrel section (HB) spans a pseudorapidity range of \num{-1.4} to \num{1.4} and has \num{2304} towers \fxnote{check}, each of which contains \num{14} \fxnote{check} brass plates and covers an area of \num{0.087} x \SI{0.087}{in} $\eta-\phi$.
 In addition, an extra layer (or two at $\eta = \num{0}$) of scintillator tiles sits just outside the solenoid.
@@
 In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline.
-\fxnote{say why HF is useful or mention crazy flux?}
 
@@
     \subsection{Muon System}
-        \fxnote{Specifically mention CMS design specs to meet physics goals?}
         The muon system (MS), which is the outermost subdetector, detects muons with \num{3} varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps.
-The choice of detector varies between barrel and endcap due to the difference in neutron-induced background\fxnote{what?} , muon rates, and magnetic field strength\fxnote{why does B matter?}.
+The choice of detector varies between barrel and endcap due to the difference in neutron-induced background, muon rates, and magnetic field strength.
 The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification.
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.5\textwidth]{images/muon_pt_resolution}
+        \includegraphics[width=0.6\textwidth]{images/muon_pt_resolution}
         \caption{Transverse momentum resolution in the tracker and muon system for small (left) and large (right) pseudorapidity~\cite{cms_image}.}
@@
 
-    \subsection{Trigger and Particle Reconstruction}
-        \fxnote{Is entire detector read out at L1?}
+    \subsection{Trigger}
         The trigger reduces the data writing rate from the \SI{40}{\mega\hertz} collision rate to less than \SI{1}{\kilo\hertz} so that events can be written to tape.
@@
         \includegraphics[width=0.7\textwidth]{images/jamie_cartoon}
-        \caption{Diagram of several LLP topologies. Image courtesy of Jamie Antonelli}
+        \caption{Diagram of several LLP topologies. Image courtesy of Jamie Antonelli.}
         \label{jamie_cartoon}
@@
 Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed~\cite{atlas_disappearing}.
-Together, these two types of analyses cover a wide range of lifetimes and topologies for LLPs that decay on detector timescales\fxnote{dangerous as hell.
-Be really good at giving a quantitative explanation of this sentence}\fxnote{find something to cite}.
+Together, these two types of analyses cover a wide range of lifetimes and topologies for LLPs that decay on detector timescales\fxnote{find something to cite}.
 
@@
     \subsection{Displaced Vertices}
-        LLPs that decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}\fxnote{Is it still a DV if it decays in active material somewhere?}.
-ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity~\cite{atlas_displaced}.\fxnote{make sure I can explain why met and multiplicity} The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range\fxnote{Am I defining sensitivity range consistently across analyses?}.
+        LLPs that decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}.
+ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity~\cite{atlas_displaced}.
+The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range\fxnote{Am I defining sensitivity range consistently across analyses?}.
 
@@
 
-        \fxnote{Add particle labels} 
         \noindent \begin{figure}[htbp] \begin{center}
-        \feynmandiagram [layered layout, horizontal=a to b] {
+        \feynmandiagram [layered layout, horizontal=a to b, small] {
             a [particle=\(\tilde{g}\)] -- [plain, gluon] b,
@@
         };
-        \caption{Long-lived gluino decay through highly virtual squark. Diagram created with~\cite{tikz}}
+        \caption{Long-lived gluino decay through highly virtual squark. Diagram created with~\cite{tikz}.}
         \label{displaced_process}
@@
         \includegraphics[width=0.6\textwidth]{images/material_map}
-            \caption{Map of material dense regions of the ATLAS detector.\fxnote{explain more}~\cite{atlas_displaced}}
+        \caption{Map of material dense regions of the ATLAS detector\fxnote{explain more}~\cite{atlas_displaced}.}
         \label{material_map}
@@
         Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
-Specifically, models with winos as the lightest gauginos\fxnote{have these words been defined?}, such as many AMSB models\fxnote{why amsb?
-what is amsb?}, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate\fxnote{why?
-how typical?}) that eventually decays to the neutralino LSP and, commonly, a pion\fxnote{why?}.
+Specifically, models with winos as the lightest gauginos\fxnote{have these words been defined?}, such as many AMSB models, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate that eventually decays to the neutralino LSP and, commonly, a pion\fxnote{why?}.
 The nearly degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
@@
 
-        Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 datataking and CMS before 2017 datataking should increase sensitivity to decays at shorter radii \fxnote{I haven't mentioned previous iterations when talking about other analyses}.
-The ATLAS search presented here is sensitive to LLP lifetimes of approximately \SI{10}{\pico\s} to \SI{10}{\nano\s} \fxnote{make sure I'm talking about lifetime sensitivity in the same way across analyses}.
+        Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 datataking and CMS before 2017 datataking should increase sensitivity to decays at shorter radii.
+The ATLAS search presented here is sensitive to LLP lifetimes of approximately \SI{10}{\pico\s} to \SI{10}{\nano\s}.
 
         The authors consider two signal processes, both shown in Fig.\ref{disappearing_processes}: (1) electroweak gaugino production resulting in a disappearing track, an ISR jet, and MET and (2) gluino pair production resulting in a disappearing track, four jets, and MET.
-Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically inaccessible\fxnote{why?}, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
+Process (1) could be the only gaugino production mode at the LHC if the gluino mass is kinematically inaccessible, but process (2), which leads to chargino production in cascade decays, will be dominant if the gluino mass is within reach.
 
-        \fxnote{ugh, this is too hard. just steal diagram from paper or make in jaxodraw. Maybe even use simulated event instead, but make sure I can draw these if asked?}  
         \noindent \begin{figure}[htbp] \begin{center}
@@
         \end{center} \end{subfigure}
-        \fxnote{Can't get it to work in tikz-feynman. Just take from paper for now.} 
-        %\feynmandiagram [layered layout] {
-        %    i1 -- [plain] a [blob],
-        %    i2 -- [plain] a,
-        %    a -- [plain, boson] b [blob],
-        %    a -- [plain] f1,
-        %    a -- [plain, boson] f2,
-        %    b -- [plain, boson] f3,
-        %    b -- [scalar] f4,
-        %};
         \caption{Benchmark signal processes: electroweak gaugino production (left) and gluino pair-production (right)~\cite{atlas_disappearing}.}
@@
 Finally, the disappearing tracks are selected by requiring exactly zero associated hits in the subsequent tracking layer.
-Event selection requires one pixel tracklet, no electron or muon candidates (to suppress $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes\fxnote{why?
-be able to explain}), and the $\MET$ and jet requirements associated with either of the two production modes described above\fxnote{be able to explain} .
+Event selection requires one pixel tracklet, no electron or muon candidates (to suppress $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and the $\MET$ and jet requirements associated with either of the two production modes described above.
 
@@
 These backgrounds come primarily from $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and estimates for each type of background are obtained from data.
-\fxnote{I initially wrote a whole big thing about how each bg was estimated, but I'm thinking it was overkill}
 
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/disappearing_ew_limit}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/disappearing_qcd_200ps_limit}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/disappearing_qcd_1ns_limit}
         \end{center} \end{subfigure}
-            \caption{Limits on chargino mass and lifetime in the electroweak production channel (left) and gluino and chargino masses in the gluon pair-production channel with a \SI{0.2}{\nano\s} (center) and \SI{1.0}{\nano\s} chargino lifetime.~\cite{atlas_disappearing}}
+        \caption{Limits on chargino mass and lifetime in the electroweak production channel (left) and gluino and chargino masses in the gluon pair-production channel with a \SI{0.2}{\nano\s} (center) and \SI{1.0}{\nano\s} chargino lifetime~\cite{atlas_disappearing}.}
         \label{disappearing_limits}
@@
         This analysis uses the muon system to look for pairs of muons that arrive out of time with bunch crossings.
-The main backgrounds to such a signal are cosmic muons, beam halo\fxnote{explain}, and muon system noise.
+The main backgrounds to such a signal are cosmic muons, beam halo, and muon system noise.
 Beam halo and muon system noise are easily removed by selection criteria, but distinguishing signal from cosmic muons requires a more nuanced approach.
-After generating signal MC\fxnote{defined?} and modeling cosmic muons from data obtained in dedicated cosmic runs, the authors found that cosmic muons and signal could be differentiated using TOF information from the muon system RPCs and DTs.
+After generating simulated signal events and modeling cosmic muons from data obtained in dedicated cosmic runs, the authors found that cosmic muons and signal could be differentiated using TOF information from the muon system RPCs and DTs.
 Essentially, the direction of muon momentum could be gleaned from the timing information, and the authors required outgoing muons in both the upper and lower hemispheres.
@@
 
-        \fxnote{check if tof, beta, or bx is better} 
         \noindent \begin{figure}[htbp] \begin{center}
         \includegraphics[width=\textwidth]{images/stopped_reject_cosmic_tof}
-            \caption{Cosmic muon rejection using time-of-flight information from the muon system.~\cite{cms_stopped}}
+        \caption{Cosmic muon rejection using time-of-flight information from the muon system\fxnote{explain}~\cite{cms_stopped}.}
         \label{stopped_muon_differentiation}
@@
         In addition to the above criteria, the authors developed a new muon reconstruction algorithm, called displaced standalone (DSA), that uses only muon system hits and does not constrain the location of the primary vertex in any way.
-The full selection requires exactly one good DSA track in each hemisphere with $\pT$ greater than \SI{50}{\giga\electronvolt}, no reconstructed vertices\fxnote{why?}, and several criteria related to the quality of the reconstructed track and timing measurement.
-Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0) minimize background from beam halo and cosmic muons\fxnote{be able to explain how}.
+The full selection requires exactly one good DSA track in each hemisphere with $\pT$ greater than \SI{50}{\giga\electronvolt}, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement.
+Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0) minimize background from beam halo and cosmic muons.
 
-        After estimating the background by extrapolating data from the cosmic-enriched\fxnote{enriched how?
-be able to explain} region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculate the expected background for LLP lifetimes ranging from $10^{-7}$ to $10^6$ s.
+        After estimating the background by extrapolating data from the cosmic-enriched region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculate the expected background for LLP lifetimes ranging from $10^{-7}$ to $10^6$ s.
 In all cases, the expected background is less then one event.
@@
 
-        \fxnote{ok to skip mchamp? Be able to explain why} 
         \noindent \begin{figure}[htbp] \begin{center}
@@
         \end{center} \end{subfigure}
-            \caption{Upper limits on production cross section as a function of gluino lifetime (left) and mass (right)~\cite{cms_stopped}}
+        \caption{Upper limits on production cross section as a function of gluino lifetime (left) and mass (right)~\cite{cms_stopped}.}
         \label{stopped_limits}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.4\textwidth]{images/hscp_dedx}
-            \caption{Ionization energy loss as a function of momentum for particles of varying mass and charge~\cite{cms_hscp}}
+        \includegraphics[width=0.45\textwidth]{images/hscp_dedx}
+        \caption{Ionization energy loss as a function of momentum for particles of varying mass and charge~\cite{cms_hscp}.}
         \label{hscp_dedx}
@@
 Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models\fxnote{do I need figures for these?}: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived lepton-like fermions with arbitrary electric charge.
-This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY\fxnote{why?}.
-
-        \fxnote{I could talk about how low-beta tracks will show up as zig-zags in DTs b/c reconstruction assumes $\beta \approx \num{1}$.
-Zig-zag offset is used to estimate beta.
-Not sure where to fit it in.} \fxnote{Worth mentioning tracker-only vs tracker+TOF?}
+This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY.
 
@@
 
-        The authors estimate the signal-region background using an ABCD method in which events are binned in a 2-D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region \fxnote{Do I need to explain this?
-I glossed over the fact that they used both an ABCD and an ABCDEFGHI}.
+        The authors estimate the signal-region background using an ABCD method in which events are binned in a 2-D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region.
 Systematic uncertainties are introduced in background estimation, signal acceptance, and integrated luminosity.
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/hscp_limit_tracker_only}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.4\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/hscp_limit_tracker_tof}
         \end{center} \end{subfigure}
-        \caption{Production cross section limits on several particles as a function of mass for the tracker-only and tracker+TOF analyses~\cite{cms_hscp}}
+        \caption{Production cross section limits on several particles as a function of mass for the tracker-only and tracker+TOF analyses~\cite{cms_hscp}.}
         \label{hscp_limits}
@@
     \fxnote{I should be able to combine or reorganize the next two paragraphs to flow better} 
-    The parameters of interest are the Higgsino\fxnote{careful - do I mean lightest higgsino?}, stop, and gluino masses, which correct the Higgs mass at tree-level, one-loop, and two-loops, respectively (see Eqs.~\ref{higgsino_correction}-\ref{gluino_correction}).
+    The parameters of interest are the Higgsino, stop, and gluino masses, which correct the Higgs mass at tree-level, one-loop, and two-loops, respectively (see Eqs.~\ref{higgsino_correction}-\ref{gluino_correction}).
 Furthermore, the stop and gluino masses are correlated --- a large difference between the two would itself be unnatural~\cite{cornering}.
@@
 The Higgsino, however, does not carry color charge and is far less likely\fxnote{be able to quantify} to be produced at the LHC, leaving stop and gluino mass limits as the most important general constraints on natural SUSY models.
-As shown in Eqs.~\ref{stop_correction} and~\ref{gluino_correction}, the size of stop and gluino corrections also depends on $\Lambda$, the messenger scale of SUSY breaking.\fxnote{Make sure I understand this.
-Messenger scale != breaking scale?
-What are the consequences of a lower messenger scale?}
+As shown in Eqs.~\ref{stop_correction} and~\ref{gluino_correction}, the size of stop and gluino corrections also depends on $\Lambda$, the messenger scale of SUSY breaking.
 
@@
 
-    \fxnote{what do I cite?}  
     \noindent \begin{figure}[htbp] \begin{center}
-    \includegraphics[width=0.7\textwidth]{images/atlas_susy_summary}
+    \includegraphics[width=.8\textwidth]{images/atlas_susy_summary}
     \caption{Summary of current experimental limits on SUSY models from ATLAS searches.}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.4\textwidth]{images/fate_limits}
-        \caption{Limits.~\cite{fate}}
+        \includegraphics[width=0.6\textwidth]{images/fate_limits}
+        \caption{Constraints on stop mass in a simplified baryonic RPV model for a wide range of lifetimes from recast LLP searches~\cite{fate}.}
         \label{fate_limits}

### 2017-08-05 tex/draft.tex
Fix great majority of fixme's

@@
     In the standard model, the mass of the Higgs boson is unnaturally small.
-Beyond the standard model (BSM) theories, such as supersymmetry, explain the smallness of the Higgs boson mass while also predicting new phenomena that could potentially be observed at the Large Hadron Collider (LHC).
+Beyond the standard model (BSM) theories, such as supersymmetry (SUSY), explain the smallness of the Higgs boson mass while also predicting new phenomena that could potentially be observed at the Large Hadron Collider.
 As natural BSM models are increasingly constrained by null results, it becomes important to identify signals that would be missed in conventional analyses, such as long-lived BSM particles.
-This paper explores the motivation for natural BSM theories that predict long-lived particles, provides an overview of the CMS detector, reviews several recent long-lived particle searches, and discusses the current status and future prospects of natural BSM models.
+This paper explores the motivation for natural SUSY models that predict long-lived particles, provides an overview of the CMS detector, reviews several recent long-lived particle searches, and discusses the current status and future prospects of natural SUSY models.
 
@@
 The fermions are further divided into six quarks, which carry color and interact via the strong force, and six leptons, which do not.
-Furthermore, all six quarks and three leptons (the electron, muon, and tau) carry electric charge and interact electromagnetically.
+Furthermore, all six quarks and three of the leptons (the electron, muon, and tau) carry electric charge and interact electromagnetically.
 All fermions interact via the weak force.
-The gauge bosons are comprised of the photon, which communicates the electromagnetic force; the $\mathrm{W}^+$, $\mathrm{W}^-$, and $\mathrm{Z}$, which communicate the weak force; and eight gluons that communicate the strong force.
+The gauge bosons include the photon, which communicates the electromagnetic force; the $\mathrm{W}^+$, $\mathrm{W}^-$, and $\mathrm{Z}$, which communicate the weak force; and eight gluons that communicate the strong force.
 Of these, only the $\mathrm{W}^+$ and $\mathrm{W}^+$ are electrically charged and only the gluons carry color charge.
@@
         };
-        \caption{Higgs mass (left) corrected by fermion loop and fermion mass (right) corrected by photon loop. Diagram created with~\cite{tikz}}
+        \caption{Higgs mass (left) corrected by fermion loop and fermion mass (right) corrected by photon loop. Diagrams created with~\cite{tikz}}
         \label{loop_diagrams}
@@
     The naturalness criterion can be formulated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of the higher-energy theory, and (3) any dimensionless parameter much smaller than unity must be protected by a custodial symmetry~\cite{giudice_naturally, thooft_naturalness}.
-Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory\fxnote{wordy and maybe repetitive}.
+Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory.
 This discussion focuses on statement (3), which is in some ways a more nuanced version of (1) that also explains cases where dimensional analysis fails.
 
-    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$~\cite{dine_naturalness}\fxnote{show diagrams and terms?}.
+    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$~\cite{dine_naturalness}.
 Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}~\cite{cms_higgs, atlas_higgs}, a value that must be equal to the sum of the bare mass and all corrections.
@@
     As a fundamental scalar, the Higgs is doubly cursed.
-As explained in section \ref{SM}, $\mHiggs$ is quadratically sensitive to $\Lambda$, but that's not all: the Higgs field also lacks the chiral and gauge symmetries enjoyed by the fermions and gauge bosons.
-These symmetries act as the custodial symmetries mentioned in naturalness statement (3) in that they protect the fermion and gauge boson masses from large corrections.
-Because the SM chiral and gauge symmetries only apply to the massless theory, the SM symmetry group would be enlarged if fermions and gauge bosons were massless.
-That is, if the fermions and gauge bosons were massless at tree level, the chiral and gauge symmetries would cause their masses to be uncorrected to all orders in perturbation theory.
-As massive particles, however, the chiral and gauge symmetries instead guarantee that any corrections to their tree-level masses are proportional to their tree-level masses, preventing any large fine tuning between correction terms~\cite{giudice_naturally}.\fxnote{confusing paragraph.
-Rewrite and add math}
+Not only is its mass quadratically sensitive to $\Lambda$, it also lacks the chiral and gauge symmetries enjoyed by the fermions and gauge bosons.
+These symmetries, referred to as custodial symmetries, protect the fermion and gauge boson masses by guaranteeing that all corrections are proportional to the bare masses.
+Custodial symmetries work because the massless theory is more symmetric than the massive theory, which means that if the fermions and gauge bosons were massless at tree level, they would be uncorrected to all orders in perturbation theory~\cite{giudice_naturally}.
 
-    \fxnote{Clarify that not technically a problem.
-Nature might just be that way.
-Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to the apparently unnatural Higgs mass\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass~\cite{craig}.
+    There are three main approaches to dealing with the apparently unnatural Higgs mass: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass~\cite{craig}.
 Arguments against naturalness often involve the anthropic principle, which posits that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
 Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck mass.
-Finally, the dominant\fxnote{what do I mean by dominant?} BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below~\cite{dine_naturalness}.
+Finally, the dominant BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below~\cite{dine_naturalness}.
 
 \section{Supersymmetry}
-    \fxnote{seems like I should explicitly mention that naturalness favors lighter sparticles and why the stop correction is so important}
-
     Supersymmetry (SUSY) introduces a new symmetry in which every SM field fits into a larger multiplet with an inherent symmetry between bosons and fermions.
-In its simplest form, SUSY results in one new boson for every SM fermion, one new fermion for every SM boson, and one new Higgs doublet.
-The increase in particle multiplicity calls for a new naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
+In its simplest form, SUSY predicts one new boson for every SM fermion, one new fermion for every SM boson, and one new Higgs doublet.
+The increase in particle multiplicity calls for a naming convention: the spin-0 superpartners to the SM fermions are referred to as sfermions (e.g.
 stop or smuon), and the spin-$\frac{1}{2}$ superpartners to the SM bosons are given the name of their SM counterpart with ``ino" tacked on to the end (e.g.
-Higgsino or wino).\fxnote{describe charginos, neutralinos?} Collectively the superpartners to the SM particles are known as sparticles~\cite{primer}.
+Higgsino or wino).
+Collectively the superpartners to the SM particles are known as sparticles~\cite{primer}.
 
@@
         \quad = \quad 0 \quad
-        \caption{Corrections to the Higgs mass from the top (left) and stop (right) cancel in exact SUSY. Diagram created with~\cite{tikz}.}
+        \caption{Corrections to the Higgs mass from the top quark (left) and stop squark (right) cancel in exact SUSY.
+The top and stop contributions are enhanced by the large top Yukawa coupling.
+Diagrams created with~\cite{tikz}.}
         \label{exact_susy_correction}
@@
 
+    \fxnote{inconsistent with eq 4!!!!}  
     \noindent \begin{equation}
@@
 A handful of models with particular approaches to SUSY breaking that are particularly prominent or particularly relevant to naturalness or long-lived particles are gauge-mediated SUSY breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating (RPV) SUSY.
-The details of these models will be explored as needed throughout this paper.
 
 \section{Long-Lived Particles}
-    The SUSY variants most relevant to this discussion are those that are motivated by naturalness and \fxnote{and/or?} produce a signal that would be missed by common SUSY search techniques.
-Specifically, we are interested in SUSY models that predict new long-lived particles (LLPs), which are defined as particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
+    The SUSY models most relevant to this discussion are those that are motivated by naturalness and produce long-lived particles (LLPs), a signal that could be missed by common SUSY search techniques.
+LLPs are defined as particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
 This category includes everything from particles that decay before reaching the inner tracker to particles that propagate through the entire detector.
@@
 Neutrons and muons, whose decays are shown in Fig.\ref{sm_llp_processes}, are long-lived for reasons (2), (3), and (4).
-Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay\fxnote{Alan doesn't think the muon-electron mass difference is that small...}.
+Being pure weak decays, they have small coupling constants and decay through a W, which is far more massive than either parent particle.
+Finally, the proton and electron masses leave them little phase space in which to decay.
 
@@
             };
-            \caption{Long-lived decays of the neutron and muon. Diagram created with~\cite{tikz}.}
+            \caption{Long-lived decays of the neutron and muon. Diagrams created with~\cite{tikz}.}
             \label{sm_llp_processes}
@@
 Conserving the product of R-parity at each vertex has two immediate phenomenological consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable.
-A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches~\cite{primer}\fxnote{could mention DM as well}\fxnote{Andrew says define met and maybe explain how weakly interacting stable particles produce met}.
+A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches~\cite{primer}.
 
     On the other hand, models with weakly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs~\cite{fate}.
-A similar situation arises in GMSB models\fxnote{should I describe GMSB?} where the gravitino is the LSP.
+A similar situation arises in GMSB models where the gravitino is the LSP.
 The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which suppresses the NSLP decay rate and can lead to LLPs~\cite{dimopoulos_low_energy}.
@@
 In these models, the gluino becomes long-lived when its decay to a quark-antiquark pair and neutralino is mediated by a highly virtual squark~\cite{kilian_split}.
-\fxnote{mention that Split throws out naturalness motivation?} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the winos as the lightest gauginos, which leads to nearly degenerate LSP and NLSP.
-The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space~\cite{randall_sundrum_out_of_this_world}\fxnote{the winos, binos, and higgsinos are not mass eigenstates, so they are not what we search for in an experiment.
-We search for charginos and neutralinos, which are linear combinations of winos, binos, and higgsinos, says andrew}.
+On the other hand, some AMSB models predict the winos as the lightest gauginos, which leads to nearly degenerate LSP and NLSP.
+The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space~\cite{randall_sundrum_out_of_this_world}.
 
-    \fxnote{show a few SUSY spectra?}
-
-\section{The CMS Detector}\fxnote{Add pictures of everything}
+\section{The CMS Detector}
     \subsection{Overview}
-        \fxnote{define eta, coordinate system in general}
-        \fxnote{Mention that ATLAS is similar, says Andrew}  
-        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC), a circular collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}.
+        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC), a circular collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present.
 To reconstuct final-state particles, CMS uses a particle-flow algorithm that combines information from several subdetectors nested radially in and around a \SI{3.8}{\tesla} superconducting solenoid.
@@
     \subsection{Tracker}
-        \fxnote{mention that analyses below used pre-upgrade tracker}
         In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
 The tracker is subdivided into two regions.
-Inside \SI{20}{cm}, the pixel tracker  uses smaller\fxnote{than what?} silicon pixels to keep the occupancy near \SI{0.1}{\percent} despite the high\fxnote{specify} particle flux.
+Inside \SI{20}{cm}, the pixel tracker uses small silicon pixels to keep the occupancy near \SI{0.1}{\percent} despite the high particle flux.
 Outside \SI{20}{\cm}, the silicon strip tracker (SST) achieves similar occupancy with larger silicon strips~\cite{cms_tdr}.\fxnote{check occupancy numbers}
@@
 The pixels are spread between four barrel layers at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks at $\num{29} < \mathrm{z} < \SI{52}{cm}$.
-The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\lvert\eta\rvert < \num{2.4}$\fxnote{define eta} and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017~\cite{cms_pixel_upgrade}.
+The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\lvert\eta\rvert < \num{2.4}$.
 
@@
         Just outside the pixel tracker, the silicon strip tracker (SST) occupies the $\num{20} < r < \SI{116}{cm}$ and $\lvert z \rvert < \SI{282}{cm}$ region of CMS.
-Composed of \num{9.3} million silicon strips that vary in size \fxnote{look up and specify} depending on particle flux in the region, the SST covers an active area of roughly \SI{196}{m^2}.
+Composed of \num{9.3} million silicon strips that vary in size depending on particle flux in the region, the SST covers an active area of roughly \SI{196}{m^2}.
 At each trigger, the strip output voltage is read out via optical link~\cite{cms_pixel_upgrade}.
@@
         The barrel section extends radially from \num{129} to \SI{177}{cm} and covers a pseudorapidity range of \num{0} to \num{1.479}.
-The crystals are tapered to approximately project back to the IP\fxnote{define if not already} but not so perfectly that likely particle trajectories align with cracks.
+The crystals are tapered to approximately project back to the IP but not so perfectly that likely particle trajectories align with cracks.
 Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.
@@
 The flux returns through an iron yoke that also houses the muon system.
-The significant \fxnote{quantify?} bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of \SI{10}{\percent} for muons up to \SI{1}{\tera\electronvolt}\cite{cms_experiment}.
+The significant  bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of \SI{10}{\percent} for muons up to \SI{1}{\tera\electronvolt}\cite{cms_experiment}.
 
@@
 Each CSC has six gas gaps with radial cathode strips and nearly perpendicular planes of anode wires.
-The wire signal from the ionization-induced electron avalanche is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements.
+The wire signal from the ionization-induced electron avalanche is fast enough to use in the L1 trigger, while the slower cathode strip signal provides precise position measurements.
 All in all, the CSC spacial resolution is approximately \SI{200}{\micro\m} and the angular resolution is approximately \SI{10}{\milli\radian}.
@@
         LLPs leave distinct signatures that differentiate them from SM backgrounds but also add complexity to LLP analyses.
-CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays, so LLP searches are often forced\fxnote{the searchers are forced, not the searches} to stray from the traditional analysis path in terms of object reconstruction and background estimation.
+CMS and ATLAS were mainly designed to reconstruct stable particles from prompt decays, so LLP searches are often forced to stray from the traditional analysis path in terms of object reconstruction and background estimation.
 This report focuses on four complementary LLP signatures: displaced vertices, disappearing tracks, low-velocity particles, and particles that come to a stop before decaying.
-See Fig.~\ref{jamie_cartoon} for a cartoon of several possible LLP signatures\fxnote{probably a better way to word this sentence}.
+See Fig.~\ref{jamie_cartoon} for a cartoon of several possible LLP signatures.
 
@@
 
-        Displaced vertex and disappearing track analyses both look for\fxnote{again, analysts look, not analyses} particles that are unstable on detector timescales.
-Displaced vertex searches are sensitive to LLPs that decay to visible particles within the inner volume \fxnote{specify} of the detector, leaving tracks that point back to a vertex some measurable distance from the nominal interaction point (IP)~\cite{atlas_displaced}.
+        Displaced vertex and disappearing track analyses both look for particles that are unstable on detector timescales.
+Displaced vertex searches are sensitive to LLPs that decay to visible particles within the inner volume of the detector, leaving tracks that point back to a vertex some measurable distance from the nominal interaction point (IP)~\cite{atlas_displaced}.
 Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed~\cite{atlas_disappearing}.
-Together, these two types of analyses cover a wide range of lifetimes and topologies for LLPs that decay on detector timescales\fxnote{find something to cite}.
+Together, these two types of analyses cover a wide range of lifetimes and topologies for LLPs that decay on detector timescales.
 
-        Slow and stopped particle searches, on the other hand, are sensitive to detector-stable\fxnote{define?} LLPs that are far more massive\fxnote{be able to quantify} than any stable SM particle.
-The lower velocity of these high-mass particles can show up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta = \frac{v}{c} > \num{0.9}$\fxnote{check this number}~\cite{cms_hscp}.
-Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy\fxnote{how long and how small?}.
+        Slow and stopped particle searches, on the other hand, are sensitive to detector-stable LLPs that are far more massive than any stable SM particle.
+The lower velocity of these high-mass particles can show up as increased ionization energy loss per unit distance or longer time-of-flight (TOF) measurements than SM particles~\cite{cms_hscp}.
+Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy.
 These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings~\cite{cms_stopped}.
 
-        These\fxnote{I've been saying `these' a lot recently} four approaches cover a wide\fxnote{how wide} range of LLP lifetimes that would be missed in traditional searches.
+        These four approaches cover a wide range of LLP lifetimes that would be missed in traditional searches.
 The next sections will examine a recent example of each analysis type from either ATLAS or CMS.
@@
     \subsection{Displaced Vertices}
-        LLPs that decay before reaching the inner tracker can be identified with a displaced vertex (DV)\fxnote{DVs defined clearly enough in overview?}.
+        LLPs that decay before reaching the inner tracker can be identified with a displaced vertex (DV).
 ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity~\cite{atlas_displaced}.
-The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range\fxnote{Am I defining sensitivity range consistently across analyses?}.
+The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range.
 
-        This search\fxnote{repetitive wording} uses a simplified benchmark model in the Split SUSY paradigm where gluinos are kinematically accessible but squarks are not.
-The relevant process, shown in Fig.~\ref{displaced_process}, is pair-produced gluinos that decay to a quark-\fxnote{how to punctuate?}virtual squark pair.
-The virtual squark then decays to a quark and the LSP, presumed to be a neutralino\fxnote{have I defined neutralino?}\fxnote{why is this a reasonable assumption?}.
-The large mass of the intermediate squark suppresses the gluino decay, giving the gluino enough time to form an R-hadron\fxnote{first use.
-Define here if not in LLP section} that propagates some measurable distance before decaying.
+        This search uses a simplified benchmark model in the Split SUSY paradigm where gluinos are kinematically accessible but squarks are not.
+The relevant process, shown in Fig.~\ref{displaced_process}, is pair-produced gluinos that decay to a quark-virtual squark pair.
+The virtual squark then decays to a quark and the LSP, presumed to be a neutralino.
+The large mass of the intermediate squark suppresses the gluino decay, giving the gluino enough time to form an R-hadron that propagates some measurable distance before decaying.
 
@@
         Because no SM process produces events that meet the mass and track multiplicity requirements on the DV, only instrumental backgrounds are considered.
-Specifically, the authors consider hadronic interactions in detector material, incorrectly combined vertices from short-lived SM particles, and hits from unrelated tracks that are incorrectly added to low-mass vertices\fxnote{unnecessary details?
-I need to get better at explaining this} .
+Specifically, the authors consider hadronic interactions in detector material, incorrectly combined vertices from short-lived SM particles, and hits from unrelated tracks that are incorrectly added to low-mass vertices.
 
@@
         \includegraphics[width=0.6\textwidth]{images/material_map}
-        \caption{Map of material dense regions of the ATLAS detector\fxnote{explain more}~\cite{atlas_displaced}.}
+        \caption{Map of material dense regions of the ATLAS detector~\cite{atlas_displaced}.}
         \label{material_map}
@@
         Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
-Specifically, models with winos as the lightest gauginos\fxnote{have these words been defined?}, such as many AMSB models, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate that eventually decays to the neutralino LSP and, commonly, a pion\fxnote{why?}.
+Specifically, models with winos as the lightest gauginos, such as many AMSB models, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate that eventually decays to the neutralino LSP and, commonly, a pion.
 The nearly degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products.
@@
 
-        Pixel tracklets can be faked\fxnote{don't use faked, says CMS} by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
+        Pixel tracklets can be faked by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
 These backgrounds come primarily from $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and estimates for each type of background are obtained from data.
@@
 Sticking with the natural SUSY theme, this discussion will focus on long-lived gluinos, which appear in models such as Split SUSY when squarks and sleptons are quite heavy, but the gluinos are relatively light.
-After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.
+After being pair produced, gluinos form R-hadrons and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.
 This process is exactly the same as in Fig.~\ref{displaced_process}, but in this case the gluino has enough time to form R-hadrons\fxnote{double check}.
@@
         \includegraphics[width=\textwidth]{images/stopped_reject_cosmic_tof}
-        \caption{Cosmic muon rejection using time-of-flight information from the muon system\fxnote{explain}~\cite{cms_stopped}.}
+        \caption{Cosmic muon rejection using time-of-flight information from the muon system~\cite{cms_stopped}.}
         \label{stopped_muon_differentiation}
@@
 
-        HSCPs will often be misidentified or missed entirely by standard reconstruction algorithms and analysis criteria, which tend to assume $\beta \approx \num{1}$ and $\lvert q \rvert = e$.
-Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models\fxnote{do I need figures for these?}: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived lepton-like fermions with arbitrary electric charge.
+        HSCPs will often be misidentified or missed entirely by standard reconstruction algorithms and analysis criteria, which tend to assume $\frac{v}{c} \approx \num{1}$ and $\lvert q \rvert = e$.
+Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived lepton-like fermions with arbitrary electric charge.
 This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY.
@@
 No well-defined, universally agreed upon criteria exist, but certain themes recur in many discussions of natural model building~\cite{craig, vestiges, evans_toward_full, feng, cornering, kim}.
-The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits\fxnote{Did I just steal Chris's language?}.
+The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits.
 
-    \fxnote{I should be able to combine or reorganize the next two paragraphs to flow better} 
     The parameters of interest are the Higgsino, stop, and gluino masses, which correct the Higgs mass at tree-level, one-loop, and two-loops, respectively (see Eqs.~\ref{higgsino_correction}-\ref{gluino_correction}).
@@
 
-    \fxnote{define \mu, Q?} 
-    \fxnote{make sure these are logically and notationally consistent w/ earlier higgs corrections} 
+    \fxnote{inconsistent w/ eq. 2?} 
     \noindent \begin{equation}
@@
     Natural SUSY scenarios, then, are most likely to be constrained by limits on the stop, gluino, and Higgsino masses.
-The Higgsino, however, does not carry color charge and is far less likely\fxnote{be able to quantify} to be produced at the LHC, leaving stop and gluino mass limits as the most important general constraints on natural SUSY models.
+The Higgsino, however, does not carry color charge and is far less likely to be produced at the LHC, leaving stop and gluino mass limits as the most important general constraints on natural SUSY models.
 As shown in Eqs.~\ref{stop_correction} and~\ref{gluino_correction}, the size of stop and gluino corrections also depends on $\Lambda$, the messenger scale of SUSY breaking.
@@
 Before null results and serious constraints started rolling in, it was common to refer to the $\Delta \lesssim 10$ regions of parameter space as natural, but as models are constrained, physicists seem willing to accept greater degrees of fine tuning.
-Feng proposes an interesting way to recast this problem: instead of asking which regions of parameter space are most natural, physicists should instead ask themselves, ``If superpartners were discovered, what level of fine tuning would be sufficient to convince me that the gauge hierarchy problem is solved by supersymmetry and I should move on to researching other problems?"\fxnote{paraphrase for brevity?} Anecdotally, fine tuning thresholds tend to increase when the question is posed in this way~\cite{feng}.
+Feng proposes an interesting way to recast this problem: instead of asking which regions of parameter space are most natural, physicists should instead ask themselves, ``If superpartners were discovered, what level of fine tuning would be sufficient to convince me that the gauge hierarchy problem is solved by supersymmetry and I should move on to researching other problems?" Anecdotally, fine tuning thresholds tend to increase when the question is posed in this way~\cite{feng}.
 
@@
 Fig.~\ref{cornering_limits} shows the results from one such attempt using $\approx \SI{15}{\femto\barn^{-1}}$ of \SI{13}{\tera\electronvolt} data for the cases of Effective SUSY, RPV SUSY, and a model that combines RPV with Effective SUSY.
-The authors find that for $\mu = \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space is currently viable in all cases but, barring discovery, will be excluded within the next few years\fxnote{check}.
+The authors find that for $\mu = \SI{100}{\giga\electronvolt}$ and $\Lambda = \SI{20}{\tera\electronvolt}$, a small region of $\Delta < 10$ parameter space is currently viable in all cases but, barring discovery, will be excluded within the next few years.
 

### 2017-08-07 tex/draft.tex
Integrate jamie, reynolds comments and other little fixes

@@
 The gauge bosons include the photon, which communicates the electromagnetic force; the $\mathrm{W}^+$, $\mathrm{W}^-$, and $\mathrm{Z}$, which communicate the weak force; and eight gluons that communicate the strong force.
-Of these, only the $\mathrm{W}^+$ and $\mathrm{W}^+$ are electrically charged and only the gluons carry color charge.
+Of these, only the $\mathrm{W}^+$ and $\mathrm{W}^-$ are electrically charged and only the gluons carry color charge.
 
@@
     SM parameters, such as masses and couplings, are corrected by interactions with virtual particles through loop diagrams.
-Fig.~\ref{loop_diagrams}, for example, shows interactions that correct the Higgs and electron masses.
+Fig.~\ref{loop_diagrams}, for example, shows interactions that correct the Higgs and fermion masses.
 Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid.
@@
         \quad = \quad 0 \quad
-        \caption{Corrections to the Higgs mass from the top quark (left) and stop squark (right) cancel in exact SUSY.
-The top and stop contributions are enhanced by the large top Yukawa coupling.
-Diagrams created with~\cite{tikz}.}
+        \caption{Corrections to the Higgs mass from the top quark (left) and stop squark (right) cancel in exact SUSY. The top and stop contributions are enhanced by the large top Yukawa coupling.}
         \label{exact_susy_correction}
@@
     The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenomena.
-A handful of models with particular approaches to SUSY breaking that are particularly prominent or particularly relevant to naturalness or long-lived particles are gauge-mediated SUSY breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating (RPV) SUSY.
+A handful of models with particular approaches to SUSY breaking that are particularly prominent or particularly relevant to naturalness or long-lived particles are gauge-mediated SUSY breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating (RPV) SUSY\fxnote{find a way to water this down or kill it}.
 
@@
     The SUSY models most relevant to this discussion are those that are motivated by naturalness and produce long-lived particles (LLPs), a signal that could be missed by common SUSY search techniques.
-LLPs are defined as particles whose lifetimes are such that they decay at least a detectable distance from the nominal interaction point.
+LLPs are defined as particles whose lifetimes are such that they decay a measurable distance from the nominal interaction point.
 This category includes everything from particles that decay before reaching the inner tracker to particles that propagate through the entire detector.
 
-    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly virtual intermediate states, or (4) limited phase space in which to decay.
+    In the SM and in BSM theories, LLPs can result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly virtual intermediate states, or (4) limited phase space in which to decay.
 In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the lightest particles carrying their respective conserved quantities.
@@
             };
-            \caption{Long-lived decays of the neutron and muon. Diagrams created with~\cite{tikz}.}
+            \caption{Long-lived decays of the neutron and muon.}
             \label{sm_llp_processes}
@@
         The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC), a circular collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present.
-To reconstuct final-state particles, CMS uses a particle-flow algorithm that combines information from several subdetectors nested radially in and around a \SI{3.8}{\tesla} superconducting solenoid.
+To reconstruct final-state particles, CMS uses a particle-flow algorithm that combines information from several subdetectors nested radially in and around a \SI{3.8}{\tesla} superconducting solenoid.
 All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}~\cite{cms_experiment}.
@@
 Inside \SI{20}{cm}, the pixel tracker uses small silicon pixels to keep the occupancy near \SI{0.1}{\percent} despite the high particle flux.
-Outside \SI{20}{\cm}, the silicon strip tracker (SST) achieves similar occupancy with larger silicon strips~\cite{cms_tdr}.\fxnote{check occupancy numbers}
+Outside \SI{20}{\cm}, the silicon strip tracker (SST) achieves an occupancy of $\approx \SI{2}{\percent}$ with larger silicon strips~\cite{cms_tdr}.
 
@@
 The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necessitates photodetectors with intrinsic gain that work in magnetic fields\cite{cms_experiment, cms_tdr}.
-Energy resolution is varies from approximately \num{1}-\SI{5}{\percent} depending on the amount of material traversed before reaching ECAL~\cite{ecal_performance}.
+Energy resolution varies from approximately \num{1}-\SI{5}{\percent} depending on the amount of material traversed before reaching ECAL~\cite{ecal_performance}.
 
@@
 
-        The barrel section (HB) spans a pseudorapidity range of \num{-1.4} to \num{1.4} and has \num{2304} towers \fxnote{check}, each of which contains \num{14} \fxnote{check} brass plates and covers an area of \num{0.087} x \SI{0.087}{in} $\eta-\phi$.
+        The barrel section (HB) spans a pseudorapidity range of \num{-1.4} to \num{1.4} and is segmented into \num{32} towers in $\eta$ and \num{64} in $\phi$ that each contain 17 active scintillator layers.
 In addition, an extra layer (or two at $\eta = \num{0}$) of scintillator tiles sits just outside the solenoid.
@@
     \subsection{Solenoid}
-        CMS employs a \SI{4}{T} superconducting solenoid to aid in the measurement of charged particle momenta.
+        CMS employs a \SI{3.8}{T} superconducting solenoid to aid in the measurement of charged particle momenta.
 The solenoid consists of \num{2168} turns of Nb-Ti superconducting cable and has an inner diameter of \SI{6}{m} and a length of \SI{12.5}{m}.
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \includegraphics[width=0.6\textwidth]{images/muon_pt_resolution}
+        \includegraphics[width=0.65\textwidth]{images/muon_pt_resolution}
         \caption{Transverse momentum resolution in the tracker and muon system for small (left) and large (right) pseudorapidity~\cite{cms_image}.}
@@
 \section{LHC Searches for Long-lived Particles} \label {analyses}
-    \fxnote{mention which data was used for each search} 
     \subsection{Overview}
@@
 ATLAS performs a search for such particles by looking for at least one DV along with large MET and large track multiplicity~\cite{atlas_displaced}.
-The search is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range.
+The search uses \SI{32.7}{\femto\barn^{-1}} of \SI{13}{TeV} data and is sensitive to LLPs with lifetimes in the \SI{20}{\pico\s} to \SI{10}{\nano\s} range.
 
@@
         };
-        \caption{Long-lived gluino decay through highly virtual squark. Diagram created with~\cite{tikz}.}
+        \caption{Long-lived gluino decay through highly virtual squark.}
         \label{displaced_process}
@@
 After a dedicated study, the background from merged vertices was found to be negligible.
-Finally, the background from crossing tracks is determined from a model that adds pseudo-tracks to data vertices.
+Finally, the background from crossing tracks is determined from a model that adds fake tracks\fxnote{check} to data vertices.
 
@@
 
-        After estimating $\num{0.02} \pm \num{0.02}$ background events, exactly zero are observed.
+        Exactly zero events are observed with an expected background of $\num{0.02} \pm \num{0.02}$ events.
 The result is then interpreted as an upper limit on the gluino mass and pair-production cross section as a function of gluino lifetime, shown in Fig.~\ref{displaced_limit}.
@@
     \subsection{Disappearing Tracks}
-        Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker.
+        Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signature: charged particles that seem to disappear in the tracker.
 Specifically, models with winos as the lightest gauginos, such as many AMSB models, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate that eventually decays to the neutralino LSP and, commonly, a pion.
@@
         Both ATLAS and CMS looked for disappearing tracks during Run I, but the tracker improvements installed in ATLAS before 2015 datataking and CMS before 2017 datataking should increase sensitivity to decays at shorter radii.
-The ATLAS search presented here is sensitive to LLP lifetimes of approximately \SI{10}{\pico\s} to \SI{10}{\nano\s}.
+The ATLAS search presented here uses \SI{36.1}{\femto\barn^{-1}} of \SI{13}{\tera\electronvolt} data and is sensitive to LLP lifetimes of approximately \SI{10}{\pico\s} to \SI{10}{\nano\s}.
 
@@
 
-        Disappearing track candidates, called pixel tracklets, are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard reconstruction algorithm.
-The pixel tracklets are required to pass several isolation, transverse momentum ($\pT$), and quality requirements such as number of pixel layer hits.
+        Disappearing track candidates are selected with a looser track reconstruction algorithm that runs over hits that were not associated to tracks by the standard reconstruction algorithm.
+The candidates must also meet isolation, transverse momentum ($\pT$), and quality requirements such as number of pixel layer hits.
 Finally, the disappearing tracks are selected by requiring exactly zero associated hits in the subsequent tracking layer.
-Event selection requires one pixel tracklet, no electron or muon candidates (to suppress $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and the $\MET$ and jet requirements associated with either of the two production modes described above.
+Event selection requires one disappearing track candidate, no electron or muon candidates (to suppress $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes), and the $\MET$ and jet requirements associated with either of the two production modes described above.
 
-        Pixel tracklets can be faked by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
+        Disappearing track candidates can be faked by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon.
 These backgrounds come primarily from $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and estimates for each type of background are obtained from data.
@@
     \subsection{Stopped Particles}
-        \fxnote{Add calorimeter search?}  
         \fxnote{too redundant with overview?}
@@
 The eventual decay would then lead to energy deposits in the calorimeters or hits in the muon system that could be out of time with proton bunch crossings.
-A recent CMS analysis looked for such a signal in dimuon final states using the full 2015 and 2016 datasets~\cite{cms_stopped}.
+A recent CMS analysis looks for such a signal in dimuon final states using \SI{39}{\femto\barn^{-1}} of \SI{13}{\tera\electronvolt} data~\cite{cms_stopped}.
 
@@
 
-        After estimating the background by extrapolating data from the cosmic-enriched region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculate the expected background for LLP lifetimes ranging from $10^{-7}$ to $10^6$ s.
+        After estimating the background by extrapolating data from the cosmic-enriched region to the signal region, the authors calculate the expected background for LLP lifetimes ranging from $10^{-7}$ to $10^6$ s.
 In all cases, the expected background is less then one event.
@@
         HSCPs will often be misidentified or missed entirely by standard reconstruction algorithms and analysis criteria, which tend to assume $\frac{v}{c} \approx \num{1}$ and $\lvert q \rvert = e$.
-Inverting these assumptions provides two handles for a dedicated HSCP search in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived lepton-like fermions with arbitrary electric charge.
+Inverting these assumptions provides two handles for a dedicated HSCP search using \SI{2.5}{\femto\barn^{-1}} of \SI{13}{\tera\electronvolt} data collected with the CMS detector in 2015.
+The search is interpreted in the context of three benchmark models: (1) HSCPs that form R-hadrons that either change the sign of their electric charge or become neutral before reaching the MS, (2) lepton-like HSCPs (quasi-stable sleptons) that are produced either through decays of squarks or gluinos or directly if squarks and gluinos are kinematically inaccessible, and (3) long-lived lepton-like fermions with arbitrary electric charge.
 This discussion will focus on the first two models, as they bear more directly on naturalness and SUSY.
@@
         The authors estimate the signal-region background using an ABCD method in which events are binned in a 2-D plane with uncorrelated axes and the ratio of events in two control regions is used to extrapolate into the signal region from a third control region.
-Systematic uncertainties are introduced in background estimation, signal acceptance, and integrated luminosity.
 
@@
     \noindent \begin{figure}[htbp] \begin{center}
-    \includegraphics[width=.8\textwidth]{images/atlas_susy_summary}
+    \includegraphics[width=\textwidth]{images/atlas_susy_summary}
     \caption{Summary of current experimental limits on SUSY models from ATLAS searches.}
@@
         \noindent \begin{figure}[htbp] \begin{center}
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/cornering_effective_100}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/cornering_rpv_100}
         \end{center} \end{subfigure}
-        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
+        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
         \includegraphics[width=\textwidth]{images/cornering_rpv_effective_100}

### 2017-08-07 tex/draft.tex
Final edit before submission

@@
 \section{Naturalness and the Higgs mass}
-    The naturalness criterion can be formulated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of the higher-energy theory, and (3) any dimensionless parameter much smaller than unity must be protected by a custodial symmetry~\cite{giudice_naturally, thooft_naturalness}.
+    The naturalness criterion can be formulated in many ways, a few of which are reproduced here: (1) All dimensionless parameters should be of order one, (2) An effective theory should not be sensitive to small variations in the parameters of the higher-energy theory, and (3) Any dimensionless parameter much smaller than unity must be protected by a custodial symmetry~\cite{giudice_naturally, thooft_naturalness}.
 Physicists implicitly, and perhaps unwittingly, apply naturalness in the form of (1) any time they use dimensional analysis to estimate a quantity, while (2) merely restates the idea that a predictive effective theory requires low-energy phenomena to be decoupled from the details of the high-energy theory.
@@
 Arguments against naturalness often involve the anthropic principle, which posits that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life.
-Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck mass.
+Alternatively, theories such as large extra dimensions lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck scale.
 Finally, the dominant BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below~\cite{dine_naturalness}.
@@
     Exact SUSY also requires that sparticles have the same mass as their SM counterparts, so the uniformly null results in collider searches imply SUSY must be broken.
-With broken SUSY, the sum of diagrams in Fig.~\ref{exact_susy_correction} produces a correction of the form~\cite{feng}
+With broken SUSY, the sum of diagrams in Fig.~\ref{exact_susy_correction} produces a correction of the form~\cite{craig}
 
-    \fxnote{inconsistent with eq 4!!!!}  
     \noindent \begin{equation}
-        \delta \mHiggs^2 = \frac{3y_t^2}{8\pi^2}\left(m_{\sfermion}^2 - m_{\f}^2 \right)\ln(\Lambda^2/m_{\sfermion}^2).
+        \delta \mHiggs^2 \propto m_{\tilde{t}}^2 \ln(\Lambda/m_{\tilde{t}}).
     \label{higgs_susy_correction}
@@
 
-    The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenomena.
-A handful of models with particular approaches to SUSY breaking that are particularly prominent or particularly relevant to naturalness or long-lived particles are gauge-mediated SUSY breaking (GMSB), anomaly-mediated SUSY breaking (AMSB), Split SUSY, and R-parity violating (RPV) SUSY\fxnote{find a way to water this down or kill it}.
+    \noindent The mechanism and scale of SUSY breaking is an open question with many competing answers that achieve different theoretical goals and lead to different TeV-scale phenomena.
+Specific models will be introduced as needed throughout this discussion.
 
@@
     The SUSY models most relevant to this discussion are those that are motivated by naturalness and produce long-lived particles (LLPs), a signal that could be missed by common SUSY search techniques.
-LLPs are defined as particles whose lifetimes are such that they decay a measurable distance from the nominal interaction point.
+LLPs are defined as particles whose lifetimes are such that they decay a measurable distance from the nominal interaction point (IP).
 This category includes everything from particles that decay before reaching the inner tracker to particles that propagate through the entire detector.
@@
     On the other hand, models with weakly coupled R-parity violating (RPV) terms produce long-lived but not perfectly stable LSPs~\cite{fate}.
-A similar situation arises in GMSB models where the gravitino is the LSP.
+A similar situation arises in gauge-mediated SUSY breaking (GMSB) models where the gravitino is the LSP.
 The coupling between the next-to-LSP (NLSP) and gravitino is inversely proportional to the scale of SUSY breaking, which suppresses the NSLP decay rate and can lead to LLPs~\cite{dimopoulos_low_energy}.
@@
 In these models, the gluino becomes long-lived when its decay to a quark-antiquark pair and neutralino is mediated by a highly virtual squark~\cite{kilian_split}.
-On the other hand, some AMSB models predict the winos as the lightest gauginos, which leads to nearly degenerate LSP and NLSP.
+On the other hand, some anomaly-mediated supersymmetry breaking (AMSB) models predict the winos as the lightest gauginos, which leads to nearly degenerate LSP and NLSP.
 The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space~\cite{randall_sundrum_out_of_this_world}.
@@
     \subsection{Tracker}
-        In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
+        In the region closest to the IP, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.
 The tracker is subdivided into two regions.
@@
         Displaced vertex and disappearing track analyses both look for particles that are unstable on detector timescales.
-Displaced vertex searches are sensitive to LLPs that decay to visible particles within the inner volume of the detector, leaving tracks that point back to a vertex some measurable distance from the nominal interaction point (IP)~\cite{atlas_displaced}.
+Displaced vertex searches are sensitive to LLPs that decay to visible particles within the inner volume of the detector, leaving tracks that point back to a vertex some measurable distance from the IP~\cite{atlas_displaced}.
 Disappearing track searches are sensitive to LLPs that decay to particles that are either neutral or too soft to be reconstructed~\cite{atlas_disappearing}.
@@
 After a dedicated study, the background from merged vertices was found to be negligible.
-Finally, the background from crossing tracks is determined from a model that adds fake tracks\fxnote{check} to data vertices.
+Finally, the background from crossing tracks is determined from a model that adds fake tracksto data vertices.
 
@@
     \subsection{Stopped Particles}
-        \fxnote{too redundant with overview?}
         With long enough lifetimes and sufficient mass, LLPs could come to rest in the detector before decaying.
@@
 After being pair produced, gluinos form R-hadrons and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs.
-This process is exactly the same as in Fig.~\ref{displaced_process}, but in this case the gluino has enough time to form R-hadrons\fxnote{double check}.
+This process is exactly the same as in Fig.~\ref{displaced_process}, but in this case the gluino has enough time to form R-hadrons.
 The gluino decay is suppressed by the large squark mass, which leads to its appreciable lifetime.
@@
 Exactly zero events are observed in every lifetime scenario.
-As shown in Fig.~\ref{stopped_limits}, these results are then interpreted as upper limits on the signal production cross section and mass\fxnote{mass of what?}, which are the first limits for stopped particles that decay to muons at the LHC.
+As shown in Fig.~\ref{stopped_limits}, these results are then interpreted as upper limits on the signal production cross section and gluino mass, which are the first limits for stopped particles that decay to muons at the LHC.
 
@@
 If such a particle is also sufficiently massive, it can be categorized as a heavy stable charged particle (HSCP).
-HSCPs are characterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material\fxnote{redundant w/ overview.
-Probably better explained here than there}.
+HSCPs are characterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material.
 Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss, as shown in Fig.~\ref{hscp_dedx}~\cite{cms_hscp}.
@@
 
-        \fxnote{I show separate trk, trk+tof limits but never explain that in text} 
         \noindent \begin{figure}[htbp] \begin{center}
@@
 
-    \fxnote{inconsistent w/ eq. 2?} 
     \noindent \begin{equation}
@@
 Fully covering natural SUSY parameter space will take a dedicated effort from the LLP community, both to maximize the reach of individual searches and to design complementary analyses that can be used to draw general conclusions.
-Although natural SUSY is under pressure from conventional and long-lived null results, it remains one of the least-tuned options for natural BSM physics\fxnote{double check, then cite cornering, feng, nate, and/or giudice}.
+Although natural SUSY is under pressure from conventional and long-lived null results, it remains one of the least-tuned options for natural BSM physics.
 The next several years will be decisive~\cite{cornering}, and physicists will have to be clever to probe every corner of natural parameter space.

### 2017-08-07 tex/draft.tex
Actual last edits before submitting

@@
     When calculating contributions from loop diagrams, one finds that fermion loops differ in sign from boson loops, which means that in SUSY every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa.
-In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory, as shown in Fig.~\ref{exact_susy_correction} below~\cite{primer}.
+In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory~\cite{primer}.
+Fig.~\ref{exact_susy_correction} shows the leading-order cancellation.
 
@@
 After a dedicated study, the background from merged vertices was found to be negligible.
-Finally, the background from crossing tracks is determined from a model that adds fake tracksto data vertices.
+Finally, the background from crossing tracks is determined from a model that adds fake tracks to data vertices.
 
@@
         \end{center} \end{subfigure}
-        \caption{Limits on chargino mass and lifetime in the electroweak production channel (left) and gluino and chargino masses in the gluon pair-production channel with a \SI{0.2}{\nano\s} (center) and \SI{1.0}{\nano\s} chargino lifetime~\cite{atlas_disappearing}.}
+            \caption{Limits on chargino mass and lifetime in the electroweak production channel (left) and gluino and chargino masses in the gluon pair-production channel with a \SI{0.2}{\nano\s} (center) and \SI{1.0}{\nano\s} (right) chargino lifetime~\cite{atlas_disappearing}.}
         \label{disappearing_limits}
@@
 
-    Combining results from several searches can also elucidate new directions for important searches.
+    Combining results from several analyses can also elucidate new directions for important searches.
 By recasting several LLP searches similar to those described in Sec.~\ref{analyses}, Evans and Shelten looked at the current viability of several SUSY spectra that predict long-lived staus.
